---
title: "analysis_bogi"
author: "ludmanyboglarka"
output: html_document
date: "2026-02-13"
---
# load libraries
```{r}
library(dplyr)
library(tidyverse)
library(tidyr)
library(magrittr)
library(apyramid)
library(ggplot2)
```

# load raw data
```{r}
raw_data <- readr::read_csv(("/Users/ludmanyboglarka/Documents/emotional_landscape/raw_data.csv"))
```
## pre-formatting raw data 
```{r}
raw_renamed <- raw_data %>% 
 rename(
    interest = feeling_stage_1,
    amusement = feeling_stage_2, 
    pride = feeling_stage_3, 
    joy = feeling_stage_4, 
    pleasure = feeling_stage_5, 
    contentment = feeling_stage_6, 
    love = feeling_stage_7, 
    admiration = feeling_stage_8, 
    relief = feeling_stage_9, 
    compassion = feeling_stage_10, 
    sadness = feeling_stage_11, 
    guilt = feeling_stage_12, 
    regret = feeling_stage_13, 
    shame = feeling_stage_14, 
    disappointment = feeling_stage_15, 
    fear = feeling_stage_16, 
    disgust = feeling_stage_17, 
    contempt = feeling_stage_18, 
    hate = feeling_stage_19, 
    anger = feeling_stage_20
  ) %>% 
  select(
    -Status, 
    -StartDate, 
    -EndDate, 
    -RecordedDate, 
    -DistributionChannel,
    -UserLanguage
  ) %>% 
  relocate(ResponseId, .before = Progress) %>% 
  mutate(
    across(9:28, as.numeric), 
    across(9:28, ~ na_if(., 0))) %>% ## this replaces 0 values with NA
  mutate(
    research_stage = recode(
      research_stage,
      "Project genesis/ first thoughts/ idea creation" =  "Project genesis", 
       "Preparations (IRB permit, preregistration, experiment preparations)" = "Preparations", 
       "Reality check (e.g., literature search, consultation with colleagues)" = "Reality check", 
       "Waiting for journal's response and revisions" = "Waiting",
       "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)" = "Post-project stage"
  )) %>% 
  slice(-1:-3) %>% 
  filter(dismiss_1 != "No")
```
## load functions
```{r}
source("functions_bogi.R")
```

# =================================================================================
# Emotions By Research Stage
## 1. Emotions during the Data Analysis stage
## 1.1 Emotions on the participant-level
```{r}
analysis_data <- raw_renamed %>% 
  filter(
    research_stage == "Data analysis"
  ) %>%
  analysis_select()

# pivot_longer for the heatmap
analysis_heatmap <- analysis_data %>% 
  longer_heatmap()

# heatmap by participant - Data Analysis stage
analysis_heatmap %>% 
  ggplot(aes(x = emotion, y = ResponseId, fill = intensity)) +
  geom_tile(
    inherit.aes = T,
    position = position_identity(), na.rm = T) +
  scale_fill_gradient(
      low = "white", 
      high = "#02452B", 
      limits = c(0, 7)) +
  labs(
      title = "Intensity of emotions on the level of participants in the Data Analysis stage", 
      tag = "1.1.") +
    theme(
      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
      axis.text.y = element_blank())

ggsave(filename = "heatmap_data_analysis.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )

  ## heatmap_plot(analysis_heatmap)
```

## 1.2. Overall intensity of emotions
```{r}
analysis_overall <- analysis_heatmap %>% 
  sum_analysis() ## summarising emotional intensity on every emotion

analysis_overall %>% 
  plot_overall() +
    labs(
      title = "Overall intensity of emotions in the Data Analysis stage", 
      tag = "1.2.")

ggsave(filename = "overall_data_analysis.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## 2. Emotions during the Preparations stage
## 2.1. Intensity of emotions on the participant-level
```{r}
preparations_data <- raw_renamed %>% 
  filter(
    research_stage == "Preparations"
  ) %>% 
  analysis_select() ## selecting relevant columns

# pivot longer - for the heatmap of participant-level emotions
preparations_heatmap <- preparations_data %>% 
  longer_heatmap()

# heatmap by participant
preparations_heatmap %>%
  heatmap_plot() + 
   scale_fill_gradient(
      low = "white", 
      high = "#2b4a78", 
      limits = c(0, 7)) + 
  labs(
      title = "Intensity of emotions on the level of participants in the Preparations stage", 
      tag = "2.1.")

ggsave(filename = "heatmap_preparations.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## 2.2. Overall intensity of emotions in the preparations stage
```{r}
preparations_overall <- preparations_heatmap %>% 
  sum_analysis() ## summarising emotional intensity on every emotion

preparations_overall %>% 
  plot_overall() + 
  labs(
      title = "Overall intensity of emotions in the Preparations stage", 
      tag = "2.2.")

ggsave(filename = "overall_preparations.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## 3. Emotions while Waiting for journal's response and revisions
## 3.1. Participant-level intensity of emotions
```{r}
waiting_data <- raw_renamed %>% 
  filter(
    research_stage == "Waiting"
  ) %>% 
  analysis_select()

# pivot longer - for the heatmap of participant-level emotions
waiting_heatmap <- waiting_data %>% 
  longer_heatmap()

# heatmap by participant
waiting_heatmap %>% 
  heatmap_plot() + 
   scale_fill_gradient(
      low = "white", 
      high = "#9D3B06", 
      limits = c(0, 7)) + 
  labs(
      title = "Intensity of emotions on the level of participants in the Waiting stage", 
      tag = "3.1.")

ggsave(filename = "heatmap_waiting.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## 3.2. Overall intensity of emotions in the preparations stage
```{r}
waiting_overall <- waiting_heatmap %>% 
  sum_analysis() ## summarising intensity on every emotion

waiting_overall %>% 
  plot_overall() + 
  labs(
      title = "Overall intensity of emotions in the Waiting stage", 
      tag = "3.2.")

ggsave(filename = "overall_preparations.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```
## 4. Post-project stage 
```{r}
post_project <- raw_renamed %>% 
  filter(
    research_stage == "Post-project stage"
  ) %>% 
  select(-dismiss_1) 

# 4.1. accepted and published - mean intensity of emotions
post_project1 <- post_project %>%  
  filter(
    Q22 == "Accepted and published"
  ) %>% 
  select(-Q22_6_TEXT) 

post_project1_long <- post_project1 %>% 
  longer_heatmap() %>% 
  sum_analysis()

# geom_col for mean intensity
post_project1_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Accepted and published", 
      tag = "4.1.")
# most intense emotions if the article was accepted and published: interest, joy, pride, pleasure, relief, contentment (+ admiration, amusement)

ggsave(filename = "overall_accepted_published.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )

# 4.2. Accepted but not yet published
post_project2 <- post_project %>% 
  filter(
    Q22 == "Accepted but not yet published"
  ) %>% 
  select(-Q22_6_TEXT)

post_project2_long <- post_project2 %>% 
  longer_heatmap() %>% 
  sum_analysis()

# geom_col for mean intensity
post_project2_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Accepted but not yet published", 
      tag = "4.2.")

ggsave(filename = "overall_accepted_not_yet_published.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )

## 4.3. Rejected (rejected and abandoned, rejected and being revised, rejected and postponed)
post_project3 <- post_project %>% 
  filter(
    Q22 %in% c("Rejected and abandoned", "Rejected and being revised", "Rejected and postponed")
  ) %>% 
  select(-Q22_6_TEXT)

post_project3_long <- post_project3 %>% 
  longer_heatmap() %>%
  sum_analysis()

post_project3_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Rejected", 
      tag = "4.3.")

ggsave(filename = "overall_rejected.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## 5. Report writing stage - heatmap and overall intensity of emotions
```{r}
report_writing <- raw_renamed %>% 
  filter(
    research_stage == "Report writing"
  ) %>% 
  select(-dismiss_1, -Q22, -Q22_6_TEXT) 

# mean intensity of emotions
report_writing_long <- report_writing %>% 
  longer_heatmap() %>% 
  sum_analysis()

# heatmap 
writing_heatmap <- report_writing %>% 
  longer_heatmap() 

writing_heatmap %>% 
  heatmap_plot() +
   scale_fill_gradient(
      low = "white", 
      high = "#75069D", 
      limits = c(0, 7)) + 
  labs(
      title = "Intensity of emotions on the level of participants in the Waiting stage", 
      tag = "3.1.")

ggsave(filename = "heatmap_report_writing.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )

# geom_col for mean intensity
report_writing_long %>% 
  plot_overall() + 
  labs(
      title = "Report writing", 
      tag = "5.")

ggsave(filename = "overall_report_writing.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```


## 6. facet_wrap plot for emotional intensity in all research stages
```{r}
overall_intensity <- raw_renamed %>% 
  rename(duration = `Duration (in seconds)`) %>% 
  select(
    -Q22, -Q22_6_TEXT, -cause_stage, -dismiss_1, -Finished, -Progress, -duration, -cause_general
  ) %>% 
  arrange(research_stage)

# create plot of overall emotions
## 1. long format
overall_long <- overall_intensity %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity") %>% 
  mutate(intensity = as.numeric(intensity), 
         emotion = factor(emotion, levels = unique(emotion))) %>% 
  group_by(research_stage, emotion) %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T), .groups = "drop") %>% 
  filter(!(is.na(research_stage)))

# create plot 
ggplot(overall_long, aes(x = emotion, y = mean_intensity, fill = intensity)) +
  facet_wrap(~ research_stage, nrow = 3) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#c6a1f9", na.rm = T
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") 

ggsave(filename = "facet_wrap_heatmap.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )

```

# ====================================================================================================
# Gender, age, country, area of research, seniority level, category of work -> connections to emotions
```{r}
## 1. check difference between genders - make plot (men, women, non-binary and prefer not to say)
## 2. t-test to test statistical significance 
## 1.1. women
genders_emotions <- raw_renamed %>%
  filter(
    gender %in% c("Woman", "Man")
  ) %>% 
  select(
    -Finished, -`Duration (in seconds)`, -Progress, -dismiss_1, -cause_stage, -cause_general, -Q22, -Q22_6_TEXT
  ) %>% 
  select(
    -category_of_work, -research_stage, -feeling_general_1, -position, -area, -age, -country, -country_other) %>% 
  rename(
    positive = c("interest", "amusement", "pride", "joy", "pleasure", "contentment", "love", "admiration", "relief", "compassion"), 
    negative = c("sadness", "guilt", "regret", "shame", "disappointment", "fear", "disgust", "contempt", "hate", "anger"))
  

## overall emotions within women (mean_intensity)
genders_long <- genders_emotions %>%
  pivot_longer(
    cols = positive1:negative10,
    names_to = "valence",
    values_to = "intensity",
    values_transform = list(intensity = as.numeric)) %>% 
  mutate(valence = factor(valence,
                          levels = unique(valence)))
genders_wide <- genders_long %>%
  pivot_wider(
    names_from = "valence", 
    values_from = "intensity"
  ) %>% 
  mutate(
    positive_mean = rowMeans(select(., 3:12), na.rm = T), 
    negative_mean = rowMeans(select(., 13:22), na.rm = T)
  ) %>% 
  filter(
    !(is.na(negative_mean)), 
    !(is.nan(positive_mean))
  )
  
summary_genders <- genders_wide %>% 
  group_by(gender) %>% 
  summarise(
    positive = mean(positive_mean),
    negative = mean(negative_mean)
  ) %>% 
  pivot_longer(
    cols = c("positive", "negative"),
    names_to = "valence", 
    values_to = "intensity"
  )

ggplot(summary_genders,
       aes(x = valence, y = intensity)) +
  facet_wrap(~ gender) +
  geom_col(
    fill = "#c6a"
  ) + 
  labs(
    x = "Valence", 
    y = "Mean intensity", 
    title = "Emotional intensity between men and women" 
  ) +
  theme_minimal()

ggsave(filename = "emotions_men_women.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

# ====================================================================================================
# Analysis of standard deviations within the emotions 
```{r}
## flag where SD of emotions are > 1 
sd_flag <- raw_renamed %>% 
  select(
    -Progress, -`Duration (in seconds)`, -Finished, -dismiss_1, -Q22, -Q22_6_TEXT 
  ) %>% 
  mutate(across(2:21, as.numeric),
         mean_landscape = rowMeans(across(2:21), na.rm = T),
         sd_landscape = apply(across(2:21), 1, sd, na.rm = T)) %>% 
  filter(
    !(is.na(mean_landscape)),
    !(is.na(sd_landscape)), 
    !(is.nan(mean_landscape))
  )

## sd smaller than 0.9 -> emotional landscape lacks dimension
small_sd <- sd_flag %>% 
  filter(
    sd_landscape < 0.9
  )

## exporative: greater sd, potential reasons??
great_sd <- sd_flag %>% 
  filter(
    sd_landscape > 2.5
  )
```

## ====================================================================
# Participants with negative_mean > positive_mean -> age distributions
```{r}
averages_data <- raw_renamed %>% 
  select(
    -Progress, -`Duration (in seconds)`, -Finished, -dismiss_1,
  ) %>% 
  mutate(
    across(5:24, as.numeric), 
    pos_mean = rowMeans(across(5:14), na.rm = T), 
    neg_mean = rowMeans(across(15:24), na.rm = T), 
    across(35:36, ~ na_if(., NaN))
  )

## filter: average intensity of emotions is higher regarding the negative emotions
negative_means <- averages_data %>% 
  filter(
    ((pos_mean < neg_mean) | is.na(pos_mean)), 
    !is.na(neg_mean)
  )

## classifying the data types of columns
age_negative <- negative_means %>%
  pos_neg_classify()

## creating age groups
age_negative_counts <- age_negative %>% 
  age_grouping()

## pyramid to explore the age distribution, split by gender 
age_negative_counts %>% 
  pyramid_plot()

ggsave(filename = "age_pyramid.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```
## participants with negative_mean > positive_mean -> position
```{r}
position_negative <- negative_means %>%
  rename(category = position) %>% ## rename column for functions
  categories_prepare()

## pie chart for the distribution of positions
position_negative %>% 
  piechart_plot()

ggsave(filename = "neg_position_piechart.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## participants with negative_mean > positive_mean -> category_of_work
```{r}
work_negative <- negative_means %>% 
  rename(category = category_of_work) %>% ## rename column for the functions
  categories_prepare()

## pie chart for the distribution of the categories
work_negative %>% 
  piechart_plot()

ggsave(filename = "neg_work_piechart.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```
## participants with negative_mean > positive_mean -> research area 
```{r}
area_negative <- negative_means %>% 
  rename(category = area) %>% ## rename column for the functions
  categories_prepare()

area_negative %>% 
  piechart_plot()

ggsave(filename = "neg_researcharea_piechart.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```
## participants with negative_mean > positive_mean -> research stage
```{r}
stage_negative <- negative_means %>% 
  rename(category = research_stage) %>% ## rename column for functions 
  categories_prepare() %>% 
  mutate(
    category = stringr::str_trunc(category, 40))

## piechart plot
stage_negative %>% 
  piechart_plot()

ggsave(filename = "neg_research_stage_piechart.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## ====================================================================
# Participants with positive_mean > negative_mean -> age distributions
```{r}
positive_means <- averages_data %>% 
  filter(
    ((pos_mean > neg_mean) | is.na(neg_mean)), 
    !is.na(pos_mean)
  ) 

## classifying the data types of columns
age_positive <- positive_means %>%
  pos_neg_classify()

## creating age groups
age_positive_counts <- age_negative %>% 
  age_grouping()

## creating the age pyramid
age_positive_counts %>% 
  pyramid_plot()

ggsave(filename = "pos_age_pyramid.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )

```

## participants with negative_mean > positive_mean -> position
```{r}
position_positive <- positive_means %>%
  rename(category = position) %>% ## rename column for functions
  categories_prepare()

## pie chart for the distribution of positions
position_positive %>% 
  piechart_plot()

ggsave(filename = "pos_positive_piechart.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## participants with negative_mean < positive_mean -> category_of_work
```{r}
work_positive <- positive_means %>% 
  rename(category = category_of_work) %>% ## rename column for the functions
  categories_prepare()

## pie chart for the distribution of the categories
work_positive %>% 
  piechart_plot()

ggsave(filename = "pos_work_piechart.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )

```
## participants with negative_mean < positive_mean -> research area 
```{r}
area_positive <- positive_means %>% 
  rename(category = area) %>% ## rename column for the functions
  categories_prepare()

area_positive %>% 
  piechart_plot()

ggsave(filename = "pos_research_area_piechart.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## participants with negative_mean < positive_mean -> research stage
```{r}
stage_positive <- positive_means %>% 
  rename(category = research_stage) %>% ## rename column for functions 
  categories_prepare() %>% 
  mutate(
    category = stringr::str_trunc(category, 40))

## piechart plot
stage_positive %>% 
  piechart_plot()

ggsave(filename = "pos_research_stage_piechart.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```


## ========================================================================
# Distributions of positive-negative emotions by research stage
## 1. Interest:
```{r}
# 1.1. Interest (first try)
interest_distribution <- raw_renamed %>% 
  select(
    interest, research_stage
  ) %>% 
  filter(!(is.na(interest))) %>%
  group_by(research_stage) %>%
  mutate(
    research_stage = stringr::str_trunc(research_stage, 30))

interest_distribution %>% 
  ggplot(aes(x = research_stage, y = interest)) +
  geom_col(fill = "#B5E6D0", na.rm = T
    ) +
    labs(
      title = "Intensity of 'interest' through the research stages", tag = "2.") +
    theme(
      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```
## 2. Facet_wrap plot for all emotions in the research stages
```{r}
emotion_vars <-  c("interest", "amusement", "pride", "joy", "pleasure", "contentment", "love", "admiration", "relief", "compassion", "sadness", "guilt", "regret", "shame", "disappointment", "fear", "disgust", "contempt", "hate", "anger")                 

all_distribution <- raw_renamed %>% 
  select(
    research_stage, interest:anger
  ) %>% 
  filter(!(is.na(research_stage))) %>% 
  mutate(
    research_stage = stringr::str_trunc(research_stage, 20)) %>% 
  group_by(research_stage) %>% 
  summarise(
    across(
      all_of(emotion_vars), 
      ~ round(mean(.x[.x != 0], na.rm = T), 3)
    )
  ) %>% 
  pivot_longer(
    cols = all_of(emotion_vars),
    names_to = "emotion", 
    values_to = "intensity"
  ) %>% 
  mutate(
    emotion = factor(emotion, levels = emotion_vars)
  )

all_distribution %>% 
  ggplot(aes(x = research_stage, y = intensity)) +
  geom_col(fill = "#84CDF0", na.rm = T
    ) +
    labs(
      title = "Intensity of all emotions through the research stages") +
    theme(
      axis.text.x = element_text(angle = 
                                   45, vjust = 1, hjust = 1, size = 6)) +
  facet_wrap(~ emotion, nrow = 3) 

ggsave(filename = "all_distribution_facet.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

## ===================================================================
# Analyses to NA data regarding the emotions (emotions that were 'not felt')
```{r}
## df for counting NA values by research stage
na_counter <- raw_renamed %>% 
  select(
    ResponseId, interest:anger, research_stage
  ) %>% 
  filter(!(is.na(research_stage))) %>% 
  group_by(research_stage) %>% 
  summarise(
    across(interest:anger, ~ sum(is.na(.))))

## Data analysis stage - long format for the barchart
data_analysis_na <- na_counter %>% 
  filter(research_stage == "Data analysis") %>% 
  pivot_longer(
    cols = -research_stage, 
    names_to = "emotion", 
    values_to = "na_count"
  )

## -> Barchart
data_analysis_na %>% 
  ggplot(aes(emotion, na_count)) +
  geom_bar(stat = "identity", fill = "#34B3E0") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") +
  labs(
      title = "NA values in the Data Analysis stage")

## All stages -> facet_wrap
na_all <- na_counter %>%
  pivot_longer(
    cols = -research_stage, 
    names_to = "emotion", 
    values_to = "na_count"
  )

## -> Barchart for all stages
na_all %>% 
  ggplot(aes(emotion, na_count)) +
  facet_wrap(
    ~ research_stage) +
  geom_bar(stat = "identity", fill = "#8DB5E0") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") +
  labs(
      title = "NA values in the research stages")

ggsave(filename = "na_facet_wrap.png", 
       plot = get_last_plot(), 
       path = "/Users/ludmanyboglarka/Documents/emotional_landscape/plots" )
```

