---
title: '"Analysiscombined"'
author: "radibarbi, ludmanybogi, fejossandor"
date: "2026-02-28"
output: html_document
---

# 00. Load libraries
```{r}
# Updated library loading with checks for installation

if (!require("tidyverse")) install.packages("tidyverse")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("dplyr")) install.packages("dplyr")
if (!require("stringr")) install.packages("stringr")
if (!require("rstatix")) install.packages("rstatix")
if (!require("ggthemes")) install.packages("ggthemes")
if (!require("tidyr")) install.packages("tidyr")
if (!require("patchwork")) install.packages("patchwork")
if (!require("scales")) install.packages("scales")
if (!require("magrittr")) install.packages("magrittr")
if (!require("apyramid")) install.packages("apyramid")
if (!require("rlang")) install.packages("rlang")
if (!require("maps")) install.packages("maps")
if (!require("gganimate")) install.packages("gganimate")
if (!require("magick")) install.packages("magick")




library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(rstatix)
library(ggthemes)
library(tidyr)
library(patchwork)
library(scales)
library(magrittr)
library(apyramid)
library(rlang)
library(maps)
library(gganimate)
library(magick)
```


# 0. Data cleaning, data wrangling
```{r}
# Updated data loading with checks for missing data handling
source("functionscombined_new.R")
raw_data <- read.csv("raw_data.csv", na.strings = c("", "NA", "NaN"))

# Changed to data_clean for easier handling for next wrangling
data_clean = raw_data[-1:-2, ]

feeling_cols = c("interest","amusement","pride","joy","pleasure",
  "contentment","love","admiration","relief","compassion", "sadness", "guilt", "regret" ,"shame", 
                       "disappointment" , "fear", "disgust", "contempt" , "hate","anger")

positive_feelings <- c(
  "interest","amusement","pride","joy","pleasure",
  "contentment","love","admiration","relief","compassion"
)
negative_feelings <- c("sadness", "guilt", "regret" ,"shame", 
                       "disappointment" , "fear", "disgust", "contempt" , "hate","anger")

original_order = c(
  "Project genesis/ first thoughts/ idea creation",
  "Reality check",
  "Preparations",
  "Data collection",
  "Data analysis",
  "Report writing",
  "Revisions",
  "Waiting",
  "Post-project stage")
```

```{r}
data_recoded = data_clean %>% 
  rename(interest = feeling_stage_1,
         amusement = feeling_stage_2,
         pride = feeling_stage_3,
         joy = feeling_stage_4,
         pleasure = feeling_stage_5,
         contentment = feeling_stage_6,
         love = feeling_stage_7, 
         admiration = feeling_stage_8, 
         relief = feeling_stage_9, 
         compassion = feeling_stage_10,
         sadness = feeling_stage_11, 
         guilt = feeling_stage_12,
         regret = feeling_stage_13, 
         shame = feeling_stage_14, 
         disappointment = feeling_stage_15, 
         fear = feeling_stage_16, 
         disgust = feeling_stage_17, 
         contempt = feeling_stage_18,
         hate = feeling_stage_19, 
         anger = feeling_stage_20)%>% 
  mutate(research_stage = factor(research_stage), 
         area = factor(area),
         gender = factor(gender),
         position = factor(position), 
         category_of_work = factor(category_of_work), 
         ) %>% 
  mutate(research_stage = recode(research_stage,	
                                 "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)"
                                 = "Post-project stage", 
                                 "Preparations (IRB permit, preregistration, experiment preparations)" = 
                                   "Preparations",
                                 "Reality check (e.g., literature search, consultation with colleagues)" =
                                   "Reality check",
                                 "Waiting for journal's response and revisions" = "Waiting",
                                 "Project genesis/ first thoughts/ idea creation" = "Project genesis"
                                 )) %>% 
  mutate(across(all_of(feeling_cols),
                ~ as.numeric(as.character(.x)))) %>% 
  mutate(feeling_general_1 = as.numeric(as.character(feeling_general_1))) %>% 
  filter(!(dismiss_1 == "No")) %>% 
  rename(Duration = `Duration..in.seconds.`) %>% 
  mutate(across(interest:anger, ~ na_if(.x, 0))) %>% 
  mutate(NAcount = rowSums(is.na(across(interest:anger)))) %>%
  mutate(NAcountpos = rowSums(is.na(across(interest:compassion)))) %>% 
  mutate(NAcountneg = rowSums(is.na(across(sadness:anger)))) 


country_emotions = data_recoded %>%  
  select(ResponseId, country, country_other, all_of(feeling_cols)) %>% 
  mutate(across(interest:anger, ~ na_if(.x, 0))) %>% 
mutate(
  mutate(across(all_of(feeling_cols),
                ~ as.numeric(as.character(.x)))))

country_emotions = country_emotions %>% 
  pivot_longer(cols = c(country, country_other), 
               names_to = "group", 
               values_to = "country")
country_emotions = country_emotions %>% 
  filter(!(country == "")) %>% 
  filter(!(ResponseId == "R_7YyTHrAj3Gc1fHP")) 


target_id = "R_7gbaE2EDWdQ3wOo"
target_text = "Also Germany Australia and recently China"


split_row = country_emotions %>%
  filter(ResponseId == target_id, country == target_text) %>%
  mutate(
    country = str_replace_all(country, "(?<=[a-z])(?=[A-Z])", " "),
    country = str_remove(country, "^Also\\s+"),
    country = str_remove(country, "\\s+ and recently\\s+"),
    country = str_squish(country),
    country = str_replace_all(country, "\\s+", ",")) %>%
  separate_rows(country, sep = ",")

rest <- country_emotions %>%
  filter(!(ResponseId == target_id & country == target_text))

country_emotions_clean <- bind_rows(split_row, rest)

country_emotions_clean = country_emotions_clean %>% 
  mutate(country = if_else(country == "Did my PhD in the US graduated in August and moved to Australia for postdoc", "United States of America", country)) %>% 
  mutate(country = if_else(country == "i work from home from italy", "Italy", country)) %>% 
  mutate(country = if_else(country == "Israel I am doing a collaboration in italy", "Israel", country)) %>% #because they indicated Italy in the "country" option
  mutate(country = if_else(country == "Actually Im from Palestine unfortunatley there is no mention for state of Palestine", "Palestine", country)) %>% #???
  mutate(country = if_else(country == "China ", "China", country)) %>% 
  mutate(country = if_else(country == "Makedonija", "Northern Macedonia", country)) %>% 
  mutate(country = if_else(country == "I am from Canada and have done research there", "Canada", country)) %>% 
  mutate(country = if_else(country == "south africa", "South Africa", country)) %>% 
  mutate(country = if_else(country == "England", "United Kingdom of Great Britain and Northern Ireland", country)) %>% 
  filter(!(country == "Africa")) %>% 
mutate(country = if_else(country == "N Macedonia", "North Macedonia", country)) %>% 
  filter(!(country %in% c("and","recently"))) %>% 
  mutate(country = if_else(country == "United States of America", "USA", country)) %>% 
  mutate(country = if_else(country == "United Kingdom of Great Britain and Northern Ireland", "UK", country))

country_emotions_clean <- bind_rows(
  country_emotions_clean %>%
    filter(ResponseId == "R_2GQ90ZxUHZ6JyFB", country == 	
             "Burkina Faso USA") %>%
    mutate(country = str_replace(country, "\\s+USA\\b", ",USA")) %>%  # insert delimiter before USA
    separate_rows(country, sep = ","),
  country_emotions_clean%>%
    filter(!(ResponseId == "R_2GQ90ZxUHZ6JyFB"  & country == "Burkina Faso USA")))



country_emotions_clean <- country_emotions_clean %>%
  mutate(
    continent = case_when(
      country %in% c("Algeria", "Burkina Faso", "Egypt", 
                     "Mali", "South Africa", "Sudan") ~ "Africa",
      country %in% c("Argentina", "Brazil", "Chile", "Costa Rica", 
                     "Colombia") ~ "South America/ Central America",
      country %in% c("Canada", "Mexico", 
                     "USA") ~ "North America",
      country %in% c("Austria", "Belgium", "Croatia", "Czech Republic",
                     "Denmark", "Finland", "France", "Germany", "Greece",
                     "Hungary", "Iceland", "Ireland", "Italy", "Lithuania",
                     "Netherlands", "North Macedonia", "Norway", "Poland",
                     "Portugal", "Romania", "Serbia", "Slovenia", "Spain",
                     "Sweden", "Switzerland",
                     "UK") ~ "Europe",
      country %in% c("China", "Hong Kong (S.A.R.)", "India", "Iran", "Iraq",
                     "Israel", "Japan", "Lebanon", "Malaysia", "Pakistan",
                     "Palestine", "Philippines", "Saudi Arabia", "Singapore",
                     "South Korea", "Sri Lanka", "Taiwan", "Thailand") ~ "Asia",
      country == "Turkey" ~ "Europe", 
      country %in% c("Australia", "New Zealand") ~ "Oceania", TRUE ~ NA_character_))


country_emotions_clean = country_emotions_clean %>% 
  mutate(country = factor(country)) %>% 
   mutate(mean_feeling = rowMeans(across(interest:compassion), na.rm = TRUE)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))



country_emotions_clean_pos = country_emotions_clean %>% 
  select(ResponseId, country, continent, all_of(positive_feelings)) %>% 
  mutate(mean_feeling = rowMeans(across(interest:compassion), na.rm = TRUE)) 



country_emotions_clean_neg = country_emotions_clean %>% 
  select(ResponseId, country, continent, all_of(negative_feelings)) %>% 
  mutate(mean_feeling = rowMeans(across(sadness:anger), na.rm = TRUE)) %>% 
  mutate(NAcount = rowSums(is.na(across(sadness:anger)))) %>% 
   mutate(across(sadness:anger, ~ 8 - .x)) %>% 
  filter(!(NAcount > 5)) %>% 
  mutate(mean_feeling = rowMeans(across(sadness:anger), na.rm = TRUE))

## Prepare data for piecharts for comparison - overall emotional landscape dominated by mostly positive or negative emotions 
### prepare data -> positive, negative emotional averages

averages_data <- data_recoded %>% 
  select(
    -Progress, -Duration, -Finished, -dismiss_1, 
  ) %>% 
  mutate(
    across(interest:anger, as.numeric), 
    pos_mean = rowMeans(across(interest:compassion), na.rm = T), 
    neg_mean = rowMeans(across(sadness:anger), na.rm = T), 
    across(pos_mean:neg_mean, ~ na_if(., NaN))
  ) %>% 
  select(
    ResponseId, research_stage, interest:anger, category_of_work, position, area, age, country, country_other, pos_mean, neg_mean, gender
  )

## filter: average intensity of emotions is higher regarding the negative emotions
negative_means <- averages_data %>% 
  filter(
    (pos_mean < neg_mean), 
    !is.na(pos_mean), 
    !is.na(neg_mean) 
  )
```

# 1. Study description, descriptives
```{r}
data_recoded$Status <- ifelse(data_recoded$Finished,
                         "Completed",
                         "Not Completed")
plot_distribution_categorical(data_recoded, "Status", "Questionnaire Completion")
```

## 1.1. Distributions
### Gender distribution - Men and Women
```{r}
# The plot is hard to read, I suggest cleaning the labels

plot_distribution_categorical(
  data_recoded,
  "gender",
  "Participant Gender Distribution",
  custom_levels = c(
    "Man",
    "Woman"))
```

### Research area distribution
```{r}
plot_distribution_categorical(data_recoded, "area", "Participants by Research Area")
```

### Research stage distribution
```{r}
plot_distribution_categorical(
  data_recoded,
  "research_stage",
  "Participants by Research Stage",
  remove_parentheses = TRUE
)
```

### Position distribution
```{r}
plot_distribution_categorical(data_recoded, "position", "Participants by Position")
```

### Work distribution
```{r}
plot_distribution_categorical(data_recoded, "category_of_work", "Participants by Category of Work")
```


### Age distribution
```{r}
df_age <- data_recoded %>%
  mutate(
    age = as.numeric(age)
  ) %>%
  filter(!is.na(age))

ggplot(df_age, aes(x = age)) +
  geom_histogram(binwidth = 1, color = "white") +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_y_continuous(breaks = seq(0, 50, by = 5)) +
  labs(
    title = "Age Distribution of Participants",
    x = "Age",
    y = "Number of Participants"
  ) +
  theme_minimal (base_size = 14)

mean_age <- mean(df_age$age)
sd_age <- sd(df_age$age)
median_age <- median(df_age$age, na.rm = TRUE)
min_age <- min(df_age$age, na.rm = TRUE)
max_age <- max(df_age$age, na.rm = TRUE)

mean_age
sd_age
median_age
min_age
max_age
```

### Questionnaire dropout spikes
```{r}
df_dropout <- data_recoded %>%
  mutate(Progress = as.numeric(Progress)) %>%
  filter(!is.na(Progress), Progress < 100)

df_dropout_counts <- df_dropout %>%
  count(Progress) %>%
  arrange(Progress) %>%
  mutate(
    Progress = factor(Progress, levels = Progress)
  )

mean_progress <- mean(df_dropout$Progress, na.rm = TRUE)
sd_progress   <- sd(df_dropout$Progress, na.rm = TRUE)

mean_progress
sd_progress

ggplot(df_dropout_counts, aes(x = Progress, y = n)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = n),
            vjust = -0.4,
            size = 4) +
  labs(
    title = "Dropout Points Across Questionnaire",
    x = "Progress (%) at Dropout",
    y = "Number of Participants"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(),
    axis.title = element_text(),
    axis.text.x = element_text()
  )

```

### Country distribution - World map
```{r}
df_country_map <- data_recoded %>%
  mutate(country = ifelse(country == "" | is.na(country), NA, country)) %>%
  filter(!is.na(country)) %>%
  count(country) %>%
  mutate(country = tolower(country),
         country = dplyr::case_when(
           country == "united states of america" ~ "usa",
           country == "united kingdom of great britain and northern ireland" ~ "uk",
           TRUE ~ country
         ))

world_map <- map_data("world") %>%
  mutate(region = tolower(region))

world_data <- left_join(world_map, df_country_map, by = c("region" = "country"))

ggplot(world_data, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = n), color = "white", linewidth = 0.1) +
  scale_fill_gradient(
    low = "#deebf7",
    high = "#08519c",
    na.value = "grey95"
  ) +
  labs(
    title = "Participants by Country",
    fill = "Participants"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank()
)
```

```{r}
df_country_ranked <- df_country_map %>%
  arrange(desc(n))

df_country_ranked
```

## 1.2. SD in emotions
```{r}
## flag where SD of emotions are > 1 
sd_flag <- data_recoded %>% 
  select(
    -Progress, -Duration, -Finished, -dismiss_1, -Q22, -Q22_6_TEXT 
  ) %>% 
  mutate(across("interest":"anger", as.numeric),
         mean_landscape = rowMeans(across("interest":"anger"), na.rm = T),
         sd_landscape = apply(across("interest":"anger"), 1, sd, na.rm = T)) %>% 
  filter(
    !(is.na(mean_landscape)),
    !(is.na(sd_landscape)), 
    !(is.nan(mean_landscape))
  )

## sd smaller than 0.9 -> emotional landscape lacks dimension
small_sd <- sd_flag %>% 
  filter(
    sd_landscape < 0.9
  )

## exporative: greater sd, potential reasons??
great_sd <- sd_flag %>% 
  filter(
    sd_landscape > 2.5
  )
```


# 2. Research stage

## 2.1. Intensity of specific emotions across research stages - version A
```{r}
color_vector = c(
  "Project genesis" = "#750600",
  "Reality check" = "#D15B00",
  "Preparations" = "#D1B200",
  "Data collection" = "#007519",
  "Data analysis" = "#00A393",
  "Report writing" = "#005ED6",
  "Revisions" = "#2b4a78",
  "Waiting" = "#892EFF",
  "Post-project stage" = "#75069D")

original_order = c(
  "Project genesis",
  "Reality check",
  "Preparations",
  "Data collection",
  "Data analysis",
  "Report writing",
  "Revisions",
  "Waiting",
  "Post-project stage")

plots_emotions_stages = list()

data_recoded <- data_recoded %>% 
  mutate(
    research_stage = factor(research_stage, levels = original_order))

for (stage in levels(na.omit(data_recoded$research_stage))) {
  stage_data <- data_recoded %>% 
    filter(research_stage == stage) %>% 
    analysis_select() %>% 
    longer_heatmap() %>% 
    sum_analysis()
  
  plot <- stage_data %>% 
    plot_overall() + 
    labs(
      title = paste("Overall intensity of emotions in the", stage, "stage")
    ) 
  
  plots_emotions_stages[[stage]] <- plot 
  
  print(plot)
}


plots_heatmap_stages <- list()

for (stage in unique(na.omit(data_recoded$research_stage))) {

  stage_data <- data_recoded %>%
    filter(research_stage == stage) %>%
    analysis_select()
  
  stage_heatmap <- stage_data %>% 
    longer_heatmap()
  
  plot <- stage_heatmap %>%
    heatmap_plot() +
    scale_fill_gradient(
      low = "white", 
      high = color_vector[stage], 
      limits = c(0, 7)) +
    labs(
      title = paste("Intensity of emotions on the level of participants in the", stage, "stage")
    )

  plots_heatmap_stages[[stage]] <- plot 

  print(plot) 
}

plots_emotions_stages
plots_heatmap_stages
```

## 2.1. Combining the overall intensity and heatmap plots into an animated plot: using magick
```{r}
# 1. overall emotional intensity 
imgs_overall <- lapply(plots_emotions_stages, function(single_overall_plot) {
  img_overall <- image_graph(width = 800, height = 600, res = 96) ## saving the plots as magick images
  print(single_overall_plot)
  dev.off()
  img_overall
})

## animate plots into one object
animation_overall <- image_animate(
  image_join(imgs_overall), 
  fps = 1
)

## save overall emotional plots
image_write(animation_overall, "emotions_stages_animation.gif", format = "gif")

# 2. heatmaps 
imgs_heatmap <- lapply(plots_heatmap_stages, function(single_heatmap) {
  img_heatmap <- image_graph(width = 800, height = 600, res = 96)
  print(single_heatmap)
  dev.off()
  img_heatmap
})

animation_heatmap <- image_animate(
  image_join(imgs_heatmap), 
  fps = 1
)

animation_heatmap
```


## 2.2. Intensity of specific emotions across research stages - version B
```{r}
original_order = c(
  "Project genesis/ first thoughts/ idea creation",
  "Reality check",
  "Preparations",
  "Data collection",
  "Data analysis",
  "Report writing",
  "Revisions",
  "Waiting",
  "Post-project stage")

for (feeling in feeling_cols) {
  feeling_data <- data_recoded %>%
    select(all_of(c(feeling, "research_stage"))) %>%
    filter(!is.na(.data[[feeling]])) %>%
    group_by(research_stage)}


plots_specfeeling <- list()

for (feeling in feeling_cols) {

  feeling_distribution <- data_recoded %>% 
    select(all_of(c(feeling, "research_stage"))) %>% 
    filter(!is.na(.data[[feeling]])) %>%
    group_by(research_stage) %>%
    mutate(research_stage = factor(research_stage, levels = original_order))

  plots_specfeeling[[feeling]] <- feeling_distribution %>% 
    ggplot(aes(x = research_stage, y = .data[[feeling]])) +
    geom_col(fill = "#B5E6D0", na.rm = TRUE) +
    labs(
      title = paste("Intensity of", feeling, "through the research stages")) +
    theme(
      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)
    )
}

plots_specfeeling

```

## 2.3. Intensity of specific emotions across research stages - version C
```{r}
all_distribution <- data_recoded %>% 
  select(
    research_stage, interest:anger
  ) %>% 
  filter(!(is.na(research_stage))) %>% 
  mutate(
    research_stage = stringr::str_trunc(research_stage, 20)) %>% 
  group_by(research_stage) %>% 
  summarise(
    across(
      all_of(feeling_cols), 
      ~ round(mean(.x[.x != 0], na.rm = T), 3)
    )
  ) %>% 
  pivot_longer(
    cols = all_of(feeling_cols),
    names_to = "emotion", 
    values_to = "intensity"
  ) %>% 
  mutate(
    emotion = factor(emotion, levels = feeling_cols)
  )

all_distribution %>% 
  ggplot(aes(x = research_stage, y = intensity)) +
  geom_col(fill = "#84CDF0", na.rm = T
    ) +
    labs(
      title = "Intensity of all emotions through the research stages") +
    theme(
      axis.text.x = element_text(angle = 
                                   45, vjust = 1, hjust = 1, size = 6)) +
  facet_wrap(~ emotion, nrow = 3) 


```


## 2.4. Post-project stage
```{r}
post_project <- data_recoded %>% 
  filter(
    research_stage == "Post-project stage"
  ) %>% 
  select(-dismiss_1) 

# 4.1. accepted and published - mean intensity of emotions
post_project1 <- post_project %>%  
  filter(
    Q22 == "Accepted and published"
  ) %>% 
  select(-Q22_6_TEXT) 

post_project1_long <- post_project1 %>% 
  longer_heatmap() %>% 
  sum_analysis()

# geom_col for mean intensity
post_project1_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Accepted and published", 
      tag = "4.1.")
# most intense emotions if the article was accepted and published: interest, joy, pride, pleasure, relief, contentment (+ admiration, amusement)

# 4.2. Accepted but not yet published
post_project2 <- post_project %>% 
  filter(
    Q22 == "Accepted but not yet published"
  ) %>% 
  select(-Q22_6_TEXT)


post_project2_long <- post_project2 %>% 
  longer_heatmap() %>% 
  sum_analysis()

# geom_col for mean intensity
post_project2_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Accepted but not yet published", 
      tag = "4.2.")

## 4.3. Rejected (rejected and abandoned, rejected and being revised, rejected and postponed)
post_project3 <- post_project %>% 
  filter(
    Q22 %in% c("Rejected and abandoned", "Rejected and being revised", "Rejected and postponed")
  ) %>% 
  select(-Q22_6_TEXT)

post_project3_long <- post_project3 %>% 
  longer_heatmap() %>%
  sum_analysis()

post_project3_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Rejected", 
      tag = "4.3.")
```

## 2.5. facet_wrap plot for emotional intensity in all research stages
```{r}
head(data_recoded)
overall_intensity <- data_recoded %>% 
  select(
    -Q22, -Q22_6_TEXT, -cause_stage, -dismiss_1, -Finished, -Progress, -Duration, -cause_general
  ) %>% 
  arrange(research_stage)

# create plot of overall emotions
## 1. long format
overall_long <- overall_intensity %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity") %>% 
  mutate(intensity = as.numeric(intensity), 
         emotion = factor(emotion, levels = unique(emotion))) %>% 
  group_by(research_stage, emotion) %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T), .groups = "drop") %>% 
  filter(!(is.na(research_stage)))

# create plot 
ggplot(overall_long, aes(x = emotion, y = mean_intensity, fill = intensity)) +
  facet_wrap(~ research_stage, nrow = 3) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#c6a1f9", na.rm = T
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") 

```


## 2.6. Na values in specific emotions across research stages
```{r}
## df for counting NA values by research stage
na_counter <- data_recoded %>% 
  filter(!(is.na(research_stage))) %>% 
  select(
    ResponseId, interest:anger, research_stage
  ) %>% 
  group_by(research_stage) %>% 
  summarise(
    across(interest:anger, ~ sum(is.na(.))))

## Data analysis stage - long format for the barchart
data_analysis_na <- na_counter %>% 
  filter(research_stage == "Data analysis") %>% 
  pivot_longer(
    cols = -research_stage, 
    names_to = "emotion", 
    values_to = "na_count"
  )

## -> Barchart
data_analysis_na %>% 
  ggplot(aes(emotion, na_count)) +
  geom_bar(stat = "identity", fill = "#34B3E0") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") +
  labs(
      title = "NA values in the Data Analysis stage")

## All stages -> facet_wrap
na_all <- na_counter %>%
  pivot_longer(
    cols = -research_stage, 
    names_to = "emotion", 
    values_to = "na_count"
  )

## -> Barchart for all stages
na_all %>% 
  mutate(emotion = factor(emotion, levels = unique(emotion))) %>%
  mutate(research_stage = factor(research_stage, levels = c("Project genesis/ first thoughts/ idea creation",
  "Reality check","Preparations","Data collection","Data analysis","Report writing","Revisions","Waiting","Post-project stage"))) %>% 
  ggplot(aes(emotion, na_count)) +
  facet_wrap(
    ~ research_stage) +
  geom_bar(stat = "identity", fill = "#8DB5E0") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") +
  labs(
      title = "NA values in the research stages")

```

## 2.7 Overall emotional landscape across research stages
```{r}
research_stage_emotions = data_recoded %>% 
  select(research_stage, all_of(feeling_cols)) %>% 
  filter(!(research_stage == "")) %>% 
    mutate(across(sadness:anger, ~ 8 - .x))
research_stage_emotions_positive = research_stage_emotions %>% 
  select(research_stage, all_of(positive_feelings))
research_stage_emotions_negative = research_stage_emotions %>% 
  select(research_stage, all_of(negative_feelings)) %>% 
    mutate(across(sadness:anger, ~ 8 - .x))

research_stage_na = Nacount(data_recoded, research_stage) %>% 
  filter(!(is.na(research_stage)))
na_prop_diverging_plot(research_stage_na, research_stage, "Proportion of NA's in Positive and Negative Emotions")

research_stage_emotions = emotion_function(research_stage_emotions, research_stage)

research_stage_emotions_mean = mean_function(research_stage_emotions, research_stage)

research_stage_emotions_positive = emotion_function(research_stage_emotions_positive, research_stage)

research_stage_emotions_mean_positive = mean_function(research_stage_emotions_positive, research_stage)

research_stage_emotions_negative = emotion_function(research_stage_emotions_negative, research_stage)

research_stage_emotions_mean_negative = mean_function(research_stage_emotions_negative, research_stage)


research_stage_pos = overall_emotion_plot_valence(
  research_stage_emotions_mean_positive,
  research_stage,
  mean_emotion,
  color_low = "orange",
  color_high = "red",
  "Positive Emotions"
)

research_stage_neg = overall_emotion_plot_valence(
  research_stage_emotions_mean_negative,
  research_stage,
  mean_emotion,
  color_low = "lightblue",
  color_high = "blue",
  "Negative Emotions"
)

overall_emotion_plot(
  research_stage_emotions_mean,
  research_stage,
  mean_emotion,
  "Overall Emotional Landscape by Research Stage")

combined_research_stage = research_stage_pos + research_stage_neg
research_stage_neg 
research_stage_pos
combined_research_stage
```

## 2.8 Emotional landscape across research stages in chronological order
```{r}

original_order = c(
  "Project genesis",
  "Reality check",
  "Preparations",
  "Data collection",
  "Data analysis",
  "Report writing",
  "Revisions",
  "Waiting",
  "Post-project stage")



research_stage_emotion_chron1 =
  left_join(
    research_stage_emotions_mean_positive,
    research_stage_emotions_mean_negative,
    by = "research_stage"
  ) %>%
  rename(
    mean_emotion_pos = mean_emotion.x,
    mean_emotion_neg = mean_emotion.y
  )

chron_long <- research_stage_emotion_chron1 %>%
  pivot_longer(
    cols = c(mean_emotion_pos, mean_emotion_neg),
    names_to = "valence",
    values_to = "mean_emotion"
  ) %>% 
  mutate(research_stage = factor(research_stage, levels = original_order))



chron_plot <- chron_long %>%
  ggplot(aes(x = research_stage,
             y = mean_emotion,
             color = valence,
             group = valence)) +
  geom_line() +
  geom_point(size = 3) +
  scale_color_manual(
    values = c(
      mean_emotion_pos = "red",
      mean_emotion_neg = "blue"
    )
  ) +
  labs(title = "Positive vs Negative Emotions") +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
  scale_y_continuous(
  limits = c(0, 7),
  breaks = 0:7
)


chron_plot  
```

## 2.9.  NA values in emotions across research stages
```{r}
# df for counting NA values by research stage
na_counter_all <- data_recoded %>% 
  group_by(ResponseId) %>% 
  summarise(
    across(interest:anger, ~ sum(is.na(.)))) %>% 
  mutate(sum_na_feelings = rowSums(across(interest:anger)))
```

## 2.10. Distributions: overall emotional landscape dominated by positive or negative emotions - comparison
### 2.10.1. Negative emotions more dominant - prepare dataset, create piechart
```{r}

stage_negative <- negative_means %>% 
  rename(category = research_stage) %>% ## rename column for functions 
  mutate(category = as.character(category)) %>% 
  mutate(category = ifelse(category == "Project genesis/ first thoughts/ idea creation", "Project genesis", category)) %>% 
  categories_prepare() %>% 
  mutate(category = as.factor(category))
  

## piechart plot
stage_negative_piechart <- stage_negative %>% 
  piechart_plot(legend_name = "Research stage") + 
  labs(title = "Negative emotions more dominant") +
   theme(legend.position = "bottom", legend.justification = "left")
  
stage_negative_piechart
```

### 2.10.2. Positive emotions more dominant -> prepare df, create piechart
```{r}
positive_means <- averages_data %>% 
  filter(
    ((pos_mean > neg_mean) | is.na(neg_mean)), 
    !is.na(pos_mean)
  ) 

stage_positive <- positive_means %>% 
  rename(category = research_stage) %>% ## rename column for functions 
  categories_prepare()
  

## piechart plot
stage_positive_piechart <- stage_positive %>% 
  piechart_plot(legend_name = "Research stage") +
  labs(title = "Positive emotions more dominant") + 
  theme(legend.position = "none")

```

### 2.10.3. Combining the piecharts for comparison
```{r}
stage_piecharts <- (stage_negative_piechart + stage_positive_piechart)

stage_piecharts +
  plot_annotation(title = "Overall intensity of emotions within the different research stages")
```

# 3. Gender
## 3.1. Intensity of emotions
```{r}
genders_emotions = data_recoded %>%
  filter(
    gender %in% c("Woman", "Man")
  ) %>% 
  select(
    -Finished, -Duration, -Progress, -dismiss_1, -cause_stage, -cause_general, -Q22, -Q22_6_TEXT
  ) %>% 
  select(
    -category_of_work, -research_stage, -feeling_general_1, -position, -area, -age, -country, -country_other) %>% 
  rename(
    positive = c("interest", "amusement", "pride", "joy", "pleasure", "contentment", "love", "admiration", "relief", "compassion"), 
    negative = c("sadness", "guilt", "regret", "shame", "disappointment", "fear", "disgust", "contempt", "hate", "anger"))

genders_long <- genders_emotions %>%
  pivot_longer(
    cols = positive1:negative10,
    names_to = "valence",
    values_to = "intensity",
    values_transform = list(intensity = as.numeric)) %>% 
  mutate(valence = factor(valence,
                          levels = unique(valence)))

genders_wide <- genders_long %>%
  pivot_wider(
    names_from = "valence", 
    values_from = "intensity"
  ) %>% 
  mutate(
    positive_mean = rowMeans(select(., positive1:positive10), na.rm = T), 
    negative_mean = rowMeans(select(., negative1:negative10), na.rm = T)
  ) %>% 
  filter(
    !(is.na(negative_mean)), 
    !(is.nan(positive_mean))
  )
  
summary_genders <- genders_wide %>% 
  group_by(gender) %>% 
  summarise(
    positive = mean(positive_mean),
    negative = mean(negative_mean)
  ) %>% 
  pivot_longer(
    cols = c("positive", "negative"),
    names_to = "valence", 
    values_to = "intensity"
  )
```

```{r}
ggplot(summary_genders,
       aes(x = valence, y = intensity)) +
  facet_wrap(~ gender) +
  geom_col(
    fill = "#c6a"
  ) + 
  labs(
    x = "Valence", 
    y = "Mean intensity", 
    title = "Emotional intensity between men and women" 
  ) +
  theme_minimal()

```

## 3.2. Overall emotional landscape across genders

```{r}
# overall emotions visualization by gender
gender_emotions = data_recoded%>% 
  select(gender, all_of(feeling_cols)) %>% 
  filter(!(gender %in% c("Non-binary / third gender / gender non-conforming", NA, "Prefer not to say")))
gender_emotions = gender_emotions %>% 
  mutate(gender = factor(gender)) %>% 
    mutate(across(sadness:anger, ~ 8 - .x))
gender_emotions_positive = gender_emotions %>% 
  select(gender, all_of(positive_feelings))
gender_emotions_negative = gender_emotions %>% 
  select(gender, all_of(negative_feelings)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))

gender_na = Nacount(data_recoded, gender) %>% 
  filter(!(gender %in% c(NA, "Non-binary / third gender / gender non-conforming", "Prefer not to say")))
na_prop_diverging_plot(gender_na, gender, "Proportion of NA's in Positive and Negative Emotions")


gender_emotions = emotion_function(gender_emotions, gender)

gender_emotions_mean = mean_function(gender_emotions, gender)

gender_emotions_positive = emotion_function(gender_emotions_positive, gender)

gender_emotions_mean_positive = mean_function(gender_emotions_positive, gender)

gender_emotions_negative = emotion_function(gender_emotions_negative, gender)

gender_emotions_mean_negative = mean_function(gender_emotions_negative, gender)


gender_pos = overall_emotion_plot_valence(gender_emotions_mean_positive, gender, mean_emotion, color_low = "orange", color_high = "red",
                             "Positive Emotions")

gender_neg = overall_emotion_plot_valence(gender_emotions_mean_negative, gender, mean_emotion, color_low = "lightblue", 
                     color_high = "blue", "Negative Emotions")

overall_emotion_plot(gender_emotions_mean, gender, mean_emotion,
                             "Overall Emotional Landscape by Gender")
combined_gender = gender_pos+gender_neg

combined_gender
```


## 3.3. Distributions: emotional landscapes dominated by mainly negative or positive emotions: Age-gender distributions 
### 3.3.1. Negative emotions more dominant - preparing data, saving plot as an object
```{r}
## classifying the data types of columns
age_negative <- negative_means %>%
  pos_neg_classify() ## age: as_numeric, gender: as_factor, filter if age of gender is NA

## creating age groups
age_negative_counts <- age_negative %>% 
  age_grouping() %>% ## age groups, from 20-100 years, by 10 years
  droplevels()

## pyramid to explore the age distribution, split by gender 
negative_age_plot <- pyramid_plot(age_negative_counts) +
  labs(title = "Overally negative emotions")
```

### 3.3.2. Positive emotions more dominant - prepare data, save plot as an object
```{r}
positive_means <- averages_data %>% 
  filter(
    ((pos_mean > neg_mean) | is.na(neg_mean)), 
    !is.na(pos_mean)
  ) 

## classifying the data types of columns
age_positive <- positive_means %>%
  pos_neg_classify()

## creating age groups
age_positive_counts <- age_positive %>% 
  age_grouping() %>% 
  droplevels()

## creating the age pyramid
positive_age_plot <- pyramid_plot(age_positive_counts) +
  labs(title = "Overally positive emotions")
```

### 3.3.3. Combining the two age pyramids for comparison
```{r}
age_comparisons <- positive_age_plot | negative_age_plot

age_comparisons +
  plot_annotation(title = "Age distributions")
```

# 4. Category_of_work
## Distributions: overall emotional landscape dominated by mostly positive or negative emotions 
## 4.1. Negative emotions more dominant -> prepare data, create piechart
```{r}
work_negative <- negative_means %>% 
  rename(category = category_of_work) %>% ## rename column for the functions
  categories_prepare()

## pie chart for the distribution of the categories
work_negative_piechart <- work_negative %>% 
  piechart_plot(legend_name = "Category of work") +
  labs(title = "Negative emotions more dominant") +
   theme(legend.position = "bottom", legend.justification = "left")
```
## 4.2. Positive emotions more dominant -> create piechart, prepare data
```{r}
work_positive <- positive_means %>% 
  rename(category = category_of_work) %>% ## rename column for the functions
  categories_prepare()

## pie chart for the distribution of the categories
work_positive_piechart <- work_positive %>% 
  piechart_plot(legend_name = "Category of work") + 
  labs(title = "Positive emotions more dominant") +
  theme(legend.position = "none")

work_positive_piechart
```
## 4.3. Combine two piecharts
```{r}
work_piecharts <- (work_negative_piechart + work_positive_piechart)

work_piecharts +
  plot_annotation(title = "Overall intensity of emotions within the different categories of work")
```

# 5. Area
## 5.1. Distributions: emotional landscapes dominated by mainly negative or positive emotions
### 5.1.1. Negative emotions more dominant than positive emotions -> prepare dataset, create piechart 
```{r}
area_negative <- negative_means %>% 
  rename(category = area) %>% ## rename column for the functions
  categories_prepare() 

area_negative_piechart <- piechart_plot(area_negative, legend_name = "Research area") + 
  labs(title = "Negative emotions more dominant") +
   theme(legend.position = "bottom", legend.justification = "left")

area_negative_piechart
```

### 5.1.2. Positive emotions more dominant than negative emotions -> prepare dataset, create piechart 
```{r}
area_positive <- positive_means %>% 
  rename(category = area) %>% ## rename column for the functions
  categories_prepare()

area_positive_piechart <- piechart_plot(area_negative, legend_name = "Research stage") + 
  labs(title = "Positive emotions more dominant") +
  theme(legend.position = "none")

area_positive_piechart
```

### 5.1.3. Combine piecharts 
```{r}
area_piecharts <- (area_negative_piechart + area_positive_piechart) 

area_piecharts +
  plot_annotation(title = "Overall intensity of emotions within the different research areas")

## percentages are the same - causes?? 
```

### 5.2 Overall emotional landscape by area
```{r}
area_emotions = data_recoded %>% 
  select(area, all_of(feeling_cols)) %>% 
  filter(!(area == "")) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))
area_emotions_positive = area_emotions %>%
select(area, all_of(positive_feelings))
area_emotions_negative = area_emotions %>% 
  select(area, all_of(negative_feelings))

area_na = Nacount(data_recoded, area) %>% 
  filter(!(area == ""))

na_prop_diverging_plot(
  area_na,
  area,
  "Proportion of NA's in Positive and Negative Emotions")
area_emotions = emotion_function(area_emotions, area)

area_emotions_mean = mean_function(area_emotions, area)

area_emotions_positive = emotion_function(area_emotions_positive, area)

area_emotions_mean_positive = mean_function(area_emotions_positive, area)

area_emotions_negative = emotion_function(area_emotions_negative, area)

area_emotions_mean_negative = mean_function(area_emotions_negative, area)


area_pos = overall_emotion_plot_valence(
  area_emotions_mean_positive,
  area,
  mean_emotion,
  color_low = "orange",
  color_high = "red",
  "Positive Emotions"
)

area_neg = overall_emotion_plot_valence(
  area_emotions_mean_negative,
  area,
  mean_emotion,
  color_low = "lightblue",
  color_high = "blue",
  "Negative Emotions"
)


overall_emotion_plot(
  area_emotions_mean,
  area,
  mean_emotion,
  "Overall Emotional Landscape by Area"
)

combined_area = area_pos + area_neg

combined_area


```

# 6. Position
## 6.1. Distributions: emotional landscapes dominated by mainly negative or positive emotions
### 6.1.1. Negative emotions more dominant - prepare data, create piechart
```{r}
position_negative <- negative_means %>%
  rename(category = position) %>% ## rename column for functions
  categories_prepare() ## counting the numbers of unique values in the subgroups of the category (in this case, the numbers of people in the different positions), creating the percentage of each subgroup in the category

## pie chart for the distribution of positions
piechart_position_negative <- position_negative %>% 
  piechart_plot(legend_name = "Position") +
  labs(
    title = "Negative emotions more dominant"
  ) +
  theme(legend.position = "bottom", legend.justification = "left")

piechart_position_negative
```

### 6.1.2. Positive emotions more dominant - create piechart 
```{r}
position_positive <- positive_means %>%
  rename(category = position) %>% ## rename column for functions
  categories_prepare()

## pie chart for the distribution of positions
piechart_position_positive <- position_positive %>%
  piechart_plot(legend_name = "position")+
  labs(title = "Positive emotions more dominant")+
  theme(legend.position = "none")

```

### 6.1.3. Combine two piecharts for comparison
```{r}
piechart_position <- (piechart_position_negative + piechart_position_positive)


piechart_position +
  plot_annotation(title = "Overall intensity of emotions within the positions")
```

## 6.2. Overall emotional landscape by position
```{r}
position_emotions = data_recoded %>% 
  filter(!(position == "")) %>% 
  select(position, all_of(feeling_cols)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))
position_emotions_positive = position_emotions %>%
  select(position, all_of(positive_feelings))
position_emotions_negative = position_emotions %>% 
  select(position, all_of(negative_feelings)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))

position_na = Nacount(data_recoded, position) %>% 
  filter(!(position == ""))

na_prop_diverging_plot(
  position_na,
  position,
  "Proportion of NA's in Positive and Negative Emotions")


position_emotions = emotion_function(position_emotions, position)

position_emotions_mean = mean_function(position_emotions, position)

position_emotions_positive = emotion_function(position_emotions_positive, position)

position_emotions_mean_positive = mean_function(position_emotions_positive, position)

position_emotions_negative = emotion_function(position_emotions_negative, position)

position_emotions_mean_negative = mean_function(position_emotions_negative, position)


position_pos = overall_emotion_plot_valence(
  position_emotions_mean_positive,
  position,
  mean_emotion,
  color_low = "orange",
  color_high = "red",
  "Positive Emotions"
)

position_neg = overall_emotion_plot_valence(
  position_emotions_mean_negative,
  position,
  mean_emotion,
  color_low = "lightblue",
  color_high = "blue",
  "Negative Emotions"
)


overall_emotion_plot(
  position_emotions_mean,
  position,
  mean_emotion,
  "Overall Emotional Landscape by Position"
)

position_combined = position_pos + position_neg
position_combined
```

# 7. Combined df of means - Research stage, gender, area, position

## 7.1. DF mean emotions combined
```{r}
combined_emotions <- bind_rows(
  area_emotions_mean %>% 
    mutate(group = "Area",
           category = area),
  
  position_emotions_mean %>% 
    mutate(group = "Position",
           category = position), 
  
  gender_emotions_mean %>% 
    mutate(group = "Gender", 
           category = gender), 
  
  research_stage_emotions_mean %>% 
    mutate(group = "Research Stage",
           category = research_stage)
) %>% 
  select(group, category, mean_emotion)
```


# 8. Country, regions
## 8.1. Overall emotional landscape region-wise
```{r}
continents <- c("Europe", "Africa", "Asia", "North America", "South America/ Central America", "Oceania")


continent_results <- list()

for (cont in continents) {
  continent_results[[cont]] <- continent_emotions_mean_function(country_emotions_clean, cont)
}

continent_plots <- list()

for (cont in continents) {
  
  temp_data = continent_emotions_mean_function(country_emotions_clean, cont)
  
  continent_plots[[cont]] = continent_plot_function(
    temp_data,
    title_text = paste("Overall emotional landscape in", cont))}


continent_results
continent_plots
```


## 8.2. Intensity of positive emotions region-wise
```{r}
#Positive
continent_results_pos = list()
continent_plots_pos = list()

for (cont in continents) {
  
  temp_data = continent_emotions_mean_function_pos(country_emotions_clean_pos, cont)
  
  continent_results_pos[[cont]] = temp_data
  
  continent_plots_pos[[cont]] = continent_plot_function_valence(
    temp_data,color_low = "orange",color_high = "red",
    title_text = paste("Positive Emotions in", cont))}
continent_plots_pos

```



## 8.3. Intensity of negative emotions region-wise
```{r}
#Negative
continent_results_neg = list()
continent_plots_neg = list()

for (cont in continents) {
  
  temp_data = continent_emotions_mean_function_neg(country_emotions_clean_neg, cont)
  
  continent_results_neg[[cont]] = temp_data
  
  continent_plots_neg[[cont]] = continent_plot_function_valence(
    temp_data,color_low = "lightblue",color_high = "blue",
    title_text = paste("Negative Emotions in", cont))}

continent_results_neg
continent_plots_neg
```


## 8.4. Combined plots
```{r}
combined_plots = Map(`+`, continent_plots_pos, continent_plots_neg) #The map goes through the two vectors in parallel --> given they contain plots, the combined plots are this easy to create

combined_plots
```



## 8.5. Countries with the top 10 most respondents
```{r}
#based on frequency
top10_countries <- country_emotions_clean %>% 
  count(country, sort = TRUE) %>% 
  slice_head(n = 10) %>% 
  pull(country)

country_11_groups <- country_emotions_clean %>% 
  mutate(
    country_group = if_else(
      country %in% top10_countries,
      country,
      "Other countries")) %>% 
  group_by(country_group) %>% 
  summarise(
    mean_emotion = mean(mean_feeling, na.rm = TRUE),
    n = n(),   # optional, but nice to keep
    .groups = "drop")

country_11_groups %>% 
  mutate(dev = mean_emotion - 4) %>% 
  arrange(desc(n)) %>%   # arrange by frequency
  ggplot(aes(
    y = reorder(country_group, ifelse(country_group == "Other countries", -Inf, n)),
    x = dev,
    fill = mean_emotion)) +
  geom_col(width = 0.3) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(
    limits = c(-3, 3),
    breaks = -3:3,
    labels = 1:7) +
  scale_fill_gradient(low = "orange", high = "red") +
  theme_tufte() +
  labs(
    title = "Overall emotional landscape – top 10 countries with the most responses vs others", x = "", y = "" ) +
  theme(
    axis.text.y = element_text(size = 11,),
    plot.title  = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none")+
  theme(axis.ticks.y = element_blank())
```


## 8.6. Country mapping with at least 10 respondents from the given country 
```{r}
country_emotions_min10 = country_emotions_clean %>% 
  mutate(country = factor(country)) %>% 
  group_by(country) %>% 
  filter(n() >= 10) %>% 
  ungroup() 

min10_emotions = emotion_function(country_emotions_min10, country)
min10_mean = mean_function(min10_emotions, country)

min10_plot = overall_emotion_plot(min10_mean, country, mean_emotion, "Overall Emotional Landscape in Countries with at least 10 Respondents")
min10_plot
```



# 9. Attributional analysis of general feeling

```{r}
df_feeling_general = data_recoded %>% 
  filter(!(cause_general %in% c("", "-", "na", "Na", "NA", "I don't know", "I dont know"))) %>% 
  filter(!(feeling_general_1 == 0)) %>% 
  select(ResponseId,feeling_general_1, cause_general ) %>% 
  mutate(valence = if_else(feeling_general_1 > 0, "positive", "negative"))

df_feeling_general<- df_feeling_general %>%
  mutate( attribution_category = case_when(
      
      str_detect(cause_general, regex("reviewer|editor|revision|reject|publication|journal", ignore_case = TRUE)) ~ "Peer Review",
      
      str_detect(cause_general, regex("data|analysis|results|insight|experiment|finding|discover", ignore_case = TRUE)) ~ "Data/Results",
      
      str_detect(cause_general, regex("project|employ|paper|\\bwork\\b", ignore_case = TRUE)) ~ "Project/Work-related",
      
      str_detect(cause_general, regex("ethic|bureaucr|paperwork|funding|NIH|permit|legal|funded|funding|job|employ", ignore_case = TRUE)) ~ "Institutional",
      
      str_detect(cause_general, regex("co-investigator|collaborat|team|mentor|colleague|supervisor|co-author|boss|\\bPI\\b|help", ignore_case = TRUE)) ~ "Collaboration",
      
      str_detect(cause_general, regex("deadline|timeline|pressure|workload|slow|delay", ignore_case = TRUE)) ~ "Time Pressure",
      
      str_detect(cause_general, regex("guilt|fear|self|my fault|competence|fail|underperform", ignore_case = TRUE)) ~ "Self-Evaluation",
      
      str_detect(cause_general, regex("interest|fascinat|passion|exciting|love research|idea|pleasure|creative", ignore_case = TRUE)) ~ "Intrinsic Interest",
      
      str_detect(cause_general, regex("sexism|bias|underfund|peripheral|mobing|institution|racism|female|woman", ignore_case = TRUE)) ~ "Structural Inequality",
      
      str_detect(cause_general, regex("lonely|isolat", ignore_case = TRUE)) ~ "Isolation",
      
      TRUE ~ "Other/Unclear"
    ))

#Visualization
attribution_counts_general <- df_feeling_general %>%
  count(attribution_category) %>%
  mutate(prop = n / sum(n)) %>%
  arrange(prop)

ggplot(attribution_counts_general,
       aes(x = reorder(attribution_category, prop),
           y = prop)) +
  geom_col(width = 0.6) +
  coord_flip() +
  labs(title = "Overall Attribution of Research-Related Emotions",
       x = "",
       y = "Proportion of Responses") +
  theme_minimal(base_size = 13)

valence_counts_general <- df_feeling_general %>%
  count(valence, attribution_category) %>%
  group_by(valence) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

ggplot(valence_counts_general,
       aes(x = reorder(attribution_category, prop),
           y = prop,
           fill = valence)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~ valence) +
  scale_fill_manual(values = c(
    "positive" = "red",
    "negative" = "blue"
  )) +
  labs(
    title = "Attributional Factors by Emotional Valence",
    x = "",
    y = "Proportion within Valence"
  ) +
  theme_minimal(base_size = 13)
```

# 10. Saving plots

## 10.1. Research stage heatmaps
```{r}
for (stage in names(plots_heatmap_stages)) {

  ggsave(
    filename = paste0("heatmap_", gsub("[^A-Za-z0-9]", "_", stage), ".png"),
    plot = plots_heatmap_stages[[stage]],
    width = 8,
    height = 6
  )

} 
```

## 10.2. Emotions across stages
```{r}
for (stage in names(plots_emotions_stages)) {

  ggsave(
    filename = paste0("across_", gsub("[^A-Za-z0-9]", "_", stage), ".png"),
    plot = plots_emotions_stages[[stage]],
    width = 8,
    height = 6
  )

}
```


