---
title: '"Analysiscombined"'
author: "radibarbi, ludmanybogi, fejossandor"
date: "2026-02-28"
output: html_document
---

#load libraries
```{r}
# Updated library loading with checks for installation

if (!require("tidyverse")) install.packages("tidyverse")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("dplyr")) install.packages("dplyr")
if (!require("stringr")) install.packages("stringr")
if (!require("rstatix")) install.packages("rstatix")
if (!require("ggthemes")) install.packages("ggthemes")
if (!require("tidyr")) install.packages("tidyr")
if (!require("patchwork")) install.packages("patchwork")
if (!require("scales")) install.packages("scales")
if (!require("magrittr")) install.packages("magrittr")
if (!require("apyramid")) install.packages("apyramid")
if (!require("rlang")) install.packages("rlang")
if (!require("maps")) install.packages("maps")

library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(rstatix)
library(ggthemes)
library(tidyr)
library(patchwork)
library(scales)
library(magrittr)
library(apyramid)
library(rlang)
library(maps)
```


#data formatting, setup
```{r}
# Updated data loading with checks for missing data handling
source("functionscombined_new.R")
raw_data <- read.csv("raw_data.csv", na.strings = c("", "NA", "NaN"))

# Changed to data_clean for easier handling for next wrangling
data_clean = raw_data[-1:-2, ]

feeling_cols = c("interest","amusement","pride","joy","pleasure",
  "contentment","love","admiration","relief","compassion", "sadness", "guilt", "regret" ,"shame", 
                       "disappointment" , "fear", "disgust", "contempt" , "hate","anger")

positive_feelings <- c(
  "interest","amusement","pride","joy","pleasure",
  "contentment","love","admiration","relief","compassion"
)
negative_feelings <- c("sadness", "guilt", "regret" ,"shame", 
                       "disappointment" , "fear", "disgust", "contempt" , "hate","anger")
```

```{r}
data_recoded = data_clean %>% 
  rename(interest = feeling_stage_1,
         amusement = feeling_stage_2,
         pride = feeling_stage_3,
         joy = feeling_stage_4,
         pleasure = feeling_stage_5,
         contentment = feeling_stage_6,
         love = feeling_stage_7, 
         admiration = feeling_stage_8, 
         relief = feeling_stage_9, 
         compassion = feeling_stage_10,
         sadness = feeling_stage_11, 
         guilt = feeling_stage_12,
         regret = feeling_stage_13, 
         shame = feeling_stage_14, 
         disappointment = feeling_stage_15, 
         fear = feeling_stage_16, 
         disgust = feeling_stage_17, 
         contempt = feeling_stage_18,
         hate = feeling_stage_19, 
         anger = feeling_stage_20)%>% 
  mutate(research_stage = factor(research_stage), 
         area = factor(area),
         gender = factor(gender),
         position = factor(position), 
         category_of_work = factor(category_of_work), 
         ) %>% 
  mutate(research_stage = recode(research_stage,	
                                 "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)"
                                 = "Post-project stage", 
                                 "Preparations (IRB permit, preregistration, experiment preparations)" = 
                                   "Preparations",
                                 "Reality check (e.g., literature search, consultation with colleagues)" =
                                   "Reality check",
                                 "Waiting for journal's response and revisions" = "Waiting")) %>% 
  mutate(across(all_of(feeling_cols),
                ~ as.numeric(as.character(.x)))) %>% 
  mutate(feeling_general_1 = as.numeric(as.character(feeling_general_1))) %>% 
  filter(!(dismiss_1 == "No")) %>% 
  rename(Duration = `Duration..in.seconds.`) %>% 
  mutate(across(interest:anger, ~ na_if(.x, 0))) 

# Updated missing data handling, this is not needed as na.strings in read.csv handles this across the data
# %>% 
#   mutate(across(ResponseId:Q22_6_TEXT, ~ na_if(.x, ""))) %>% 
#   mutate(cause_stage = if_else(cause_stage == "", NA, cause_stage)) %>% 
#   mutate(across(cause_general:country_other, ~ na_if(.x, ""))) 
```


```{r}
# Why is this a new dataset? As I understand this is only for calculating missing values, if so you can just do this in the data_recoded dataset, no need to create a new one.
data_recoded_clean = data_recoded %>% 
  select(ResponseId,gender, position, research_stage, category_of_work,
         country, country_other, area, all_of(feeling_cols), feeling_general_1) %>% 
  mutate(across(interest:feeling_general_1, ~ na_if(.x, 0))) %>% 
  mutate(NAcount = rowSums(is.na(across(interest:anger)))) %>%
  mutate(NAcountpos = rowSums(is.na(across(interest:compassion)))) %>% 
  mutate(NAcountneg = rowSums(is.na(across(sadness:anger)))) %>% 
  mutate(across(sadness:anger, ~ 8 - .x)) %>% 
  filter(!if_all(all_of(feeling_cols), is.na)) %>% 
  select(-feeling_general_1) 

```

# ========================================================================================================
# Barbi
# ========================================================================================================

```{r}
# updated dataset to match the correct one
plot_distribution_categorical(data_recoded, "Status", "Questionnaire Completion")
```

```{r}
# The plot is hard to read, I suggest cleaning the labels

#gender distribution
plot_distribution_categorical(
  data_recoded,
  "gender",
  "Participant Gender Distribution",
  custom_levels = c(
    "Man",
    "Woman",
    "Non-binary / third gender / gender non-conforming",
    "Prefer not to say"
  )
)
```


```{r}
#research area distribution
plot_distribution_categorical(data_recoded, "area", "Participants by Research Area")
```


```{r}
#research stage distribution
plot_distribution_categorical(
  data_recoded,
  "research_stage",
  "Participants by Research Stage",
  remove_parentheses = TRUE
)
```


```{r}
#position distribution
plot_distribution_categorical(data_recoded, "position", "Participants by Position")
```

```{r}
#work distribution
plot_distribution_categorical(data_recoded, "category_of_work", "Participants by Category of Work")
```


```{r}
#Other distributions
#age distribution

df_age <- data_recoded %>%
  mutate(
    age = as.numeric(age)
  ) %>%
  filter(!is.na(age))

ggplot(df_age, aes(x = age)) +
  geom_histogram(binwidth = 1, color = "white") +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_y_continuous(breaks = seq(0, 50, by = 5)) +
  labs(
    title = "Age Distribution of Participants",
    x = "Age",
    y = "Number of Participants"
  ) +
  theme_minimal (base_size = 14)

mean_age <- mean(df_age$age)
sd_age <- sd(df_age$age)
median_age <- median(df_age$age, na.rm = TRUE)
min_age <- min(df_age$age, na.rm = TRUE)
max_age <- max(df_age$age, na.rm = TRUE)

mean_age
sd_age
median_age
min_age
max_age
```

```{r}

#questionnaire dropout spikes

df_dropout <- data_recoded %>%
  mutate(Progress = as.numeric(Progress)) %>%
  filter(!is.na(Progress), Progress < 100)

df_dropout_counts <- df_dropout %>%
  count(Progress) %>%
  arrange(Progress) %>%
  mutate(
    Progress = factor(Progress, levels = Progress)
  )

mean_progress <- mean(df_dropout$Progress, na.rm = TRUE)
sd_progress   <- sd(df_dropout$Progress, na.rm = TRUE)

mean_progress
sd_progress

ggplot(df_dropout_counts, aes(x = Progress, y = n)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = n),
            vjust = -0.4,
            size = 4) +
  labs(
    title = "Dropout Points Across Questionnaire",
    x = "Progress (%) at Dropout",
    y = "Number of Participants"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(),
    axis.title = element_text(),
    axis.text.x = element_text()
  )
```
```{r}
#country distribution

df_country_map <- data_recoded %>%
  mutate(country = ifelse(country == "" | is.na(country), NA, country)) %>%
  filter(!is.na(country)) %>%
  count(country) %>%
  mutate(country = tolower(country),
         country = dplyr::case_when(
           country == "united states of america" ~ "usa",
           country == "united kingdom of great britain and northern ireland" ~ "uk",
           TRUE ~ country
         ))

world_map <- map_data("world") %>%
  mutate(region = tolower(region))

world_data <- left_join(world_map, df_country_map, by = c("region" = "country"))

ggplot(world_data, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = n), color = "white", linewidth = 0.1) +
  scale_fill_gradient(
    low = "#deebf7",
    high = "#08519c",
    na.value = "grey95"
  ) +
  labs(
    title = "Participants by Country",
    fill = "Participants"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank()
)
```

```{r}
df_country_ranked <- df_country_map %>%
  arrange(desc(n))

df_country_ranked
```

# ========================================================================================================

# Bogi
# ========================================================================================================

# For loop solution
```{r}
color_vector = c(
  "Data analysis" = "#02452B", 
  "Data collection" = "#84CDF0", 
  "Post-project stage" = "#75069D",
  "Preparations" = "#2b4a78", 
  "Waiting" = "#9D3B06", 
  "Project genesis/ first thoughts/ idea creation" = "#B5E6D0",
  "Report writing" = "#E7C582", 
  "Reality check" = "#FFBF65",
  "Revisions" = "#c6a1f9"
)

for (stage in unique(na.omit(data_recoded$research_stage))) {
  stage_data <- data_recoded %>% 
    filter(research_stage == stage) %>% 
    analysis_select() %>% 
    longer_heatmap() %>% 
    sum_analysis()
  
  plot <- stage_data %>% 
    plot_overall() + 
    labs(
      title = paste("Overall intensity of emotions in the", stage, "stage")
    ) 
  
  print(plot)
}

for (stage in unique(na.omit(data_recoded$research_stage))) {
  stage_data <- data_recoded %>%
    filter(research_stage == stage) %>%
    analysis_select()
  
  stage_heatmap <- stage_data %>% 
  longer_heatmap()
  
  plot <- stage_heatmap %>%
    heatmap_plot() +
    scale_fill_gradient(
      low = "white", 
      high = color_vector[stage], 
      limits = c(0, 7)) +
  labs(
      title = paste("Intensity of emotions on the level of participants in the", stage, "stage"))
  
    print(plot)
}
  
```


# PART 1: Emotions By Research Stage
## 1. Emotions during the Data Analysis stage
## 1.1 Emotions on the participant-level
```{r}
analysis_data <- data_recoded %>% 
  filter(
    research_stage == "Data analysis"
  ) %>%
  analysis_select()

# pivot_longer for the heatmap
analysis_heatmap <- analysis_data %>% 
  longer_heatmap()

# heatmap by participant - Data Analysis stage
analysis_heatmap %>% 
  ggplot(aes(x = emotion, y = ResponseId, fill = intensity)) +
  geom_tile(
    inherit.aes = T,
    position = position_identity(), na.rm = T) +
  scale_fill_gradient(
      low = "white", 
      high = "#02452B", 
      limits = c(0, 7)) +
  labs(
      title = "Intensity of emotions on the level of participants in the Data Analysis stage", 
      tag = "1.1.") +
    theme(
      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
      axis.text.y = element_blank())

  ## heatmap_plot(analysis_heatmap)
```

## 1.2. Overall intensity of emotions
```{r}
analysis_overall <- analysis_heatmap %>% 
  sum_analysis() ## summarising emotional intensity on every emotion

analysis_overall %>% 
  plot_overall() +
    labs(
      title = "Overall intensity of emotions in the Data Analysis stage", 
      tag = "1.2.")

```

## 2. Emotions during the Preparations stage
## 2.1. Intensity of emotions on the participant-level
```{r}
preparations_data <- data_recoded %>% 
  filter(
    research_stage == "Preparations"
  ) %>% 
  analysis_select() ## selecting relevant columns

# pivot longer - for the heatmap of participant-level emotions
preparations_heatmap <- preparations_data %>% 
  longer_heatmap()

# heatmap by participant
preparations_heatmap %>%
  heatmap_plot() + 
   scale_fill_gradient(
      low = "white", 
      high = "#2b4a78", 
      limits = c(0, 7)) + 
  labs(
      title = "Intensity of emotions on the level of participants in the Preparations stage", 
      tag = "2.1.")
```

## 2.2. Overall intensity of emotions in the preparations stage
```{r}
preparations_overall <- preparations_heatmap %>% 
  sum_analysis() ## summarising emotional intensity on every emotion

preparations_overall %>% 
  plot_overall() + 
  labs(
      title = "Overall intensity of emotions in the Preparations stage", 
      tag = "2.2.")
```

## 3. Emotions while Waiting for journal's response and revisions
## 3.1. Participant-level intensity of emotions
```{r}
waiting_data <- data_recoded %>% 
  filter(
    research_stage == "Waiting"
  ) %>% 
  analysis_select()

# pivot longer - for the heatmap of participant-level emotions
waiting_heatmap <- waiting_data %>% 
  longer_heatmap()

# heatmap by participant
waiting_heatmap %>% 
  heatmap_plot() + 
   scale_fill_gradient(
      low = "white", 
      high = "#9D3B06", 
      limits = c(0, 7)) + 
  labs(
      title = "Intensity of emotions on the level of participants in the Waiting stage", 
      tag = "3.1.")
```

## 3.2. Overall intensity of emotions in the preparations stage
```{r}
waiting_overall <- waiting_heatmap %>% 
  sum_analysis() ## summarising intensity on every emotion

waiting_overall %>% 
  plot_overall() + 
  labs(
      title = "Overall intensity of emotions in the Waiting stage", 
      tag = "3.2.")
```
## 4. Post-project stage 
```{r}
post_project <- data_recoded %>% 
  filter(
    research_stage == "Post-project stage"
  ) %>% 
  select(-dismiss_1) 

# 4.1. accepted and published - mean intensity of emotions
post_project1 <- post_project %>%  
  filter(
    Q22 == "Accepted and published"
  ) %>% 
  select(-Q22_6_TEXT) 

post_project1_long <- post_project1 %>% 
  longer_heatmap() %>% 
  sum_analysis()

# geom_col for mean intensity
post_project1_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Accepted and published", 
      tag = "4.1.")
# most intense emotions if the article was accepted and published: interest, joy, pride, pleasure, relief, contentment (+ admiration, amusement)

# 4.2. Accepted but not yet published
post_project2 <- post_project %>% 
  filter(
    Q22 == "Accepted but not yet published"
  ) %>% 
  select(-Q22_6_TEXT)

post_project2_long <- post_project2 %>% 
  longer_heatmap() %>% 
  sum_analysis()

# geom_col for mean intensity
post_project2_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Accepted but not yet published", 
      tag = "4.2.")

## 4.3. Rejected (rejected and abandoned, rejected and being revised, rejected and postponed)
post_project3 <- post_project %>% 
  filter(
    Q22 %in% c("Rejected and abandoned", "Rejected and being revised", "Rejected and postponed")
  ) %>% 
  select(-Q22_6_TEXT)

post_project3_long <- post_project3 %>% 
  longer_heatmap() %>%
  sum_analysis()

post_project3_long %>% 
  plot_overall() + 
  labs(
      title = "Post-project stage: Rejected", 
      tag = "4.3.")
```

## 5. Report writing stage - heatmap and overall intensity of emotions
```{r}
report_writing <- data_recoded %>% 
  filter(
    research_stage == "Report writing"
  ) %>% 
  select(-dismiss_1, -Q22, -Q22_6_TEXT) 

# mean intensity of emotions
report_writing_long <- report_writing %>% 
  longer_heatmap() %>% 
  sum_analysis()

# heatmap 
writing_heatmap <- report_writing %>% 
  longer_heatmap() 

writing_heatmap %>% 
  heatmap_plot() +
   scale_fill_gradient(
      low = "white", 
      high = "#75069D", 
      limits = c(0, 7)) + 
  labs(
      title = "Intensity of emotions on the level of participants in the Waiting stage", 
      tag = "3.1.")

# geom_col for mean intensity
report_writing_long %>% 
  plot_overall() + 
  labs(
      title = "Report writing", 
      tag = "5.")
```


## 6. facet_wrap plot for emotional intensity in all research stages
```{r}
head(data_recoded)
overall_intensity <- data_recoded %>% 
  select(
    -Q22, -Q22_6_TEXT, -cause_stage, -dismiss_1, -Finished, -Progress, -Duration, -cause_general
  ) %>% 
  arrange(research_stage)

# create plot of overall emotions
## 1. long format
overall_long <- overall_intensity %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity") %>% 
  mutate(intensity = as.numeric(intensity), 
         emotion = factor(emotion, levels = unique(emotion))) %>% 
  group_by(research_stage, emotion) %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T), .groups = "drop") %>% 
  filter(!(is.na(research_stage)))

# create plot 
ggplot(overall_long, aes(x = emotion, y = mean_intensity, fill = intensity)) +
  facet_wrap(~ research_stage, nrow = 3) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#c6a1f9", na.rm = T
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") 

```

# --------------------------------------------------------------------------------------------------------
# PART 2: Gender, age, country, area of research, seniority level, category of work -> connections to emotions
## Step 1: prepare data for visualization
```{r}
genders_emotions = data_recoded %>%
  filter(
    gender %in% c("Woman", "Man")
  ) %>% 
  select(
    -Finished, -Duration, -Progress, -dismiss_1, -cause_stage, -cause_general, -Q22, -Q22_6_TEXT
  ) %>% 
  select(
    -category_of_work, -research_stage, -feeling_general_1, -position, -area, -age, -country, -country_other) %>% 
  rename(
    positive = c("interest", "amusement", "pride", "joy", "pleasure", "contentment", "love", "admiration", "relief", "compassion"), 
    negative = c("sadness", "guilt", "regret", "shame", "disappointment", "fear", "disgust", "contempt", "hate", "anger"))

genders_long <- genders_emotions %>%
  pivot_longer(
    cols = positive1:negative10,
    names_to = "valence",
    values_to = "intensity",
    values_transform = list(intensity = as.numeric)) %>% 
  mutate(valence = factor(valence,
                          levels = unique(valence)))

genders_wide <- genders_long %>%
  pivot_wider(
    names_from = "valence", 
    values_from = "intensity"
  ) %>% 
  mutate(
    positive_mean = rowMeans(select(., positive1:positive10), na.rm = T), 
    negative_mean = rowMeans(select(., negative1:negative10), na.rm = T)
  ) %>% 
  filter(
    !(is.na(negative_mean)), 
    !(is.nan(positive_mean))
  )
  
summary_genders <- genders_wide %>% 
  group_by(gender) %>% 
  summarise(
    positive = mean(positive_mean),
    negative = mean(negative_mean)
  ) %>% 
  pivot_longer(
    cols = c("positive", "negative"),
    names_to = "valence", 
    values_to = "intensity"
  )
```

## Step 2: visualize overall mean intensity of emotions between women and men
```{r}
ggplot(summary_genders,
       aes(x = valence, y = intensity)) +
  facet_wrap(~ gender) +
  geom_col(
    fill = "#c6a"
  ) + 
  labs(
    x = "Valence", 
    y = "Mean intensity", 
    title = "Emotional intensity between men and women" 
  ) +
  theme_minimal()

```

# --------------------------------------------------------------------------------------------------------
# PART 3: Analysis of standard deviations within the emotions 
## -> additional analysis: explorative, no visualization
```{r}
## flag where SD of emotions are > 1 
sd_flag <- data_recoded %>% 
  select(
    -Progress, -Duration, -Finished, -dismiss_1, -Q22, -Q22_6_TEXT 
  ) %>% 
  mutate(across("interest":"anger", as.numeric),
         mean_landscape = rowMeans(across("interest":"anger"), na.rm = T),
         sd_landscape = apply(across("interest":"anger"), 1, sd, na.rm = T)) %>% 
  filter(
    !(is.na(mean_landscape)),
    !(is.na(sd_landscape)), 
    !(is.nan(mean_landscape))
  )

## sd smaller than 0.9 -> emotional landscape lacks dimension
small_sd <- sd_flag %>% 
  filter(
    sd_landscape < 0.9
  )

## exporative: greater sd, potential reasons??
great_sd <- sd_flag %>% 
  filter(
    sd_landscape > 2.5
  )
```

# --------------------------------------------------------------------------------------------------------
# PART 4: Descriptive statistics of participants with emotional landscapes dominated by mainly negative or positive emotions
# 4.1. Participants with negative_mean > positive_mean 
## 4.1.1. Age distributions 
```{r}
averages_data <- data_recoded %>% 
  select(
    -Progress, -Duration, -Finished, -dismiss_1,
  ) %>% 
  mutate(
    across(interest:anger, as.numeric), 
    pos_mean = rowMeans(across(interest:compassion), na.rm = T), 
    neg_mean = rowMeans(across(sadness:anger), na.rm = T), 
    across(pos_mean:neg_mean, ~ na_if(., NaN))
  )

## filter: average intensity of emotions is higher regarding the negative emotions
negative_means <- averages_data %>% 
  filter(
    ((pos_mean < neg_mean) | is.na(pos_mean)), 
    !is.na(neg_mean)
  )

## classifying the data types of columns
age_negative <- negative_means %>%
  pos_neg_classify()

## creating age groups
age_negative_counts <- age_negative %>% 
  age_grouping()

## pyramid to explore the age distribution, split by gender 
age_negative_counts %>% 
  pyramid_plot()
```
## 4.1.2. Position
```{r}
position_negative <- negative_means %>%
  rename(category = position) %>% ## rename column for functions
  categories_prepare()

## pie chart for the distribution of positions
position_negative %>% 
  piechart_plot()
```

## 4.1.3. Category_of_work
```{r}
work_negative <- negative_means %>% 
  rename(category = category_of_work) %>% ## rename column for the functions
  categories_prepare()

## pie chart for the distribution of the categories
work_negative %>% 
  piechart_plot()
```

## 4.1.4. Research area 
```{r}
area_negative <- negative_means %>% 
  rename(category = area) %>% ## rename column for the functions
  categories_prepare()

area_negative %>% 
  piechart_plot()

```
## 4.1.5. Research stage
```{r}
stage_negative <- negative_means %>% 
  rename(category = research_stage) %>% ## rename column for functions 
  categories_prepare() %>% 
  mutate(
    category = stringr::str_trunc(category, 40))

## piechart plot
stage_negative %>% 
  piechart_plot()

```

# --------------------------------------------------------------------------------------------------------
# 4.2. Participants with negative_mean > positive_mean 
## 4.2.1. Age distributions
```{r}
positive_means <- averages_data %>% 
  filter(
    ((pos_mean > neg_mean) | is.na(neg_mean)), 
    !is.na(pos_mean)
  ) 

## classifying the data types of columns
age_positive <- positive_means %>%
  pos_neg_classify()

## creating age groups
age_positive_counts <- age_negative %>% 
  age_grouping()

## creating the age pyramid
age_positive_counts %>% 
  pyramid_plot()


```

## 4.2.2. Position
```{r}
position_positive <- positive_means %>%
  rename(category = position) %>% ## rename column for functions
  categories_prepare()

## pie chart for the distribution of positions
position_positive %>% 
  piechart_plot()

```

## 4.2.3. Category_of_work
```{r}
work_positive <- positive_means %>% 
  rename(category = category_of_work) %>% ## rename column for the functions
  categories_prepare()

## pie chart for the distribution of the categories
work_positive %>% 
  piechart_plot()


```
## 4.2.4. Research area 
```{r}
area_positive <- positive_means %>% 
  rename(category = area) %>% ## rename column for the functions
  categories_prepare()

area_positive %>% 
  piechart_plot()

```

## 4.2.5. Research stage
```{r}
stage_positive <- positive_means %>% 
  rename(category = research_stage) %>% ## rename column for functions 
  categories_prepare() %>% 
  mutate(
    category = stringr::str_trunc(category, 40))

## piechart plot
stage_positive %>% 
  piechart_plot()

```


# --------------------------------------------------------------------------------------------------------
# PART 5: Distributions of positive-negative emotions by research stage
## 5.1. Interest:
```{r}
# 1.1. Interest (first try)
interest_distribution <- data_recoded%>% 
  select(
    interest, research_stage
  ) %>% 
  filter(!(is.na(interest))) %>%
  group_by(research_stage) %>%
  mutate(
    research_stage = stringr::str_trunc(research_stage, 30))

interest_distribution %>% 
  ggplot(aes(x = research_stage, y = interest)) +
  geom_col(fill = "#B5E6D0", na.rm = T
    ) +
    labs(
      title = "Intensity of 'interest' through the research stages", tag = "2.") +
    theme(
      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```
## 5.2. Facet_wrap plot for all emotions in the research stages
```{r}
emotion_vars <-  c("interest", "amusement", "pride", "joy", "pleasure", "contentment", "love", "admiration", "relief", "compassion", "sadness", "guilt", "regret", "shame", "disappointment", "fear", "disgust", "contempt", "hate", "anger")                 

all_distribution <- data_recoded %>% 
  select(
    research_stage, interest:anger
  ) %>% 
  filter(!(is.na(research_stage))) %>% 
  mutate(
    research_stage = stringr::str_trunc(research_stage, 20)) %>% 
  group_by(research_stage) %>% 
  summarise(
    across(
      all_of(feeling_cols), 
      ~ round(mean(.x[.x != 0], na.rm = T), 3)
    )
  ) %>% 
  pivot_longer(
    cols = all_of(feeling_cols),
    names_to = "emotion", 
    values_to = "intensity"
  ) %>% 
  mutate(
    emotion = factor(emotion, levels = emotion_vars)
  )

all_distribution %>% 
  ggplot(aes(x = research_stage, y = intensity)) +
  geom_col(fill = "#84CDF0", na.rm = T
    ) +
    labs(
      title = "Intensity of all emotions through the research stages") +
    theme(
      axis.text.x = element_text(angle = 
                                   45, vjust = 1, hjust = 1, size = 6)) +
  facet_wrap(~ emotion, nrow = 3) 

```

# --------------------------------------------------------------------------------------------------------
# PART 6: Analyses to NA data regarding the emotions (emotions that were 'not felt')
```{r}
## df for counting NA values by research stage
na_counter <- data_recoded %>% 
  select(
    ResponseId, interest:anger, research_stage
  ) %>% 
  filter(!(is.na(research_stage))) %>% 
  group_by(research_stage) %>% 
  summarise(
    across(interest:anger, ~ sum(is.na(.))))

## Data analysis stage - long format for the barchart
data_analysis_na <- na_counter %>% 
  filter(research_stage == "Data analysis") %>% 
  pivot_longer(
    cols = -research_stage, 
    names_to = "emotion", 
    values_to = "na_count"
  )

## -> Barchart
data_analysis_na %>% 
  ggplot(aes(emotion, na_count)) +
  geom_bar(stat = "identity", fill = "#34B3E0") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") +
  labs(
      title = "NA values in the Data Analysis stage")

## All stages -> facet_wrap
na_all <- na_counter %>%
  pivot_longer(
    cols = -research_stage, 
    names_to = "emotion", 
    values_to = "na_count"
  )

## -> Barchart for all stages
na_all %>% 
  ggplot(aes(emotion, na_count)) +
  facet_wrap(
    ~ research_stage) +
  geom_bar(stat = "identity", fill = "#8DB5E0") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") +
  labs(
      title = "NA values in the research stages")

```

# ========================================================================================================
# Sanyi
# ========================================================================================================

```{r}
# overall emotions visualization by gender
gender_emotions = data_recoded_clean %>% 
  select(gender, all_of(feeling_cols)) %>% 
  filter(!(gender == ""))
gender_emotions = gender_emotions %>%  
  mutate(gender = if_else(gender == "Non-binary / third gender / gender non-conforming", "non-binary", gender)) %>% 
  mutate(gender = factor(gender))
gender_emotions_positive = gender_emotions %>% 
  select(gender, all_of(positive_feelings))
gender_emotions_negative = gender_emotions %>% 
  select(gender, all_of(negative_feelings)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))

gender_na = Nacount(data_recoded_clean, gender) %>% 
  filter(!(gender == ""))
na_prop_diverging_plot(gender_na, gender, "Proportion of NA's in Positive and Negative Emotions")


gender_emotions = emotion_function(gender_emotions, gender)

gender_emotions_mean = mean_function(gender_emotions, gender)

gender_emotions_positive = emotion_function(gender_emotions_positive, gender)

gender_emotions_mean_positive = mean_function(gender_emotions_positive, gender)

gender_emotions_negative = emotion_function(gender_emotions_negative, gender)

gender_emotions_mean_negative = mean_function(gender_emotions_negative, gender)


gender_pos = overall_emotion_plot_valence(gender_emotions_mean_positive, gender, mean_emotion, color_low = "orange", color_high = "red",
                             "Positive Emotions")

gender_neg = overall_emotion_plot_valence(gender_emotions_mean_negative, gender, mean_emotion, color_low = "lightblue", 
                     color_high = "blue", "Negative Emotions")

overall_emotion_plot(gender_emotions_mean, gender, mean_emotion,
                             "Overall Emotional Landscape by Gender")
combined_gender = gender_pos+gender_neg

combined_gender
```


#overall emotions visualization by research stage
```{r}
research_stage_emotions = data_recoded_clean %>% 
  select(research_stage, all_of(feeling_cols)) %>% 
  filter(!(research_stage == ""))
research_stage_emotions_positive = research_stage_emotions %>% 
  select(research_stage, all_of(positive_feelings))
research_stage_emotions_negative = research_stage_emotions %>% 
  select(research_stage, all_of(negative_feelings)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))

research_stage_na = Nacount(data_recoded_clean, research_stage) %>% 
  filter(!(research_stage == ""))
na_prop_diverging_plot(research_stage_na, research_stage, "Proportion of NA's in Positive and Negative Emotions")

research_stage_emotions = emotion_function(research_stage_emotions, research_stage)

research_stage_emotions_mean = mean_function(research_stage_emotions, research_stage)

research_stage_emotions_positive = emotion_function(research_stage_emotions_positive, research_stage)

research_stage_emotions_mean_positive = mean_function(research_stage_emotions_positive, research_stage)

research_stage_emotions_negative = emotion_function(research_stage_emotions_negative, research_stage)

research_stage_emotions_mean_negative = mean_function(research_stage_emotions_negative, research_stage)


research_stage_pos = overall_emotion_plot_valence(
  research_stage_emotions_mean_positive,
  research_stage,
  mean_emotion,
  color_low = "orange",
  color_high = "red",
  "Positive Emotions"
)

research_stage_neg = overall_emotion_plot_valence(
  research_stage_emotions_mean_negative,
  research_stage,
  mean_emotion,
  color_low = "lightblue",
  color_high = "blue",
  "Negative Emotions"
)

overall_emotion_plot(
  research_stage_emotions_mean,
  research_stage,
  mean_emotion,
  "Overall Emotional Landscape by Research Stage")

combined_research_stage = research_stage_pos + research_stage_neg
research_stage_neg 
research_stage_pos
combined_research_stage
```

overall emotion visualization area
```{r}
area_emotions = data_recoded_clean %>% 
  select(area, all_of(feeling_cols)) %>% 
  filter(!(area == ""))
area_emotions_positive = area_emotions %>%
select(area, all_of(positive_feelings))
area_emotions_negative = area_emotions %>% 
  select(area, all_of(negative_feelings)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))

area_na = Nacount(data_recoded_clean, area) %>% 
  filter(!(area == ""))

na_prop_diverging_plot(
  area_na,
  area,
  "Proportion of NA's in Positive and Negative Emotions")
area_emotions = emotion_function(area_emotions, area)

area_emotions_mean = mean_function(area_emotions, area)

area_emotions_positive = emotion_function(area_emotions_positive, area)

area_emotions_mean_positive = mean_function(area_emotions_positive, area)

area_emotions_negative = emotion_function(area_emotions_negative, area)

area_emotions_mean_negative = mean_function(area_emotions_negative, area)
```


Overall emotion visualization by position 
```{r}
position_emotions = data_recoded_clean %>% 
  filter(!(position == "")) %>% 
  select(position, all_of(feeling_cols))
position_emotions_positive = position_emotions %>%
  select(position, all_of(positive_feelings))
position_emotions_negative = position_emotions %>% 
  select(position, all_of(negative_feelings)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x))

position_na = Nacount(data_recoded_clean, position) %>% 
  filter(!(position == ""))

na_prop_diverging_plot(
  position_na,
  position,
  "Proportion of NA's in Positive and Negative Emotions")


position_emotions = emotion_function(position_emotions, position)

position_emotions_mean = mean_function(position_emotions, position)

position_emotions_positive = emotion_function(position_emotions_positive, position)

position_emotions_mean_positive = mean_function(position_emotions_positive, position)

position_emotions_negative = emotion_function(position_emotions_negative, position)

position_emotions_mean_negative = mean_function(position_emotions_negative, position)


position_pos = overall_emotion_plot_valence(
  position_emotions_mean_positive,
  position,
  mean_emotion,
  color_low = "orange",
  color_high = "red",
  "Positive Emotions"
)

position_neg = overall_emotion_plot_valence(
  position_emotions_mean_negative,
  position,
  mean_emotion,
  color_low = "lightblue",
  color_high = "blue",
  "Negative Emotions"
)


overall_emotion_plot(
  position_emotions_mean,
  position,
  mean_emotion,
  "Overall Emotional Landscape by Position"
)

position_combined = position_pos + position_neg
position_combined
```


DF mean emotions combined
```{r}
combined_emotions <- bind_rows(
  area_emotions_mean %>% 
    mutate(group = "Area",
           category = area),
  
  position_emotions_mean %>% 
    mutate(group = "Position",
           category = position), 
  
  gender_emotions_mean %>% 
    mutate(group = "Gender", 
           category = gender), 
  
  research_stage_emotions_mean %>% 
    mutate(group = "Research Stage",
           category = research_stage)
) %>% 
  select(group, category, mean_emotion)
```

Overall emotion visualization by country 

#Data cleaning
```{r}
country_emotions = data_recoded %>%  
  select(ResponseId, country, country_other, all_of(feeling_cols)) %>% 
  mutate(across(interest:anger, ~ na_if(.x, 0))) %>% 
mutate(
  mutate(across(all_of(feeling_cols),
                ~ as.numeric(as.character(.x))))) %>% 
    mutate(across(sadness:anger,~ 8 - .x)) %>% 
  mutate(mean_feeling = rowMeans(across(interest:anger), na.rm = TRUE))

country_emotions = country_emotions %>% 
  pivot_longer(cols = c(country, country_other), 
               names_to = "group", 
               values_to = "country")
country_emotions = country_emotions %>% 
  filter(!(country == "")) %>% 
  filter(!(ResponseId == "R_7YyTHrAj3Gc1fHP")) 


target_id = "R_7gbaE2EDWdQ3wOo"
target_text = "Also Germany Australia and recently China"


split_row = country_emotions %>%
  filter(ResponseId == target_id, country == target_text) %>%
  mutate(
    country = str_replace_all(country, "(?<=[a-z])(?=[A-Z])", " "),
    country = str_remove(country, "^Also\\s+"),
    country = str_remove(country, "\\s+ and recently\\s+"),
    country = str_squish(country),
    country = str_replace_all(country, "\\s+", ",")) %>%
  separate_rows(country, sep = ",")

rest <- country_emotions %>%
  filter(!(ResponseId == target_id & country == target_text))

country_emotions_clean <- bind_rows(split_row, rest)

country_emotions_clean = country_emotions_clean %>% 
  mutate(country = if_else(country == "Did my PhD in the US graduated in August and moved to Australia for postdoc", "United States of America", country)) %>% 
  mutate(country = if_else(country == "i work from home from italy", "Italy", country)) %>% 
  mutate(country = if_else(country == "Israel I am doing a collaboration in italy", "Israel", country)) %>% #because they indicated Italy in the "country" option
  mutate(country = if_else(country == "Actually Im from Palestine unfortunatley there is no mention for state of Palestine", "Palestine", country)) %>% #???
  mutate(country = if_else(country == "China ", "China", country)) %>% 
  mutate(country = if_else(country == "Makedonija", "Northern Macedonia", country)) %>% 
  mutate(country = if_else(country == "I am from Canada and have done research there", "Canada", country)) %>% 
  mutate(country = if_else(country == "south africa", "South Africa", country)) %>% 
  mutate(country = if_else(country == "England", "United Kingdom of Great Britain and Northern Ireland", country)) %>% 
  filter(!(country == "Africa")) %>% 
mutate(country = if_else(country == "N Macedonia", "North Macedonia", country)) %>% 
  filter(!(country %in% c("and","recently"))) %>% 
  mutate(country = if_else(country == "United States of America", "USA", country)) %>% 
  mutate(country = if_else(country == "United Kingdom of Great Britain and Northern Ireland", "UK", country))

country_emotions_clean <- bind_rows(
  country_emotions_clean %>%
    filter(ResponseId == "R_2GQ90ZxUHZ6JyFB", country == 	
             "Burkina Faso USA") %>%
    mutate(country = str_replace(country, "\\s+USA\\b", ",USA")) %>%  # insert delimiter before USA
    separate_rows(country, sep = ","),
  country_emotions_clean%>%
    filter(!(ResponseId == "R_2GQ90ZxUHZ6JyFB"  & country == "Burkina Faso USA")))



country_emotions_clean <- country_emotions_clean %>%
  mutate(
    continent = case_when(
      country %in% c("Algeria", "Burkina Faso", "Egypt", 
                     "Mali", "South Africa", "Sudan") ~ "Africa",
      country %in% c("Argentina", "Brazil", "Chile", "Costa Rica", 
                     "Colombia") ~ "South America/ Central America",
      country %in% c("Canada", "Mexico", 
                     "USA") ~ "North America",
      country %in% c("Austria", "Belgium", "Croatia", "Czech Republic",
                     "Denmark", "Finland", "France", "Germany", "Greece",
                     "Hungary", "Iceland", "Ireland", "Italy", "Lithuania",
                     "Netherlands", "North Macedonia", "Norway", "Poland",
                     "Portugal", "Romania", "Serbia", "Slovenia", "Spain",
                     "Sweden", "Switzerland",
                     "UK") ~ "Europe",
      country %in% c("China", "Hong Kong (S.A.R.)", "India", "Iran", "Iraq",
                     "Israel", "Japan", "Lebanon", "Malaysia", "Pakistan",
                     "Palestine", "Philippines", "Saudi Arabia", "Singapore",
                     "South Korea", "Sri Lanka", "Taiwan", "Thailand") ~ "Asia",
      country == "Turkey" ~ "Europe", 
      country %in% c("Australia", "New Zealand") ~ "Oceania", TRUE ~ NA_character_))


country_emotions_clean = country_emotions_clean %>% 
  mutate(country = factor(country))
country_emotions_clean_pos = country_emotions_clean %>% 
  select(ResponseId, country, continent, all_of(positive_feelings)) %>% 
  mutate(mean_feeling = rowMeans(across(interest:compassion), na.rm = TRUE))
country_emotions_clean_neg = country_emotions_clean %>% 
  select(ResponseId, country, continent, all_of(negative_feelings)) %>% 
  mutate(mean_feeling = rowMeans(across(sadness:anger), na.rm = TRUE)) %>% 
  mutate(across(sadness:anger, ~ 8 - .x)) %>% 
  mutate(NAcount = rowSums(is.na(across(sadness:anger)))) %>% 
  filter(!(NAcount > 5)) %>% 
  mutate(mean_feeling = rowMeans(across(sadness:anger), na.rm = TRUE))
```

```{r}
#Europe
europe_emotions_mean = continent_emotions_mean_function(country_emotions_clean, "Europe")
europe_emotions_mean_pos = continent_emotions_mean_function_pos(country_emotions_clean_pos,"Europe")
europe_emotions_mean_neg = continent_emotions_mean_function_neg(country_emotions_clean_neg, "Europe")

continent_plot_function(europe_emotions_mean, "Overall Emotional Landscape - Europe")
europe_pos = continent_plot_function_valence(europe_emotions_mean_pos, color_low = "orange", color_high = "red",  "Positive Emotions")
europe_neg = continent_plot_function_valence(europe_emotions_mean_neg, color_low = "lightblue", color_high = "blue", "Negative Emotions")
europe_combined = europe_pos + europe_neg
europe_combined
```

```{r}
#Asia
asia_emotions_mean = continent_emotions_mean_function(country_emotions_clean, "Asia")
asia_emotions_mean_pos = continent_emotions_mean_function_pos(country_emotions_clean_pos, "Asia")
asia_emotions_mean_neg = continent_emotions_mean_function_neg(country_emotions_clean_neg, "Asia")

continent_plot_function(asia_emotions_mean, "Overall Emotional Landscape - Asia")
asia_pos = continent_plot_function_valence(asia_emotions_mean_pos, color_low = "orange", color_high = "red", "Positive Emotions")
asia_neg = continent_plot_function_valence(asia_emotions_mean_neg, color_low = "lightblue", color_high = "blue", "Negative Emotions")
asia_combined = asia_pos + asia_neg
asia_combined
```

```{r}
#Africa
africa_emotions_mean = continent_emotions_mean_function(country_emotions_clean, "Africa")
africa_emotions_mean_pos = continent_emotions_mean_function_pos(country_emotions_clean_pos, "Africa")
africa_emotions_mean_neg = continent_emotions_mean_function_neg(country_emotions_clean_neg, "Africa")

continent_plot_function(africa_emotions_mean, "Overall Emotional Landscape - Africa")
africa_pos = continent_plot_function_valence(africa_emotions_mean_pos, color_low = "orange", color_high = "red", "Positive Emotions")
africa_neg = continent_plot_function_valence(africa_emotions_mean_neg, color_low = "lightblue", color_high = "blue", "Negative Emotions")
africa_combined = africa_pos + africa_neg
africa_combined
```


```{r}
#North America
northamerica_emotions_mean = continent_emotions_mean_function(country_emotions_clean, "North America")
northamerica_emotions_mean_pos = continent_emotions_mean_function_pos(country_emotions_clean_pos, "North America")
northamerica_emotions_mean_neg = continent_emotions_mean_function_neg(country_emotions_clean_neg, "North America")

continent_plot_function(northamerica_emotions_mean, "Overall Emotional Landscape - NorthAmerica")
northamerica_pos = continent_plot_function_valence(northamerica_emotions_mean_pos, color_low = "orange", color_high = "red", "Positive Emotions")
northamerica_neg = continent_plot_function_valence(northamerica_emotions_mean_neg, color_low = "lightblue", color_high = "blue", "Negative Emotions")
northamerica_combined = northamerica_pos + northamerica_neg
northamerica_combined
```

```{r}
#South America/ Central America
southamerica_emotions_mean = continent_emotions_mean_function(country_emotions_clean, "South America/ Central America")
southamerica_emotions_mean_pos = continent_emotions_mean_function_pos(country_emotions_clean_pos, "South America/ Central America")
southamerica_emotions_mean_neg = continent_emotions_mean_function_neg(country_emotions_clean_neg, "South America/ Central America")

continent_plot_function(southamerica_emotions_mean, "Overall Emotional Landscape - South America/Central America")
southamerica_pos = continent_plot_function_valence(southamerica_emotions_mean_pos, color_low = "orange", color_high = "red", "Positive Emotions")
southamerica_neg = continent_plot_function_valence(southamerica_emotions_mean_neg, color_low = "lightblue", color_high = "blue", "Negative Emotions")
southamerica_combined = southamerica_pos + southamerica_neg
southamerica_combined
```

```{r}
#Oceania
oceania_emotions_mean = continent_emotions_mean_function(country_emotions_clean,"Oceania")
oceania_emotions_mean_pos = continent_emotions_mean_function_pos(country_emotions_clean_pos,"Oceania")
oceania_emotions_mean_neg = continent_emotions_mean_function_neg(country_emotions_clean_neg,"Oceania")

continent_plot_function(oceania_emotions_mean,"Overall Emotional Landscape - Oceania")
oceania_pos = continent_plot_function_valence(oceania_emotions_mean_pos,color_low = "orange",color_high = "red","Positive Emotions")
oceania_neg = continent_plot_function_valence(oceania_emotions_mean_neg,color_low = "lightblue",color_high = "blue","Negative Emotions")
oceania_combined = oceania_pos + oceania_neg
oceania_combined
view(oceania_emotions_mean_neg)
```

```{r}
#based on frequency
top10_countries <- country_emotions_clean %>% 
  count(country, sort = TRUE) %>% 
  slice_head(n = 10) %>% 
  pull(country)

country_11_groups <- country_emotions_clean %>% 
  mutate(
    country_group = if_else(
      country %in% top10_countries,
      country,
      "Other countries")) %>% 
  group_by(country_group) %>% 
  summarise(
    mean_emotion = mean(mean_feeling, na.rm = TRUE),
    n = n(),   # optional, but nice to keep
    .groups = "drop")

country_11_groups %>% 
  mutate(dev = mean_emotion - 4) %>% 
  arrange(desc(n)) %>%   # arrange by frequency
  ggplot(aes(
    y = reorder(country_group, ifelse(country_group == "Other countries", -Inf, n)),
    x = dev,
    fill = mean_emotion)) +
  geom_col(width = 0.3) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(
    limits = c(-3, 3),
    breaks = -3:3,
    labels = 1:7) +
  scale_fill_gradient(low = "orange", high = "red") +
  theme_tufte() +
  labs(
    title = "Overall emotional landscape – top 10 countries with the most responses vs others", x = "", y = "" ) +
  theme(
    axis.text.y = element_text(size = 11,),
    plot.title  = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none")+
  theme(axis.ticks.y = element_blank())
```

```{r}
df_feeling_general = data_recoded %>% 
  drop_na() %>% 
  filter(!(cause_general %in% c("", "-", "na", "Na", "NA", "I don't know", "I dont know"))) %>% 
  filter(!(feeling_general_1 == 0)) %>% 
  select(ResponseId,feeling_general_1, cause_general ) %>% 
  mutate(valence = if_else(feeling_general_1 > 0, "positive", "negative"))

df_feeling_general<- df_feeling_general %>%
  mutate( attribution_category = case_when(
      
      str_detect(cause_general, regex("reviewer|editor|revision|reject|publication|journal", ignore_case = TRUE)) ~ "Peer Review",
      
      str_detect(cause_general, regex("data|analysis|results|insight|experiment|finding|discover", ignore_case = TRUE)) ~ "Data/Results",
      
      str_detect(cause_general, regex("project|employ|paper|\\bwork\\b", ignore_case = TRUE)) ~ "Project/Work-related",
      
      str_detect(cause_general, regex("ethic|bureaucr|paperwork|funding|NIH|permit|legal|funded|funding|job|employ", ignore_case = TRUE)) ~ "Institutional",
      
      str_detect(cause_general, regex("co-investigator|collaborat|team|mentor|colleague|supervisor|co-author|boss|\\bPI\\b|help", ignore_case = TRUE)) ~ "Collaboration",
      
      str_detect(cause_general, regex("deadline|timeline|pressure|workload|slow|delay", ignore_case = TRUE)) ~ "Time Pressure",
      
      str_detect(cause_general, regex("guilt|fear|self|my fault|competence|fail|underperform", ignore_case = TRUE)) ~ "Self-Evaluation",
      
      str_detect(cause_general, regex("interest|fascinat|passion|exciting|love research|idea|pleasure|creative", ignore_case = TRUE)) ~ "Intrinsic Interest",
      
      str_detect(cause_general, regex("sexism|bias|underfund|peripheral|mobing|institution|racism|female|woman", ignore_case = TRUE)) ~ "Structural Inequality",
      
      str_detect(cause_general, regex("lonely|isolat", ignore_case = TRUE)) ~ "Isolation",
      
      TRUE ~ "Other/Unclear"
    ))

#Visualization
attribution_counts_general <- df_feeling_general %>%
  count(attribution_category) %>%
  mutate(prop = n / sum(n)) %>%
  arrange(prop)

ggplot(attribution_counts_general,
       aes(x = reorder(attribution_category, prop),
           y = prop)) +
  geom_col(width = 0.6) +
  coord_flip() +
  labs(title = "Overall Attribution of Research-Related Emotions",
       x = "",
       y = "Proportion of Responses") +
  theme_minimal(base_size = 13)

valence_counts_general <- df_feeling_general %>%
  count(valence, attribution_category) %>%
  group_by(valence) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

ggplot(valence_counts_general,
       aes(x = reorder(attribution_category, prop),
           y = prop,
           fill = valence)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~ valence) +
  scale_fill_manual(values = c(
    "positive" = "red",
    "negative" = "blue"
  )) +
  labs(
    title = "Attributional Factors by Emotional Valence",
    x = "",
    y = "Proportion within Valence"
  ) +
  theme_minimal(base_size = 13)
```

