---
title: "analysis_bogi"
author: "ludmanyboglarka"
output: html_document
date: "2026-02-13"
---
# load libraries
```{r}
library(dplyr)
library(tidyverse)
library(tidyr)
library(magrittr)
library(apyramid)
library(ggplot2)
```

# load raw data
```{r}
raw_data <- readr::read_csv(("/Users/ludmanyboglarka/Documents/emotional_landscape/raw_data.csv"))
```
## pre-formatting raw data 
```{r}
raw_renamed <- raw_data %>% 
 rename(
    interest = feeling_stage_1,
    amusement = feeling_stage_2, 
    pride = feeling_stage_3, 
    joy = feeling_stage_4, 
    pleasure = feeling_stage_5, 
    contentment = feeling_stage_6, 
    love = feeling_stage_7, 
    admiration = feeling_stage_8, 
    relief = feeling_stage_9, 
    compassion = feeling_stage_10, 
    sadness = feeling_stage_11, 
    guilt = feeling_stage_12, 
    regret = feeling_stage_13, 
    shame = feeling_stage_14, 
    disappointment = feeling_stage_15, 
    fear = feeling_stage_16, 
    disgust = feeling_stage_17, 
    contempt = feeling_stage_18, 
    hate = feeling_stage_19, 
    anger = feeling_stage_20
  ) %>% 
  select(
    -Status, 
    -StartDate, 
    -EndDate, 
    -RecordedDate, 
    -DistributionChannel,
    -UserLanguage
  ) %>% 
  relocate(ResponseId, .before = Progress) %>% 
  mutate(
    across(9:28, as.numeric), 
    across(9:28, ~ na_if(., 0))) %>% ## this replaces 0 values with NA
  slice(-1:-3) %>% 
  filter(dismiss_1 != "No")
```
## load functions
```{r}
source("functions.R")
```



## Emotions By Research Stage
## 1. Emotions during the Data Analysis stage
## 1.1 Emotions on the participant-level
```{r}
analysis_data <- raw_renamed %>% 
  filter(
    research_stage == "Data analysis"
  ) %>%
  analysis_select()

# pivot_longer for the heatmap
analysis_heatmap <- analysis_data %>% 
  longer_heatmap()

# heatmap by participant - Data Analysis stage
analysis_heatmap %>% 
  heatmap_plot()
```

## 1.2. Overall intensity of emotions
```{r}
analysis_overall <- analysis_heatmap %>% 
  sum_analysis() ## summarising emotional intensity on every emotion

analysis_overall %>% 
  plot_overall()
```

## 2. Emotions during the Preparations stage
## 2.1. Intensity of emotions on the participant-level
```{r}
preparations_data <- raw_renamed %>% 
  filter(
    research_stage == "Preparations (IRB permit, preregistration, experiment preparations)"
  ) %>% 
  analysis_select() ## selecting relevant columns

# pivot longer - for the heatmap of participant-level emotions
preparations_heatmap <- preparations_data %>% 
  longer_heatmap()

# heatmap by participant
preparations_heatmap %>% 
  heatmap_plot()
```

## 2.2. Overall intensity of emotions in the preparations stage
```{r}
preparations_overall <- preparations_heatmap %>% 
  sum_analysis() ## summarising emotional intensity on every emotion

preparations_overall %>% 
  plot_overall()
```

## 3. Emotions while Waiting for journal's response and revisions
## 3.1. Participant-level intensity of emotions
```{r}
waiting_data <- raw_renamed %>% 
  filter(
    research_stage == "Waiting for journal's response and revisions"
  ) %>% 
  analysis_select()

# pivot longer - for the heatmap of participant-level emotions
waiting_heatmap <- waiting_data %>% 
  longer_heatmap()

# heatmap by participant
waiting_heatmap %>% 
  heatmap_plot()
```

## 2.2. Overall intensity of emotions in the preparations stage
```{r}
waiting_overall <- waiting_heatmap %>% 
  sum_analysis() ## summarising intensity on every emotion

waiting_overall %>% 
  plot_overall()
```
## 4. Post-project stage 
```{r}
post_project <- raw_renamed %>% 
  filter(
    research_stage == "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)"
  ) %>% 
  select(-dismiss_1) 

# 4.1. accepted and published - mean intensity of emotions
post_project1 <- post_project %>%  
  filter(
    Q22 == "Accepted and published"
  ) %>% 
  select(-Q22_6_TEXT) 

post_project1_long <- post_project1 %>% 
  longer_heatmap() %>% 
  sum_analysis()

# geom_col for mean intensity
post_project1_long %>% 
  plot_overall()
# most intense emotions if the article was accepted and published: interest, joy, prode, pleasure, relief, contentment (+ admiration, amusement)

# 4.2. Accepted but not yet published
post_project2 <- post_project %>% 
  filter(
    Q22 == "Accepted but not yet published"
  ) %>% 
  select(-Q22_6_TEXT)

post_project2_long <- post_project2 %>% 
  longer_heatmap() %>% 
  sum_analysis()

# geom_col for mean intensity
post_project2_long %>% 
  plot_overall()

## 4.3. Rejected (rejected and abandoned, rejected and being revised, rejected and postponed)
post_project3 <- post_project %>% 
  filter(
    Q22 %in% c("Rejected and abandoned", "Rejected and being revised", "Rejected and postponed")
  ) %>% 
  select(-Q22_6_TEXT)

post_project3_long <- post_project3 %>% 
  longer_heatmap() %>%
  sum_analysis()

post_project3_long %>% 
  plot_overall()

```

## 5. facet_wrap plot for emotional intensity in all research stages
```{r}
overall_intensity <- raw_renamed %>% 
  rename(duration = `Duration (in seconds)`) %>% 
  select(
    -Q22, -Q22_6_TEXT, -cause_stage, -dismiss_1, -Finished, -Progress, -duration, -cause_general
  ) %>% 
  arrange(research_stage)

# create plot of overall emotions
## 1. long format
overall_long <- overall_intensity %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity") %>% 
  mutate(intensity = as.numeric(intensity), 
         emotion = factor(emotion, levels = unique(emotion))) %>% 
  group_by(research_stage, emotion) %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T), .groups = "drop") %>% 
  filter(!(is.na(research_stage)))

# create plot 
ggplot(overall_long, aes(x = emotion, y = mean_intensity, fill = intensity)) +
  facet_wrap(~ research_stage, nrow = 3) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#c6a1f9", na.rm = T
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") 

```

## gender, age, country, area of research, seniority level, category of work -> connections to emotions
```{r}
## 1. check difference between genders - make plot (men, women, non-binary and prefer not to say)
## 2. t-test to test statistical significance 
## 1.1. women
genders_emotions <- raw_renamed %>%
  filter(
    gender %in% c("Woman", "Man")
  ) %>% 
  select(
    -Finished, -`Duration (in seconds)`, -Progress, -dismiss_1, -cause_stage, -cause_general, -Q22, -Q22_6_TEXT
  ) %>% 
  select(
    -category_of_work, -research_stage, -feeling_general_1, -position, -area, -age, -country, -country_other) %>% 
  rename(
    positive = c("interest", "amusement", "pride", "joy", "pleasure", "contentment", "love", "admiration", "relief", "compassion"), 
    negative = c("sadness", "guilt", "regret", "shame", "disappointment", "fear", "disgust", "contempt", "hate", "anger"))
  

## overall emotions within women (mean_intensity)
genders_long <- genders_emotions %>%
  pivot_longer(
    cols = positive1:negative10,
    names_to = "valence",
    values_to = "intensity",
    values_transform = list(intensity = as.numeric)) %>% 
  mutate(valence = factor(valence,
                          levels = unique(valence)))
genders_wide <- genders_long %>%
  pivot_wider(
    names_from = "valence", 
    values_from = "intensity"
  ) %>% 
  mutate(
    positive_mean = rowMeans(select(., 3:12), na.rm = T), 
    negative_mean = rowMeans(select(., 13:22), na.rm = T)
  ) %>% 
  filter(
    !(is.na(negative_mean)), 
    !(is.nan(positive_mean))
  )
  
summary_genders <- genders_wide %>% 
  group_by(gender) %>% 
  summarise(
    positive = mean(positive_mean),
    negative = mean(negative_mean)
  ) %>% 
  pivot_longer(
    cols = c("positive", "negative"),
    names_to = "valence", 
    values_to = "intensity"
  )

ggplot(summary_genders,
       aes(x = valence, y = intensity)) +
  facet_wrap(~ gender) +
  geom_col(
    fill = "#c6a"
  ) + 
  labs(
    x = "Valence", 
    y = "Mean intensity", 
    title = "Emotional intensity between men and women" 
  ) +
  theme_minimal()
```

## Analysis of standard deviations within the emotions 
```{r}
## flag where SD of emotions are > 1 
sd_flag <- raw_renamed %>% 
  select(
    -Progress, -`Duration (in seconds)`, -Finished, -dismiss_1, -Q22, -Q22_6_TEXT 
  ) %>% 
  mutate(across(2:21, as.numeric),
         mean_landscape = rowMeans(across(2:21), na.rm = T),
         sd_landscape = apply(across(2:21), 1, sd, na.rm = T)) %>% 
  filter(
    !(is.na(mean_landscape)),
    !(is.na(sd_landscape)), 
    !(is.nan(mean_landscape))
  )

## sd smaller than 0.9 -> emotional landscape lacks dimension
small_sd <- sd_flag %>% 
  filter(
    sd_landscape < 0.9
  )

## exporative: greater sd, potential reasons??
great_sd <- sd_flag %>% 
  filter(
    sd_landscape > 2.5
  )
```

## participants with negative_mean > positive_mean -> age distributions
```{r}
averages_data <- raw_renamed %>% 
  select(
    -Progress, -`Duration (in seconds)`, -Finished, -dismiss_1,
  ) %>% 
  mutate(
    across(5:24, as.numeric), 
    pos_mean = rowMeans(across(5:14), na.rm = T), 
    neg_mean = rowMeans(across(15:24), na.rm = T), 
    across(35:36, ~ na_if(., NaN))
  )

## filter: average intensity of emotions is higher regarding the negative emotions
negative_means <- averages_data %>% 
  filter(
    ((pos_mean < neg_mean) | is.na(pos_mean)), 
    !is.na(neg_mean)
  )

## classifying the data types of columns
age_negative <- negative_means %>%
  mutate(
    age = as.numeric(age), 
    gender = as.factor(gender)
  ) %>% 
  filter(!is.na(age), !is.na(gender))  

age_negative_counts <- age_negative %>% 
  select(
    ResponseId, age, gender
  ) %>% 
  mutate(
    age_group = 
      case_when(
        (age >= 20 & age <= 30) ~ "20-30", 
        (age >= 31 & age <= 40) ~ "31-40", 
        (age >= 41 & age <= 50) ~ "41-50", 
        (age >= 51 & age <= 60) ~ "51-60", 
        (age >= 61 & age <= 70) ~ "61-70", 
        (age >= 71 & age <= 80) ~ "71-80", 
        (age >= 81 & age <= 90) ~ "81-90", 
        (age >= 91 & age <= 100) ~ "91-100"
      ), ## creating age groups, then converting the age_group variable to factor, so that the age_pyramid can be made
    age_group = factor(
      age_group,
      levels = c(
        "20-30","31-40","41-50","51-60",
        "61-70","71-80","81-90","91-100")
      )
  )

## pyramid to explore the age distribution, split by gender 
age_negative_counts %>% 
  age_pyramid(age_group = age_group, split_by = gender) +
  labs(
  x = "Age group", 
  y = "Number of people", 
  title = "Age distribution chart")
```
## participants with negative_mean > positive_mean -> position
```{r}
position_negative <- negative_means %>%
  rename(category = position) %>% ## rename column for functions
  categories_prepare()

## pie chart for the distribution of positions
position_negative %>% 
  piechart_plot()
```

## participants with negative_mean > positive_mean -> category_of_work
```{r}
work_negative <- negative_means %>% 
  rename(category = category_of_work) %>% ## rename column for the functions
  categories_prepare()

## pie chart for the distribution of the categories
work_negative %>% 
  piechart_plot()

```
## participants with negative_mean > positive_mean -> research area 
```{r}
area_negative <- negative_means %>% 
  rename(category = area) %>% ## rename column for the functions
  categories_prepare()

area_negative %>% 
  piechart_plot()
```
## participants with negative_mean > positive_mean -> research stage
```{r}
stage_negative <- negative_means %>% 
  rename(category = research_stage) %>% ## rename column for functions 
  categories_prepare() %>% 
  mutate(
    category = stringr::str_trunc(category, 40))

## piechart plot
stage_negative %>% 
  piechart_plot()
```
### Distributions of positive-negative emotions by research stage
## 1. Positive emotions:
```{r}
# 1.1. Interest (first try)
interest_distribution <- raw_renamed %>% 
  select(
    interest, research_stage
  ) %>% 
  filter(!(is.na(interest))) %>%
  group_by(research_stage) %>%
  mutate(
    research_stage = stringr::str_trunc(research_stage, 30))

interest_distribution %>% 
  ggplot(aes(x = research_stage, y = interest)) +
  geom_col(fill = "#B5E6D0", na.rm = T
    ) +
    labs(
      title = "Intensity of 'interest' through the research stages", tag = "2.") +
    theme(
      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## facet_wrap plot for all emotions in the research stages
all_distribution <- raw_renamed %>% 
  select(
    research_stage, interest:anger
  ) %>% 
  filter(!(is.na(research_stage))) %>% 
  mutate(
    research_stage = stringr::str_trunc(research_stage, 20)) %>% 
  pivot_longer(
    cols = -research_stage, 
    names_to = "emotion", 
    values_to = "intensity", 
    values_drop_na = T
  )

all_distribution %>% 
  ggplot(aes(x = research_stage, y = intensity)) +
  facet_wrap(~ emotion, nrow = 3) +
  geom_col(fill = "#84CDF0", na.rm = T
    ) +
    labs(
      title = "Intensity of all emotions through the research stages") +
    theme(
      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 6)) 

```
