---
title: "emotional_landscape"
author: "ludmanyboglarka"
output: html_document
date: "2026-02-13"
---
# load libraries
```{r}
library(dplyr)
library(tidyverse)
library(tidyr)
library(magrittr)
```

# load raw data
```{r}
raw_data <- readr::read_csv(("/Users/ludmanyboglarka/Documents/emotional_landscape/raw_data.csv"))
```

```{r}
raw_renamed <- raw_data %>% 
 rename(
    interest = feeling_stage_1,
    amusement = feeling_stage_2, 
    pride = feeling_stage_3, 
    joy = feeling_stage_4, 
    pleasure = feeling_stage_5, 
    contentment = feeling_stage_6, 
    love = feeling_stage_7, 
    admiration = feeling_stage_8, 
    relief = feeling_stage_9, 
    compassion = feeling_stage_10, 
    sadness = feeling_stage_11, 
    guilt = feeling_stage_12, 
    regret = feeling_stage_13, 
    shame = feeling_stage_14, 
    disappointment = feeling_stage_15, 
    fear = feeling_stage_16, 
    disgust = feeling_stage_17, 
    contempt = feeling_stage_18, 
    hate = feeling_stage_19, 
    anger = feeling_stage_20
  ) %>% 
  select(
    -Status, 
    -StartDate, 
    -EndDate, 
    -RecordedDate, 
    -DistributionChannel,
    -UserLanguage
  ) %>% 
  relocate(ResponseId, .before = Progress)

raw_renamed = raw_renamed[3:nrow(raw_renamed), ] %>% 
  filter(dismiss_1 != "No")
```

## 1. Emotions during the Data Analysis stage
## 1.1 Emotions on the participant-level
```{r}
analysis_data <- raw_renamed %>% 
  filter(
    research_stage == "Data analysis"
  ) %>% 
 select(
    -Q22,
    -Q22_6_TEXT, 
    -dismiss_1 
  ) %>% 
  filter(
    !(is.na(interest))) # only include participants whose emotions are recorded 

# pivot_longer for the heatmap
analysis_long <- analysis_data %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity", 
    values_transform = list(intensity = as.numeric
  ))

analysis_heatmap <- analysis_long %>% 
  select(
    ResponseId, emotion, intensity
  ) %>% 
  group_by(emotion)

# heatmap by participant
ggplot(analysis_heatmap, 
       aes(x = emotion, 
           y = ResponseId, 
           fill = intensity)) +
geom_tile(
    inherit.aes = T,
    position = position_identity(),
    height = 5) +
  scale_fill_gradient(
    low = "white", 
    high = "darkred", 
    limits = c(0, 7)) + 
  labs(
    title = "Intensity of emotions in the Data Analysis Stage on the level of participants", 
    tag = "1.") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    axis.text.y = element_blank()
  )
```

## 1.2. Overall intensity of emotions
```{r}
analysis_overall <- analysis_heatmap %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T))

ggplot(analysis_overall, 
        aes(x = emotion, 
            y = mean_intensity)) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#924624"
  ) +
  labs(
    title = "Overall intensity of emotions in the Data Analysis Stage", 
    tag = "2.") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

## 2. Emotions during the Preparations stage
## 2.1. Intensity of emotions on the participant-level
```{r}
preparations_data <- raw_renamed %>% 
  filter(
    research_stage == "Preparations (IRB permit, preregistration, experiment preparations)"
  ) %>% 
  select(
    -Q22, -Q22_6_TEXT, -dismiss_1
  )

# pivot longer - for the heatmap of participant-level emotions
preparations_long <- preparations_data %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity", 
    values_transform = list(intensity = as.numeric
  ))
preparations_heatmap <- preparations_long %>% 
  select(
    ResponseId, emotion, intensity
  ) %>% 
  group_by(emotion)

# heatmap by participant
ggplot(preparations_heatmap, 
       aes(x = emotion, 
           y = ResponseId, 
           fill = intensity)) +
geom_tile(
    inherit.aes = T,
    position = position_identity(),
    height = 5) +
  scale_fill_gradient(
    low = "white", 
    high = "#0a4376", 
    limits = c(0, 7)) + 
  labs(
    title = "Intensity of emotions in the Preparations Stage on the level of participants", 
    tag = "1.") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    axis.text.y = element_blank()
  )
```

## 2.2. Overall intensity of emotions in the preparations stage
```{r}
preparations_overall <- preparations_heatmap %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T))

ggplot(preparations_overall, 
        aes(x = emotion, 
            y = mean_intensity)) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#74b3ea"
  ) +
  labs(
    title = "Overall intensity of emotions in the Preparations Stage", 
    tag = "2.") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

## 3. Emotions while Waiting for journal's response and revisions
## 3.1. Participant-level intensity of emotions
```{r}
waiting_data <- raw_renamed %>% 
  filter(
    research_stage == "Waiting for journal's response and revisions"
  ) %>% 
  select(
     -Q22, -Q22_6_TEXT, -dismiss_1)

# pivot longer - for the heatmap of participant-level emotions
waiting_long <- waiting_data %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity", 
    values_transform = list(intensity = as.numeric
  ))
waiting_heatmap <- waiting_long %>% 
  select(
    ResponseId, emotion, intensity
  ) %>% 
  group_by(emotion)

# heatmap by participant
ggplot(waiting_heatmap, 
       aes(x = emotion, 
           y = ResponseId, 
           fill = intensity)) +
geom_tile(
    inherit.aes = T,
    position = position_identity(),
    height = 5, 
    na.rm = T) +
  scale_fill_gradient(
    low = "white", 
    high = "#0f531e", 
    limits = c(0, 7)) + 
  labs(
    title = "Intensity of emotions in the Waiting on the level of participants", 
    tag = "1.") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    axis.text.y = element_blank()
  )
```

## 2.2. Overall intensity of emotions in the preparations stage
```{r}
waiting_overall <- waiting_heatmap %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T))

ggplot(waiting_overall, 
        aes(x = emotion, 
            y = mean_intensity)) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#7ebf8c", na.rm = T
  ) +
  labs(
    title = "Overall intensity of emotions in the Waiting Stage", 
    tag = "2.") +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```
## 4. Post-project stage 
```{r}
post_project <- raw_renamed %>% 
  filter(
    research_stage == "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)"
  ) %>% 
  select(-dismiss_1) 

# 4.1. accepted and published - mean intensity of emotions
post_project1 <- post_project %>%  
  filter(
    Q22 == "Accepted and published"
  ) %>% 
  select(-Q22_6_TEXT) 

post_project1_long <- post_project1 %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity", 
    values_transform = list(intensity = as.numeric
  )) %>% 
  select(
    ResponseId, emotion, intensity
  ) %>% 
  group_by(emotion) %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T))

# geom_col for mean intensity
ggplot(post_project1_long, aes(x = emotion, y = mean_intensity)) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#b45bfc", na.rm = T
  ) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
# most intense emotions if the article was accepted and published: interest, joy, prode, pleasure, relief, contentment (+ admiration, amusement)

# 4.2. Accepted but not yet published
post_project2 <- post_project %>% 
  filter(
    Q22 == "Accepted but not yet published"
  ) %>% 
  select(-Q22_6_TEXT)
post_project2_long <- post_project2 %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity", 
    values_transform = list(intensity = as.numeric
  )) %>% 
  select(
    ResponseId, emotion, intensity
  ) %>% 
  group_by(emotion) %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T))

# geom_col for mean intensity
ggplot(post_project2_long, aes(x = emotion, y = mean_intensity)) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#b45bfc", na.rm = T
  ) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) 

## 4.3. Rejected (rejected and abandoned, rejected and being revised, rejected and postponed)
post_project3 <- post_project %>% 
  filter(
    Q22 %in% c("Rejected and abandoned", "Rejected and being revised", "Rejected and postponed")
  ) %>% 
  select(-Q22_6_TEXT)
post_project3_long <- post_project3 %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity", 
    values_transform = list(intensity = as.numeric
  )) %>% 
  select(
    ResponseId, emotion, intensity
  ) %>% 
  mutate(emotion = factor(emotion, 
                          levels = unique(emotion))) %>% 
  filter(!is.na(intensity))

ggplot(post_project3_long, aes(x = emotion, y = intensity)) +
  geom_jitter() + 
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) # plot is quite messy

```

## 5. facet_wrap plot for emotional intensity in all research stages
```{r}
overall_intensity <- raw_renamed %>% 
  rename(duration = `Duration (in seconds)`) %>% 
  select(
    -Q22, -Q22_6_TEXT, -cause_stage, -dismiss_1, -Finished, -Progress, -duration, -cause_general
  ) %>% 
  arrange(research_stage)

# create plot of overall emotions
## 1. long format
overall_long <- overall_intensity %>% 
  pivot_longer(
    cols = interest:anger,
    names_to = "emotion", 
    values_to = "intensity") %>% 
  mutate(intensity = as.numeric(intensity), 
         emotion = factor(emotion, levels = unique(emotion))) %>% 
  group_by(research_stage, emotion) %>% 
  summarise(mean_intensity = mean(intensity, na.rm = T), .groups = "drop") %>% 
  filter(!(is.na(research_stage)))

# create plot 
ggplot(overall_long, aes(x = emotion, y = mean_intensity, fill = intensity)) +
  facet_wrap(~ research_stage, nrow = 3) +
  scale_y_continuous(limits = c(0, 7)) +
  geom_col(
    fill = "#c6a1f9", na.rm = T
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), 
    legend.position = "none") 

```

