---
title: "plots-compiled"
author: "Boglarka Ludmany"
date: "2026-06-23"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r setup, include = FALSE}
# Updated library loading with checks for installation

if (!require("tidyverse")) install.packages("tidyverse")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("dplyr")) install.packages("dplyr")
if (!require("stringr")) install.packages("stringr")
if (!require("rstatix")) install.packages("rstatix")
if (!require("ggthemes")) install.packages("ggthemes")
if (!require("tidyr")) install.packages("tidyr")
if (!require("patchwork")) install.packages("patchwork")
if (!require("scales")) install.packages("scales")
if (!require("magrittr")) install.packages("magrittr")
if (!require("apyramid")) install.packages("apyramid")
if (!require("rlang")) install.packages("rlang")
if (!require("maps")) install.packages("maps")
if (!require("gganimate")) install.packages("gganimate")
if (!require("magick")) install.packages("magick")
if (!require("fmsb")) install.packages("fmsb")



library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(rstatix)
library(ggthemes)
library(tidyr)
library(patchwork)
library(scales)
library(magrittr)
library(apyramid)
library(rlang)
library(maps)
library(gganimate)
library(magick)
library(fmsb)
```

```{r setup, include = FALSE}
source("plots.R")
data <- read.csv("data/full_data.csv", na.strings = c("", "NA", "NaN"))

# Changed to data_clean for easier handling for next wrangling
raw_data = data[-1:-2, ]

feelings = c("interest","amusement","pride","joy","pleasure",
  "contentment","love","admiration","relief","compassion", "sadness", "guilt", "regret" ,"shame", "disappointment" , "fear", "disgust", "contempt" , "hate","anger")

positive <- c("interest", "amusement", "pride", "joy", "pleasure", "contentment", "love", "admiration", "relief", "compassion")
negative <- c("sadness", "guilt", "regret" ,"shame", "disappointment" , "fear", "disgust", "contempt" , "hate","anger")

original_order = c(
  "Project genesis/ first thoughts/ idea creation",
  "Reality check",
  "Preparations",
  "Data collection",
  "Data analysis",
  "Report writing",
  "Revisions",
  "Waiting",
  "Post-project stage")

position_order = c("Other", 
                   "Non-academic researcher",
                   "Full professor",
                   "Associate professor", 
                   "Assistant professor",
                   "Postdoc",
                   "PhD student",
                   "Research assistant")
```

```{r setup, include = FALSE}
processed_data = raw_data %>% 
  rename(interest = feeling_stage_1,
         amusement = feeling_stage_2,
         pride = feeling_stage_3,
         joy = feeling_stage_4,
         pleasure = feeling_stage_5,
         contentment = feeling_stage_6,
         love = feeling_stage_7, 
         admiration = feeling_stage_8, 
         relief = feeling_stage_9, 
         compassion = feeling_stage_10,
         sadness = feeling_stage_11, 
         guilt = feeling_stage_12,
         regret = feeling_stage_13, 
         shame = feeling_stage_14, 
         disappointment = feeling_stage_15, 
         fear = feeling_stage_16, 
         disgust = feeling_stage_17, 
         contempt = feeling_stage_18,
         hate = feeling_stage_19, 
         anger = feeling_stage_20) %>% 
  mutate(research_stage = factor(research_stage), 
         area = factor(area),
         gender = factor(gender),
         position = factor(position), 
         category_of_work = factor(category_of_work), 
         ) %>% 
  mutate(research_stage = recode(research_stage,	
                                 "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)"
                                 = "Post-project stage", 
                                 "Preparations (IRB permit, preregistration, experiment preparations)" = 
                                   "Preparations",
                                 "Reality check (e.g., literature search, consultation with colleagues)" =
                                   "Reality check",
                                 "Waiting for journal's response and revisions" = "Waiting",
                                 "Project genesis/ first thoughts/ idea creation" = "Project genesis"
                                 )) %>% 
  mutate(across(all_of(feelings),
                ~ as.numeric(as.character(.x)))) %>% 
  mutate(feeling_general_1 = as.numeric(as.character(feeling_general_1))) %>% 
  filter(!(dismiss_1 == "No")) %>% 
  rename(Duration = `Duration..in.seconds.`) %>% 
  # mutate(across(interest:anger, ~ na_if(.x, 0))) %>% 
  mutate(NAcount = rowSums(is.na(across(interest:anger)))) %>%
  mutate(NAcountpos = rowSums(is.na(across(interest:compassion)))) %>% 
  mutate(NAcountneg = rowSums(is.na(across(sadness:anger))))

means_data <- processed_data %>% 
  select(
    -Progress, -Duration, -Finished, -dismiss_1, 
  ) %>% 
  mutate(
    across(interest:anger, as.numeric), 
    pos_mean = rowMeans(across(interest:compassion), na.rm = T), 
    neg_mean = rowMeans(across(sadness:anger), na.rm = T), 
    across(pos_mean:neg_mean, ~ na_if(., NaN))
  ) %>% 
  select(
    ResponseId, research_stage, interest:anger, category_of_work, position, area, age, country, country_other, pos_mean, neg_mean, gender
  )
```

# 1. Overall pattern

- kutatók éreznek

## radar chart -\> overall intensity

- positive emotions more intensive than negative emotions

```{r}
## Radar chart - not yet sure if this is informative enough
### data preparation
emotion_means <- means_data %>% 
  select(interest:anger) %>% 
  pivot_longer(
    cols = everything(),
    names_to = "emotion", 
    values_to = "value"
  ) %>% 
  mutate(
    emotion = factor(emotion, levels = feelings)
  ) %>% 
  arrange(emotion) %>% 
  group_by(emotion) %>% 
  summarise(mean_value = mean(value, na.rm = T))

pos_radar_df <- emotion_means %>% 
  slice(1:10) %>% 
  pivot_wider(
    names_from = "emotion", 
    values_from = "mean_value"
  ) 

max_values <- rep(7, ncol(pos_radar_df))  
min_values <- rep(0, ncol(pos_radar_df))
  
pos_ready_df <- rbind(max_values, min_values, pos_radar_df)

positive_radar <- ggplotify::as.ggplot(function() radarchart(pos_ready_df,
          title = paste("Intensity of positive emotions")))

### negative emotions
neg_radar <- emotion_means %>% 
  slice(11:20) %>% 
  pivot_wider(
    names_from = "emotion", 
    values_from = "mean_value"
  )
neg_ready_df <- rbind(max_values, min_values, neg_radar)
negative_radar <- ggplotify::as.ggplot(function() radarchart(neg_ready_df,
          title = paste("Intensity of negative emotions")))

### both radars together: 
overall_radars <- negative_radar + positive_radar
overall_radars
```

-\> ha a 0-kat nem NA-ként kódolom, akkor a negatív-pozitív kontraszt sokkal nagyobb -\> a negatív érzelmek átlagát lehúzza az elemszám -\> ?

## 1.2. General feeling

```{r}
feeling_general <- processed_data %>% 
  select(feeling_general_1, research_stage) %>% 
  arrange(research_stage) %>% 
  filter(!is.na(research_stage), 
         !is.na(feeling_general_1)) %>% 
  mutate(general_valence = case_when(
    feeling_general_1 > 0 ~ "positive",
    feeling_general_1 < 0 ~ "negative", 
    feeling_general_1 == 0 ~ "neutral"))

ggplot(feeling_general, aes(x = research_stage, y = feeling_general_1, fill = general_valence)) +
  geom_jitter(aes(colour = general_valence)) +
  labs(
    title = "Intensity of general feeling", 
    x = "Research stage", 
    y = "General feeling", 
    fill = "General feeling", 
    colour = "General feeling"
  ) +
    theme(
      plot.title = element_text(),
      axis.text.x = element_text(size = 9, angle = 30, hjust = 1), 
      legend.title = element_text()
    )
  
  
```

# 2. Descriptives

## questionnaire completion

- only a data frame

```{r}
completion_table <- processed_data %>% 
  select(Finished) %>% 
  count(Finished, name = "count") %>% 
  mutate(Finished = recode(Finished, "True" = "completed", 
         "False" = "not completed"))

# completion_plot <- descriptive_plots(processed_data, "Status", "Questionnaire Completion")
# completion_plot
completion_table
```

## genders data frame:

```{r}
gender_table <- processed_data %>% 
  select(gender) %>% 
  count(gender, name = "n")

gender_table
```

## research area

```{r}
area_descriptive = descriptive_plots(processed_data, "area", "Participants by Research Area")

area_descriptive
```

## position

```{r}
position_descriptive <- descriptive_plots(processed_data, "position", "Participants by Position")

position_descriptive
```

## category of work

```{r}
work_descriptive <- descriptive_plots(processed_data, "category_of_work", "Participants by Category of Work")

work_descriptive
```

## country distribution

```{r}
df_country_map <- processed_data %>%
  mutate(country = ifelse(country == "" | is.na(country), NA, country)) %>%
  filter(!is.na(country)) %>%
  count(country) %>%
  mutate(country = tolower(country),
         country = dplyr::case_when(
           country == "united states of america" ~ "usa",
           country == "united kingdom of great britain and northern ireland" ~ "uk",
           TRUE ~ country
         ))

world_map <- map_data("world") %>%
  mutate(region = tolower(region))

world_map

world_data <- left_join(world_map, df_country_map, by = c("region" = "country"))

country_centroids <- world_data %>%
  filter(!is.na(n)) %>%
  group_by(region, n) %>%
  summarise(
    long = mean(long, na.rm = TRUE),
    lat  = mean(lat,  na.rm = TRUE),
    .groups = "drop"
  )


descriptive_plotmap <- ggplot(world_data, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = n), 
               color = "white", 
               linewidth = 0.1
               ) +
  # ggrepel::geom_label_repel(
  #   data = country_centroids,
  #   aes(x = long, y = lat, label = n),
  #   inherit.aes = FALSE, 
  #   size = 3, 
  #   max.overlaps = 20
  #   ) +
  geom_label(
    data = country_centroids,
    aes(x = long, y = lat, label = n),
    inherit.aes = FALSE,
    size = 2.5,
    color = "black",
    fontface = "bold",
    fill = "white",        
    alpha = 0.6,           
    label.size = 0.1,      
    check_overlap = TRUE
  ) +
  scale_fill_gradient(
    low  = "#deebf7",
    high = "#08519c",
    na.value = "grey95"
  ) +
  labs(
    title = "Participants by Country",
    fill  = "Participants"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title    = element_text(face = "bold"),
    axis.text.x   = element_blank(),
    axis.title    = element_blank(),
    panel.grid    = element_blank()
  )
descriptive_plotmap
```

## Europe

```{r}
plot_europe <- ggplot(world_data, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = n), color = "white", linewidth = 0.1) +
  geom_label(
    data = country_centroids %>% filter(long >= -25, long <= 45, lat >= 35, lat <= 72),
    aes(x = long, y = lat, label = n),
    inherit.aes = FALSE,
    size = 2.5,
    fill = "white",
    alpha = 0.7,
    label.size = 0.1
  ) +
  scale_fill_gradient(low = "#deebf7", high = "#08519c", na.value = "grey95") +
  coord_fixed(xlim = c(-25, 45), ylim = c(35, 72), ratio = 1.3) +
  labs(title = "Europe") +
  theme_minimal(base_size = 11) +
  theme(
    plot.title  = element_text(face = "bold"),
    axis.text   = element_blank(),
    axis.title  = element_blank(),
    panel.grid  = element_blank(),
    legend.position = "none"
  )

plot_europe
```

## data frame to rank countries

```{r}
df_country_ranked <- df_country_map %>%
  arrange(desc(n))

df_country_ranked
```

# 3. Research stage

- overall erzelmek a stagekben: line chart (?) -\> informative for research stage comparison

```{r}
by_research_stage <- sd_data(processed_data) %>% 
  select(research_stage, all_of(feelings), sd_landscape) %>% 
  filter(!(research_stage == "")) %>%
  filter(!(sd_landscape < 0)) %>% 
    mutate(across(sadness:anger, ~ 8 - .x))

research_stage_emotions_positive = by_research_stage %>% 
  select(research_stage, all_of(positive))
research_stage_emotions_positive = emotion_function(research_stage_emotions_positive, research_stage)

stage_pos_means = mean_function(research_stage_emotions_positive, research_stage) 

research_stage_emotions_negative = by_research_stage %>% 
  select(research_stage, all_of(negative)) %>% 
    mutate(across(sadness:anger, ~ 8 - .x))
research_stage_emotions_negative = emotion_function(research_stage_emotions_negative, research_stage)

stage_neg_means = mean_function(research_stage_emotions_negative, research_stage)

research_stage_emotion_chron1 =
  left_join(
    stage_pos_means,
    stage_neg_means,
    by = "research_stage"
  ) %>%
  rename(
    mean_emotion_pos = mean_emotion.x,
    mean_emotion_neg = mean_emotion.y
  )

chron_long <- research_stage_emotion_chron1 %>%
  pivot_longer(
    cols = c(mean_emotion_pos, mean_emotion_neg),
    names_to = "valence",
    values_to = "mean_emotion"
  ) %>% 
  mutate(research_stage = factor(research_stage, levels = original_order)) %>% 
  filter(!is.na(research_stage))

chron_plot <- chron_long %>%
  ggplot(aes(x = research_stage,
             y = mean_emotion,
             color = valence,
             group = valence)) +
  geom_point() +
  geom_point(size = 3) +
  scale_color_manual(
    values = c(
      mean_emotion_pos = "red",
      mean_emotion_neg = "blue"
    )
  ) +
  labs(title = "Positive vs Negative Emotions") +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
  scale_y_continuous(
  limits = c(1, 7),
  breaks = 1:7
)

chron_plot
```

## positive and negative emotions separately - dotplot
```{r}
research_stage_emotions_negative <- research_stage_emotions_negative %>% 
  mutate(research_stage = factor(research_stage, levels = original_order)) %>% 
  filter(!is.na(research_stage))

research_stage_emotions_positive <- research_stage_emotions_positive %>% 
   mutate(research_stage = factor(research_stage, levels = original_order)) %>% 
  filter(!is.na(research_stage))

stage_neg_long <- scatter_long(research_stage_emotions_negative)
stage_neg_plot <- scatterplot(stage_neg_long, palette_type = "Paired")
stage_neg_plot

stage_pos_long <- scatter_long(research_stage_emotions_positive)
stage_pos_plot <- scatterplot(stage_pos_long, palette_type = "Spectral")
stage_pos_plot

## Overall plot
mean_emotions_stage <- stage_neg_plot + stage_pos_plot
mean_emotions_stage
```

## Post-Project stage
```{r}
post_project <- processed_data %>% 
  filter(
    research_stage == "Post-project stage"
  ) %>% 
  select(-dismiss_1, -StartDate, -EndDate, -Status, -Progress, -Duration, -Finished, -RecordedDate, -DistributionChannel, -UserLanguage) 

# Accepted and published - mean intensity of emotions
post_project1 <- post_project %>%  
  filter(
    Q22 == "Accepted and published"
  ) %>% 
  select(-Q22_6_TEXT) 

post_project1_long <- post_project1 %>% 
  longer_heatmap() %>% 
  sum_analysis()

post_project1_plot <- post_project_plot(post_project1_long, "Accepted and Published: mean intensity of all emotions")
  
post_project1_plot
```
most intense emotions if the article was accepted and published: interest, joy, pride, pleasure, relief, contentment (+ admiration, amusement)

### Accepted but not yet published
```{r}
post_project2 <- post_project %>% 
  filter(
    Q22 == "Accepted but not yet published"
  ) %>% 
  select(-Q22_6_TEXT) %>% 
  filter(NAcount < 15)

post_project2_long <- post_project2 %>% 
  longer_heatmap() %>% 
  sum_analysis()

post_project2_plot <- post_project_plot(post_project2_long, "Accepted but not yet published: mean intensity of all emotions")
post_project2_plot
```
missing negative values - most likely due to the small sample (n = 12). only 2 answers contained negative emotions, yet the intensity was definitely not high (rather moderate-low). 

### 4.3. Rejected (rejected and abandoned, rejected and being revised, rejected and postponed)
```{r}
post_project3 <- post_project %>% 
  filter(
    Q22 %in% c("Rejected and abandoned", "Rejected and being revised", "Rejected and postponed")
  ) %>% 
  select(-Q22_6_TEXT)

post_project3_long <- post_project3 %>% 
  longer_heatmap() %>%
  sum_analysis()

post_project3_plot <- post_project_plot(post_project3_long, "Rejected: mean intensity of all emotions")
post_project3_plot
```

# Waiting stage, reality check stage
negative emotions slightly more intense, specifically: fear? 

# By age: Where positive or negative emotions were more dominant 
```{r}
## Data preparation: 
averages_data <- processed_data %>% 
  averages_prep()

age_data <- averages_data %>% 
  age_grouping() %>% 
  filter(!is.na(age), 
         !(is.na(pos_mean)),
         !(is.na(neg_mean))) %>% 
  mutate(valence = ifelse(pos_mean > neg_mean, "positive", "negative")) %>% 
  arrange(age_group) %>% 
  group_by(age_group) %>% 
  summarise(
    positive_mean = mean(pos_mean), 
    negative_mean = mean(neg_mean)
  ) %>% 
  pivot_longer(
    cols = c(positive_mean, negative_mean), 
    names_to = "valence", 
    values_to = "mean_value"
  )

age_proportional <- age_data %>% 
  mutate(mean_plot = ifelse(valence == "negative_mean", -mean_value, mean_value)) %>% 
    group_by(age_group) %>% 
    mutate(prop = mean_value/sum(mean_value))

age_plot <- ggplot(age_proportional, aes(x = age_group, y = prop, fill = valence)) +
    geom_col(width = 0.7) +
    # geom_hline(yintercept = 0.5) +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    scale_fill_manual(
      values = c("positive_mean" = "firebrick", "negative_mean" = "steelblue"),
      name = "Valence",
      labels = c("positive_mean" = "Positive", "negative_mean" = "Negative")
    ) +
    theme_tufte() +
    labs(y = "Proportion of total emotional intensity", 
         x = "", 
         title = "Proportion of total emotional intensity\nwithin the age groups") +
    coord_flip()
age_plot 
```

# Area
```{r}
area_data <- averages_data %>% 
  select(
    ResponseId, area, pos_mean, neg_mean
  ) %>% 
  filter(!is.na(area), 
         !(is.na(pos_mean)),
         !(is.na(neg_mean))) %>% 
  mutate(valence = ifelse(pos_mean > neg_mean, "positive", "negative")) %>% 
  arrange(area) %>% 
  group_by(area) %>% 
  summarise(
    positive_mean = mean(pos_mean), 
    negative_mean = mean(neg_mean)
  ) %>% 
  pivot_longer(
    cols = c(positive_mean, negative_mean), 
    names_to = "valence", 
    values_to = "mean_value"
  )

area_proportional <- area_data %>% 
  mutate(mean_plot = ifelse(valence == "negative_mean", -mean_value, mean_value)) %>% 
  group_by(area) %>% 
  mutate(prop = mean_value/sum(mean_value))

area_plot <- ggplot(area_proportional, aes(x = area, y = prop, fill = valence)) +
    geom_col(width = 0.7) +
    # geom_hline(yintercept = 0.5) +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    scale_fill_manual(
      values = c("positive_mean" = "firebrick", "negative_mean" = "steelblue"),
      name = "Valence",
      labels = c("positive_mean" = "Positive", "negative_mean" = "Negative")
    ) +
    theme_tufte() +
    labs(y = "Proportion of total emotional intensity", 
         x = "", 
         title = "Proportion of total emotional intensity\nwithin the areas of research") +
    coord_flip()
area_plot
```

# Category of work 
```{r}
work_data <- averages_data %>% 
  select(
    ResponseId, category_of_work, pos_mean, neg_mean
  ) %>% 
  filter(!is.na(category_of_work), 
         !(is.na(pos_mean)),
         !(is.na(neg_mean))) %>% 
  mutate(valence = ifelse(pos_mean > neg_mean, "positive", "negative")) %>% 
  arrange(category_of_work) %>% 
  group_by(category_of_work) %>% 
  summarise(
    positive_mean = mean(pos_mean), 
    negative_mean = mean(neg_mean)
  ) %>% 
  pivot_longer(
    cols = c(positive_mean, negative_mean), 
    names_to = "valence", 
    values_to = "mean_value"
  )

work_proportional <- work_data %>% 
  mutate(mean_plot = ifelse(valence == "negative_mean", -mean_value, mean_value)) %>% 
  group_by(category_of_work) %>% 
  mutate(prop = mean_value/sum(mean_value))

work_plot <- ggplot(work_proportional, aes(x = category_of_work, y = prop, fill = valence)) +
    geom_col(width = 0.7) +
    # geom_hline(yintercept = 0.5) +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    scale_fill_manual(
      values = c("positive_mean" = "firebrick", "negative_mean" = "steelblue"),
      name = "Valence",
      labels = c("positive_mean" = "Positive", "negative_mean" = "Negative")
    ) +
    theme_tufte() +
    labs(y = "Proportion of total emotional intensity", 
         x = "", 
         title = "Proportion of total emotional intensity\nwithin the categories of academic work") +
    coord_flip()
work_plot
```

# Position
```{r}
position_data <- averages_data %>% 
  select(
    ResponseId, position, pos_mean, neg_mean
  ) %>% 
  filter(!is.na(position), 
         !(is.na(pos_mean)),
         !(is.na(neg_mean))) %>% 
  mutate(valence = ifelse(pos_mean > neg_mean, "positive", "negative")) %>% 
  mutate(position = factor(position, levels = position_order)) %>% 
  arrange(position) %>% 
  group_by(position) %>% 
  summarise(
    positive_mean = mean(pos_mean), 
    negative_mean = mean(neg_mean)
  ) %>% 
  pivot_longer(
    cols = c(positive_mean, negative_mean), 
    names_to = "valence", 
    values_to = "mean_value"
  )

position_proportional <- position_data %>% 
  mutate(mean_plot = ifelse(valence == "negative_mean", -mean_value, mean_value)) %>% 
  group_by(position) %>% 
  mutate(prop = mean_value/sum(mean_value))

position_plot <- ggplot(position_proportional, aes(x = position, y = prop, fill = valence)) +
    geom_col(width = 0.7) +
    # geom_hline(yintercept = 0.5) +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    scale_fill_manual(
      values = c("positive_mean" = "firebrick", "negative_mean" = "steelblue"),
      name = "Valence",
      labels = c("positive_mean" = "Positive", "negative_mean" = "Negative")
    ) +
    theme_tufte() +
    labs(y = "Proportion of total emotional intensity", 
         x = "", 
         title = "Proportion of total emotional intensity\nacross positions") +
    coord_flip()
position_plot
```
- ?? missing values at associate professor 
