---
title: "Emotional Landscape of Empirical Research Projects"
author: "Boglarka Ludmany"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
                      echo = FALSE)
```

```{r}
# Updated library loading with checks for installation

if (!require("tidyverse")) install.packages("tidyverse")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("dplyr")) install.packages("dplyr")
if (!require("stringr")) install.packages("stringr")
if (!require("rstatix")) install.packages("rstatix")
if (!require("ggthemes")) install.packages("ggthemes")
if (!require("tidyr")) install.packages("tidyr")
if (!require("patchwork")) install.packages("patchwork")
if (!require("scales")) install.packages("scales")
if (!require("magrittr")) install.packages("magrittr")
if (!require("apyramid")) install.packages("apyramid")
if (!require("rlang")) install.packages("rlang")
if (!require("maps")) install.packages("maps")
if (!require("gganimate")) install.packages("gganimate")
if (!require("magick")) install.packages("magick")
if (!require("fmsb")) install.packages("fmsb")
if (!require("viridis")) install.packages("viridis")
if (!require("ggrepel")) install.packages("ggrepel")
if (!require("countrycode")) install.packages("countrycode")
if (!require("flextable")) install.packages("flextable")


library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(rstatix)
library(ggthemes)
library(tidyr)
library(patchwork)
library(scales)
library(magrittr)
library(apyramid)
library(rlang)
library(maps)
library(gganimate)
library(magick)
library(fmsb)
library(countrycode)
library(viridis)
library(ggrepel)
library(flextable)
```

```{r}
source("plots.R")
data <- read.csv("data/full_data.csv", na.strings = c("", "NA", "NaN"))

# Changed to data_clean for easier handling for next wrangling
raw_data = data[-1:-2, ]

feelings = c("interest","amusement","pride","joy","pleasure",
  "contentment","love","admiration","relief","compassion", "sadness", "guilt", "regret" ,"shame", "disappointment" , "fear", "disgust", "contempt" , "hate","anger")

positive <- c("interest", "amusement", "pride", "joy", "pleasure", "contentment", "love", "admiration", "relief", "compassion")
negative <- c("sadness", "guilt", "regret" ,"shame", "disappointment" , "fear", "disgust", "contempt" , "hate","anger")

original_order = c(
  "Project genesis/ first thoughts/ idea creation",
  "Reality check",
  "Preparations",
  "Data collection",
  "Data analysis",
  "Report writing",
  "Revisions",
  "Waiting",
  "Post-project stage")

position_order = c("Other", 
                   "Non-academic researcher",
                   "Full professor",
                   "Associate professor", 
                   "Assistant professor",
                   "Postdoc",
                   "PhD student",
                   "Research assistant")
```

```{r}
processed_data = raw_data %>% 
  rename(interest = feeling_stage_1,
         amusement = feeling_stage_2,
         pride = feeling_stage_3,
         joy = feeling_stage_4,
         pleasure = feeling_stage_5,
         contentment = feeling_stage_6,
         love = feeling_stage_7, 
         admiration = feeling_stage_8, 
         relief = feeling_stage_9, 
         compassion = feeling_stage_10,
         sadness = feeling_stage_11, 
         guilt = feeling_stage_12,
         regret = feeling_stage_13, 
         shame = feeling_stage_14, 
         disappointment = feeling_stage_15, 
         fear = feeling_stage_16, 
         disgust = feeling_stage_17, 
         contempt = feeling_stage_18,
         hate = feeling_stage_19, 
         anger = feeling_stage_20) %>% 
  mutate(research_stage = factor(research_stage), 
         area = factor(area),
         gender = factor(gender),
         position = factor(position), 
         category_of_work = factor(category_of_work), 
         ) %>% 
  mutate(research_stage = recode(research_stage,	
                                 "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)"
                                 = "Post-project stage", 
                                 "Preparations (IRB permit, preregistration, experiment preparations)" = 
                                   "Preparations",
                                 "Reality check (e.g., literature search, consultation with colleagues)" =
                                   "Reality check",
                                 "Waiting for journal's response and revisions" = "Waiting",
                                 "Project genesis/ first thoughts/ idea creation" = "Project genesis"
                                 )) %>% 
  mutate(across(all_of(feelings),
                ~ as.numeric(as.character(.x)))) %>% 
  mutate(feeling_general_1 = as.numeric(as.character(feeling_general_1))) %>% 
  filter(!(dismiss_1 == "No")) %>% 
  rename(Duration = `Duration..in.seconds.`) %>% 
  # mutate(across(interest:anger, ~ na_if(.x, 0))) %>% 
  mutate(NAcount = rowSums(is.na(across(interest:anger)))) %>%
  mutate(NAcountpos = rowSums(is.na(across(interest:compassion)))) %>% 
  mutate(NAcountneg = rowSums(is.na(across(sadness:anger))))

means_data <- processed_data %>% 
  select(
    -Progress, -Duration, -Finished, -dismiss_1, 
  ) %>% 
  mutate(
    across(interest:anger, as.numeric), 
    pos_mean = rowMeans(across(interest:compassion), na.rm = T), 
    neg_mean = rowMeans(across(sadness:anger), na.rm = T), 
    across(pos_mean:neg_mean, ~ na_if(., NaN))
  ) %>% 
  select(
    ResponseId, research_stage, interest:anger, category_of_work, position, area, age, country, country_other, pos_mean, neg_mean, gender
  )
```

# Overall pattern

The overall pattern represents that researchers reported both positive and negative emotional intensity in relation to their work.

## Overall intensity of positive and negative emotions

```{r}
## Radar chart - not yet sure if this is informative enough
### data preparation
emotion_means <- means_data %>% 
  select(interest:anger) %>% 
  pivot_longer(
    cols = everything(),
    names_to = "emotion", 
    values_to = "value"
  ) %>% 
  mutate(
    emotion = factor(emotion, levels = feelings)
  ) %>% 
  arrange(emotion) %>% 
  group_by(emotion) %>% 
  summarise(mean_value = mean(value, na.rm = T))

pos_radar_df <- emotion_means %>% 
  slice(1:10) %>% 
  pivot_wider(
    names_from = "emotion", 
    values_from = "mean_value"
  ) 

max_values <- rep(7, ncol(pos_radar_df))  
min_values <- rep(0, ncol(pos_radar_df))
  
pos_ready_df <- rbind(max_values, min_values, pos_radar_df)

positive_radar <- ggplotify::as.ggplot(function() radarchart(pos_ready_df,
          title = paste("Positive emotions")))

### negative emotions
neg_radar <- emotion_means %>% 
  slice(11:20) %>% 
  pivot_wider(
    names_from = "emotion", 
    values_from = "mean_value"
  )
neg_ready_df <- rbind(max_values, min_values, neg_radar)
negative_radar <- ggplotify::as.ggplot(function() radarchart(neg_ready_df,
          title = paste("Negative emotions")))
```

```{r}
### both radars together: 
overall_radars <- negative_radar + positive_radar + plot_layout(widths = c(1, 1))
overall_radars
```

As can be seen on the radar charts, positive emotions tended to be more intensely experienced than negative emotions. Interest was reported with the greatest intensity, followed by pride and contentment. Among negative emotions, fear and disappointment exhibited the highest mean intensity. 

## Intensity of general feeling throughout the research stages

Regarding the intensity of the general feeling (represented on a scale of -3 to 3), the visualization includes a distribution of the reported general feeling scores.

```{r}
feeling_general <- processed_data %>% 
  select(feeling_general_1) %>% 
  filter(!is.na(feeling_general_1)) %>% 
  mutate(feeling_general_1 = as.double(feeling_general_1)) %>% 
  count(feeling_general_1)

general_distribution1 <- ggplot(feeling_general, aes(x = feeling_general_1, y = n)) +
  geom_point(width = 0.25) +
  scale_x_continuous(
    breaks = -3:3,
    labels = -3:3
  ) +
  theme(
    axis.title.y = element_blank()
  ) +
  labs(
    x = "General feeling scores",
    y = "n", 
    title = "")
```

```{r}
general_distribution1 + theme_bw()
```

The distribution shifted toward the positive end of the scale. The most frequent response (the mode) was 2, while the strongest positive response (3) was less frequent. Negative scores were relatively uncommon. 

# Overall emotional landscape by research stage

### Overall emotional landscape

```{r}
by_research_stage <- sd_data(processed_data) %>% 
  select(research_stage, all_of(feelings), sd_landscape) %>% 
  filter(!(research_stage == "")) %>%
  filter(!(sd_landscape < 0)) %>% 
    mutate(across(sadness:anger, ~ 8 - .x))

research_stage_emotions_positive = by_research_stage %>% 
  select(research_stage, all_of(positive))
research_stage_emotions_positive = emotion_function(research_stage_emotions_positive, research_stage)

stage_pos_means = mean_function(research_stage_emotions_positive, research_stage) 

research_stage_emotions_negative = by_research_stage %>% 
  select(research_stage, all_of(negative)) %>% 
    mutate(across(sadness:anger, ~ 8 - .x))
research_stage_emotions_negative = emotion_function(research_stage_emotions_negative, research_stage)

stage_neg_means = mean_function(research_stage_emotions_negative, research_stage)

research_stage_emotion_chron1 =
  left_join(
    stage_pos_means,
    stage_neg_means,
    by = "research_stage"
  ) %>%
  rename(
    mean_emotion_pos = mean_emotion.x,
    mean_emotion_neg = mean_emotion.y
  )

chron_long <- research_stage_emotion_chron1 %>%
  pivot_longer(
    cols = c(mean_emotion_pos, mean_emotion_neg),
    names_to = "valence",
    values_to = "mean_emotion"
  ) %>% 
  mutate(research_stage = factor(research_stage, levels = original_order)) %>% 
  filter(!is.na(research_stage))

chron_plot <- chron_long %>%
  ggplot(aes(x = research_stage,
             y = mean_emotion,
             color = valence,
             group = valence)) +
  geom_point() +
  geom_point(size = 3) +
  scale_color_manual(
    values = c(
      mean_emotion_pos = "red",
      mean_emotion_neg = "blue"
    ), 
    labels = c(
      mean_emotion_pos = "Positive", 
      mean_emotion_neg = "Negative"
    )
  ) +
  labs(
    title = "Emotional valence througout the research stages",
    x = "", 
    y = "Mean emotional intensity", 
    color = "Emotional valence") +
  # theme_tufte() +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    axis.title.x = element_blank(), 
    axis.title.y = element_text(size = 8)
    ) + 
  scale_y_continuous(
    limits = c(1, 7),
    breaks = 1:7
  )

chron_plot 
```

Throughout the research stages, it is clear that the valence of certain emotions was dominantly positive, especially regarding the Post-project stage, the Data analysis, Data collection and Report writing stages. Negative emotions were more intensely reported in the Reality check, and the Preparations stages, however, the intensity of positive emotions was substantially higher.

### Positive and negative emotions

```{r}
research_stage_emotions_negative <- research_stage_emotions_negative %>% 
  mutate(research_stage = factor(research_stage, levels = original_order)) %>% 
  filter(!is.na(research_stage))

research_stage_emotions_positive <- research_stage_emotions_positive %>% 
   mutate(research_stage = factor(research_stage, levels = original_order)) %>% 
  filter(!is.na(research_stage))

stage_neg_long <- scatter_long(research_stage_emotions_negative)
stage_neg_plot <- scatterplot(stage_neg_long, palette_type = "Paired") +
  labs(
      title = "Negative emotions",
      x = "",
      y = "Mean Score",
      color = "Emotion"
    )
# stage_neg_plot
```

```{r}
stage_pos_long <- scatter_long(research_stage_emotions_positive)
stage_pos_plot <- scatterplot(stage_pos_long, palette_type = "Spectral") +
  labs(
      title = "Positive emotions",
      x = "",
      y = "Mean Score",
      color = "Emotion"
    )
# stage_pos_plot
```

```{r, fig.height = 5, fig.width = 12}
mean_emotions_stage <- stage_neg_plot + stage_pos_plot + plot_layout(widths = c(1, 1))
mean_emotions_stage
```

Again, the plots illustrate that the intensity positive emotions was consistently higher than that of negative emotions. However, among negative emotions, disappointment was reported with relatively high intensity. The intensity of fear gradually decreased throughout the stages, although a slight increase was observed in the Waiting stage. With regards to positive emotions, interest emerged as the most intensely experienced emotion, followed by pride. A notable pattern is visible for relief, whose intensity increased steadily throughout the stages of research.

### Post-project stage

The Post-project stage was divided into 3 categories, depending on the outcome of the submission/future of the project: Accepted and published; Accepted but not yet published; Rejected (rejected and postponed, rejected and abandoned, rejected and being revised). The three subgroups of the Rejected category were merged due to the small sample size (_N_ = 12), therefore the results should be interpreted carefully.

```{r}
post_project <- processed_data %>% 
  filter(
    research_stage == "Post-project stage"
  ) %>% 
  select(-dismiss_1, -StartDate, -EndDate, -Status, -Progress, -Duration, -Finished, -RecordedDate, -DistributionChannel, -UserLanguage) 

# Accepted and published - mean intensity of emotions
post_project1 <- post_project %>%  
  filter(
    Q22 == "Accepted and published"
  ) %>% 
  select(-Q22_6_TEXT) %>% 
  filter(NAcount < 15)

post_project1_long <- post_project1 %>% 
  longer_heatmap() %>% 
  sum_analysis()

post_project1_plot <- post_project_plot(post_project1_long, "Accepted and Published") + 
  scale_colour_manual(
    values = c(
      positive = "firebrick",
      negative = "steelblue"
    )
  ) +
  theme(
    legend.position = "none"
  )

# post_project1_plot
```

```{r}
post_project2 <- post_project %>% 
  filter(
    Q22 == "Accepted but not yet published"
  ) %>% 
  select(-Q22_6_TEXT) %>% 
  filter(NAcount < 15)

post_project2_long <- post_project2 %>% 
  longer_heatmap() %>% 
  sum_analysis()

post_project2_plot <- post_project_plot(post_project2_long, "Accepted but not yet published") + 
  scale_colour_manual(
    values = c(
      positive = "firebrick",
      negative = "steelblue"
    )
  ) +
  theme(
    legend.position = "none"
  )
# post_project2_plot
```

```{r}
accepted_plots <- post_project1_plot + post_project2_plot + plot_layout(widths = c(1, 1))
accepted_plots
```

In both cases, positive emotions were still reported more intensively than negative emotions; the intensity of interest and pride was the highest, whereas amusement, love, admiration and compassion were the least intensely experienced emotions. Interestingly, in the *"Accepted but not yet published"* category, the intensity of negative emotions was slightly lower, and the intensity of certain positive emotions (joy, contentment, relief) was slightly higher, compared to the *"Accepted and published"* category. Across both categories, shame, hate, guilt and contempt were among the least experienced negative emotions; conversely, in the *"Accepted but not yet published"* category, sadness and disappointment were reported with relatively low intensity.

However, it is important to mention that the sample size of the *"Accepted but not yet published"* category is particularly small: *N* = 12, whilst in the *"Accepted and published"* category, the sample size is *N* = 23. The small sample size in the former category represents the exclusion of participants who did not complete the questionnaire.

```{r}
post_project3 <- post_project %>% 
  filter(
    Q22 %in% c("Rejected and abandoned", "Rejected and being revised", "Rejected and postponed")
  ) %>% 
  select(-Q22_6_TEXT) %>%
  filter(!is.na(feeling_general_1))

post_project3_long <- post_project3 %>%
  longer_heatmap() %>%
  sum_analysis()

post_project3_plot <- post_project_plot(post_project3_long, "Rejected: mean intensity of all emotions") + 
  scale_colour_manual(
    values = c(
      positive = "firebrick",
      negative = "steelblue"
    )
  ) +
  theme(
    legend.position = "none"
  )
```

```{r}
post_project3_plot + plot_layout(widths = c(1, 1))
```

In the *"Rejected"* category (including the *"Rejected and abandoned, Rejected and being revised, Rejected and postponed"* subcategories), negative emotions were relatively higher, compared to former visualizations. The most prominent negative emotions were disappointment, anger, sadness and regret. Furthermore, the interest remained to be reported with high intensity, followed by pride.

# Emotional Landscape Across Key Variables

```{r}
## Data preparation: 
averages_data <- processed_data %>% 
  averages_prep()

age_data <- averages_data %>% 
  age_grouping() %>% 
  filter(!is.na(age), 
         !(is.na(pos_mean)),
         !(is.na(neg_mean))) %>% 
  mutate(valence = ifelse(pos_mean > neg_mean, "positive", "negative")) %>% 
  arrange(age_group) %>% 
  group_by(age_group) %>% 
  summarise(
    positive_mean = mean(pos_mean), 
    negative_mean = mean(neg_mean)
  ) %>% 
  pivot_longer(
    cols = c(positive_mean, negative_mean), 
    names_to = "valence", 
    values_to = "mean_value"
  )

age_proportional <- age_data %>% 
  mutate(mean_plot = ifelse(valence == "negative_mean", -mean_value, mean_value)) %>% 
    group_by(age_group) %>% 
    mutate(prop = mean_value/sum(mean_value))

age_plot <- ggplot(age_proportional, aes(x = age_group, y = prop, fill = valence)) +
  geom_col(width = 0.7) +
  # geom_hline(yintercept = 0.5) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_fill_manual(
    values = c("positive_mean" = "firebrick", "negative_mean" = "steelblue"),
    name = "Valence",
    labels = c("positive_mean" = "Positive", "negative_mean" = "Negative")
    ) +
  # theme_tufte() +
  theme_light() +
  theme(
    plot.title = element_text(hjust = 0.5)
  ) +
  labs(
    y = "Proportion of total emotional intensity",
    x = "", 
    title = "Proportion of total emotional intensity\nwithin the age groups") +
  coord_flip()
age_plot 
```

The plot represents the proportion of the emotional intensity of positive and negative emotions. Across all groups, positive emotional intensity accounted for the majority of the total emotional intensity, indicating that positive emotions were dominant. Participants aged 71-90 exhibited the highest proportion of positive emotions. In the younger age groups, positive emotions represent roughly two-thirds or three-quarters of the total emotional intensity.

```{r}
area_data <- averages_data %>% 
  select(
    ResponseId, area, pos_mean, neg_mean
  ) %>% 
  filter(!is.na(area), 
         !(is.na(pos_mean)),
         !(is.na(neg_mean))) %>% 
  mutate(valence = ifelse(pos_mean > neg_mean, "positive", "negative")) %>% 
  arrange(area) %>% 
  group_by(area) %>% 
  summarise(
    positive_mean = mean(pos_mean), 
    negative_mean = mean(neg_mean)
  ) %>% 
  pivot_longer(
    cols = c(positive_mean, negative_mean), 
    names_to = "valence", 
    values_to = "mean_value"
  )

area_proportional <- area_data %>% 
  mutate(mean_plot = ifelse(valence == "negative_mean", -mean_value, mean_value)) %>% 
  group_by(area) %>% 
  mutate(prop = mean_value/sum(mean_value))

area_plot <- ggplot(area_proportional, aes(x = area, y = prop, fill = valence)) +
  geom_col(width = 0.7) +
  # geom_hline(yintercept = 0.5) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_fill_manual(
    values = c("positive_mean" = "firebrick", "negative_mean" = "steelblue"),
    name = "Valence",
    labels = c("positive_mean" = "Positive", "negative_mean" = "Negative")
    ) +
  # theme_tufte() +
  theme_light() +
  theme(
    plot.title = element_text(hjust = 0.5)
  ) +
  labs(y = "Proportion of total emotional intensity", 
       x = "", 
       title = "Proportion of total emotional intensity\nwithin the areas of research") +
  coord_flip()
area_plot
```

Among different areas of research, the pattern regarding the proportion of positive and negative emotions is consistent with the aforementioned results: positive emotional intensity represents the majority of the total emotional intensity. Nevertheless, it should be noted that compared to the other areas, researchers working in Physical sciences reported a slightly larger proportion of negative emotional intensity.

```{r}
work_data <- averages_data %>% 
  select(
    ResponseId, category_of_work, pos_mean, neg_mean
  ) %>% 
  filter(!is.na(category_of_work), 
         !(is.na(pos_mean)),
         !(is.na(neg_mean))) %>% 
  mutate(valence = ifelse(pos_mean > neg_mean, "positive", "negative")) %>% 
  arrange(category_of_work) %>% 
  group_by(category_of_work) %>% 
  summarise(
    positive_mean = mean(pos_mean), 
    negative_mean = mean(neg_mean)
  ) %>% 
  pivot_longer(
    cols = c(positive_mean, negative_mean), 
    names_to = "valence", 
    values_to = "mean_value"
  )

work_proportional <- work_data %>% 
  mutate(mean_plot = ifelse(valence == "negative_mean", -mean_value, mean_value)) %>% 
  group_by(category_of_work) %>% 
  mutate(prop = mean_value/sum(mean_value))

work_plot <- ggplot(work_proportional, aes(x = category_of_work, y = prop, fill = valence)) +
  geom_col(width = 0.7) +
  # geom_hline(yintercept = 0.5) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_fill_manual(
    values = c("positive_mean" = "firebrick", "negative_mean" = "steelblue"),
    name = "Valence",
    labels = c("positive_mean" = "Positive", "negative_mean" = "Negative")
    ) +
  # theme_tufte() +
  theme_light() +
  theme(
    plot.title = element_text(hjust = 0.5)
  ) +
  labs(y = "Proportion of total emotional intensity", 
       x = "", 
       title = "Proportion of total emotional intensity\nwithin the categories of academic work") +
  coord_flip()
work_plot
```

Across all research settings, positive emotions consistently represented the majority of total emotional intensity. A minor difference can be observed in the case of Lab/online research, where the proportion of negative emotions seems to be slightly larger.

```{r}
position_data <- averages_data %>% 
  select(
    ResponseId, position, pos_mean, neg_mean
  ) %>% 
  filter(!is.na(position), 
         !(is.na(pos_mean)),
         !(is.na(neg_mean))) %>% 
  mutate(valence = ifelse(pos_mean > neg_mean, "positive", "negative")) %>% 
  mutate(position = factor(position, levels = position_order)) %>% 
  arrange(position) %>% 
  group_by(position) %>% 
  summarise(
    positive_mean = mean(pos_mean), 
    negative_mean = mean(neg_mean)
  ) %>% 
  pivot_longer(
    cols = c(positive_mean, negative_mean), 
    names_to = "valence", 
    values_to = "mean_value"
  )

position_proportional <- position_data %>% 
  # mutate(mean_plot = ifelse(valence == "negative_mean", -mean_value, mean_value)) %>% 
  group_by(position) %>% 
  mutate(prop = mean_value/sum(mean_value))

position_plot <- ggplot(position_proportional, aes(x = position, y = prop, fill = valence)) +
  geom_col(
    # width = 0.7
  ) +
  # geom_hline(yintercept = 0.5) +
  scale_y_continuous(
    labels = scales::percent
  ) +
  scale_fill_manual(
    values = c("positive_mean" = "firebrick", "negative_mean" = "steelblue"),
    name = "Valence",
    labels = c("positive_mean" = "Positive", "negative_mean" = "Negative")
  ) +
  # theme_tufte() +
  theme_light() +
  theme(
    plot.title = element_text(hjust = 0.5)
  ) +
  labs(y = "Proportion of total emotional intensity", 
       x = "", 
       title = "Proportion of total emotional intensity\nacross positions") +
  coord_flip()
position_plot
```

Consistent with the previous findings regarding the proportion of positive and negative emotions, positive emotional intensity dominated across all academic positions. Associate and full professors reported relatively higher proportions of positive emotions, whereas PhD students and researchers classified in the "Other" category showed a comparatively larger proportion of negative emotional intensity.

### Countries

```{r}
country_emotions = processed_data %>%  
  select(ResponseId, country, country_other, all_of(feelings)) %>% 
  # mutate(across(interest:anger, ~ na_if(.x, 0))) %>% 
mutate(
  mutate(across(all_of(feelings),
                ~ as.numeric(as.character(.x))))) %>% 
  pivot_longer(cols = c(country, country_other), 
               names_to = "group", 
               values_to = "country") %>% 
  filter(!(country == "")) %>% 
  filter(!(ResponseId == "R_7YyTHrAj3Gc1fHP")) 


target_id = "R_7gbaE2EDWdQ3wOo"
target_text = "Also Germany Australia and recently China"


split_row = country_emotions %>%
  filter(ResponseId == target_id, country == target_text) %>%
  mutate(
    country = str_replace_all(country, "(?<=[a-z])(?=[A-Z])", " "),
    country = str_remove(country, "^Also\\s+"),
    country = str_remove(country, "\\s+ and recently\\s+"),
    country = str_squish(country),
    country = str_replace_all(country, "\\s+", ",")) %>%
  separate_rows(country, sep = ",")

rest <- country_emotions %>%
  filter(!(ResponseId == target_id & country == target_text))

country_emotions_clean <- bind_rows(split_row, rest)

country_emotions_clean = country_emotions_clean %>% 
  mutate(country = if_else(country == "Did my PhD in the US graduated in August and moved to Australia for postdoc", "United States of America", country)) %>% 
  mutate(country = if_else(country == "Uk", "UK", country)) %>% 
  mutate(country = if_else(country == "i work from home from italy", "Italy", country)) %>% 
  mutate(country = if_else(country == "Israel I am doing a collaboration in italy", "Israel", country)) %>% # because they indicated Italy in the "country" option
  mutate(country = if_else(country == "Actually Im from Palestine unfortunatley there is no mention for state of Palestine", "Israel", country)) %>% # ???
  mutate(country = if_else(country == "China ", "China", country)) %>% 
  mutate(country = if_else(country == "Makedonija", "Northern Macedonia", country)) %>% 
  mutate(country = if_else(country == "I am from Canada and have done research there", "Canada", country)) %>% 
  mutate(country = if_else(country == "south africa", "South Africa", country)) %>% 
  mutate(country = if_else(country == "England", "United Kingdom of Great Britain and Northern Ireland", country)) %>% 
  filter(!(country == "Africa")) %>% 
mutate(country = if_else(country == "N Macedonia", "North Macedonia", country)) %>% 
  filter(!(country %in% c("and","recently"))) %>% 
  mutate(country = if_else(country == "United States of America", "USA", country)) %>% 
  mutate(country = if_else(country == "United Kingdom of Great Britain and Northern Ireland", "UK", country))

country_emotions_clean <- bind_rows(
  country_emotions_clean %>%
    filter(ResponseId == "R_2GQ90ZxUHZ6JyFB", country == 	
             "Burkina Faso USA") %>%
    mutate(country = str_replace(country, "\\s+USA\\b", ",USA")) %>%  # insert delimiter before USA
    separate_rows(country, sep = ","),
  country_emotions_clean%>%
    filter(!(ResponseId == "R_2GQ90ZxUHZ6JyFB"  & country == "Burkina Faso USA"))) 

country_emotions_clean = country_emotions_clean %>%  
  mutate(country = factor(country))

positive_countries = country_emotions_clean %>% 
  select(ResponseId, country, all_of(positive)) %>% 
  mutate(mean_feeling = rowMeans(across(interest:compassion), na.rm = TRUE)) %>% 
  arrange(country) %>% 
  mutate(country = factor(country)) %>% 
  group_by(country) %>% 
  filter(n() >= 10) %>% 
  ungroup() %>% 
  group_by(country) %>% 
  summarise(
    mean_emotion = mean(mean_feeling, na.rm = TRUE), 
    n = n(), 
    .groups = "drop"
  ) %>% 
  arrange(mean_emotion) %>% 
  mutate(
    country_iso = countrycode::countrycode(sourcevar = country, origin = "country.name", destination = "iso3c"))

negative_countries = country_emotions_clean %>% 
  select(ResponseId, country, all_of(negative)) %>% 
  mutate(mean_feeling = rowMeans(across(sadness:anger), na.rm = TRUE)) %>% 
  arrange(country) %>% 
  mutate(country = factor(country)) %>% 
  group_by(country) %>% 
  filter(n() >= 10) %>% 
  ungroup() %>% 
  group_by(country) %>% 
  summarise(
    mean_emotion = mean(mean_feeling, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>% 
  arrange(mean_emotion) %>% 
  mutate(country_iso = countrycode::countrycode(sourcevar = country, origin = "country.name", destination = "iso3c"))
```

Altogether, 71 countries were recorded in the dataset, many of which were represented by only 1-2 respondents. Therefore the visualizations only include countries with at least 10 respondents.

```{r}
countries_pos <- ggplot(positive_countries, aes(x = reorder(country, mean_emotion), y = mean_emotion, colour = country)) +
  geom_point(size = 3) +
  theme_bw() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
          plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(limits = c(1, 7)) +
  labs(
      title = "Mean positive emotional intensity by countries (with at least 10 respondents)",
      x = "",
      y = ""
    ) +
  ggrepel::geom_text_repel(aes(label = paste0(country_iso, "\n", n)))

countries_pos
```

Indian, Spanish, Brazilian and Turkish respondents indicated the highest values regarding positive emotions (mean emotional intensity was above 4). 

```{r}
countries_neg <- ggplot(negative_countries, aes(x = reorder(country, mean_emotion), y = mean_emotion, colour = country)) +
  geom_point(size = 3) + 
  ggrepel::geom_text_repel(aes(label = paste0(country_iso, "\n", n))) +
  theme_bw() +
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
          plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(limits = c(0, 7)) +
  labs(
      title = "Mean negative emotional intensity by countries (with at least 10 respondents)",
      x = "",
      y = ""
    )

countries_neg
```

The differences in mean values regarding negative emotions is not substantial: Belgian respondents' mean emotional intensity was 0.8833, and mean emotional intensity regarding Turkey was 2.2283. 

Notably, respondents from Turkey also reported comparatively high levels of both positive and negative emotional intensity relative to respondents from other countries.

# Descriptives

### Questionnaire completion

The following table summarizes questionnaire completion rates.

```{r}
completion_table <- processed_data %>% 
  select(Finished) %>% 
  count(Finished, name = "count") %>% 
  mutate(Finished = recode(Finished, "True" = "Completed", 
         "False" = "Not completed")) 

# completion_plot <- descriptive_plots(processed_data, "Status", "Questionnaire Completion")
completion_table %>% 
  flextable() %>% 
  set_header_labels(Finished = "") %>% 
  set_table_properties(align = "left", layout = "autofit")
```

### Genders

```{r}
gender_table <- processed_data %>% 
  select(gender) %>% 
  count(gender, name = "n") %>% 
  filter(!is.na(gender)) %>% 
  arrange(desc(n))
  
gender_table %>% 
  flextable() %>% 
  set_table_properties(align = "left", layout = "autofit")
```

With regards to gender, female respondents comprised the largest proportion of respondents, followed by male participants. Participants identifying as non-binary or selecting "Prefer not to say" constituted a smaller proportion of the sample.

### Participants by research area

```{r}
area_descriptive = descriptive_plots(processed_data, "area", "")

area_descriptive 
```

Health scientists represented the largest disciplinary groups, whereas physical scientists represented the smallest.

### Participants by position

```{r}
position_descriptive <- descriptive_plots(processed_data, "position", "")

position_descriptive
```

Professors comprised the most sizable position group in the sample (with full professors representing the most largest subgroup), while research assistants constituted the smallest position group.

### Participants by category of work

```{r}
work_descriptive <- descriptive_plots(processed_data, "category_of_work", "")

work_descriptive
```

The vast majority of researchers conduct research in laboratory or in online settings, yet researchers in the clinical field constitute a notable subgroup.

### Country distribution

```{r}
df_country_map <- processed_data %>%
  mutate(country = ifelse(country == "" | is.na(country), NA, country)) %>%
  filter(!is.na(country)) %>%
  count(country) %>%
  mutate(country = tolower(country),
         country = dplyr::case_when(
           country == "united states of america" ~ "usa",
           country == "united kingdom of great britain and northern ireland" ~ "uk",
           TRUE ~ country
         ))

world_map <- map_data("world") %>%
  mutate(region = tolower(region))

world_data <- left_join(world_map, df_country_map, by = c("region" = "country"))

country_centroids <- world_data %>%
  filter(!is.na(n)) %>%
  group_by(region, n) %>%
  summarise(
    long = mean(long, na.rm = TRUE),
    lat  = mean(lat,  na.rm = TRUE),
    .groups = "drop"
  )


descriptive_plotmap <- ggplot(world_data, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = n), 
               color = "white", 
               linewidth = 0.1
               ) +
  # ggrepel::geom_label_repel(
  #   data = country_centroids,
  #   aes(x = long, y = lat, label = n),
  #   inherit.aes = FALSE, 
  #   size = 3, 
  #   max.overlaps = 20
  #   ) +
  geom_label(
    data = country_centroids,
    aes(x = long, y = lat, label = n),
    inherit.aes = FALSE,
    size = 2.5,
    color = "black",
    fontface = "bold",
    fill = "white",        
    alpha = 0.6,           
    label.size = 0.1,      
    check_overlap = TRUE
  ) +
  scale_fill_gradient(
    low  = "#deebf7",
    high = "#08519c",
    na.value = "grey95"
  ) +
  labs(
    title = "",
    fill  = "Participants"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title    = element_text(face = "bold"),
    axis.text.x   = element_blank(),
    axis.title    = element_blank(),
    panel.grid    = element_blank(),
    legend.position = "none", 
    axis.text.y   = element_blank(),
  )
descriptive_plotmap
```

Respondents from the United States of America comprised the largest group in the sample. Although Australia and Canadian were notably represented countries, however, their representation was substantially lower that that of the United States.

Researchers from European countries constituted a substantial proportion of respondents, however, as can be seen on the map, the labels are visually cluttered (probably due to the size of Europe in contrast to the size of the world).\
In order to overcome the issue of the congested labels, a separate plot was created, which visualizes the numbers of respondents from European countries.

```{r}
plot_europe <- ggplot(world_data, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = n), color = "white", linewidth = 0.1) +
  geom_label(
    data = country_centroids %>% 
      filter(long >= -25, long <= 45, lat >= 35, lat <= 72),
    aes(x = long, y = lat, label = n),
    inherit.aes = FALSE,
    size = 2.5,
    fill = "white",
    alpha = 0.7,
    label.size = 0.1
  ) +
  scale_fill_gradient(low = "#deebf7", high = "#08519c", na.value = "grey95") +
  coord_fixed(xlim = c(-25, 45), ylim = c(35, 72), ratio = 1.3) +
  labs(title = "Europe") +
  theme_minimal(base_size = 11) +
  theme(
    plot.title  = element_text(face = "bold"),
    axis.text   = element_blank(),
    axis.title  = element_blank(),
    panel.grid  = element_blank(),
    legend.position = "none"
  )

plot_europe
```

Out of all 569 European participants, the researchers from the United Kingdom formed the largest group, followed by researchers from Spain, Italy, Poland and Germany.