---
title: "descriptive_analysis"
author: "Dominik Dianovics"
format: html
---

# Emotional landscape of reesearchers pilot data cleaning

## Descriptive analysis

### Installing packages

```{r echo=FALSE, output=FALSE}
library(tidyverse)
library(here)
library(ggplot2)
# install.packages("ggnewscale")
library(ggnewscale)
# install.packages("scales")
library(scales)
data_path <- here("data")
```

### Importing data

```{r}
data = read.csv(here::here("data/clean_to_processed_data.csv"))
```

### Refactoring research stages chronologically

```{r}
data = data |> 
  mutate(research_stage = factor(research_stage, levels = c(
    "Project genesis/ first thoughts/ idea creation",
    "Reality check (e.g., literature search, consultation with colleagues)",
    "Preparations (IRB permit, preregistration, experiment preparations)",
    "Data collection",
    "Data analysis",
    "Report writing",
    "Waiting for journal's response and revisions",
    "Revisions",
    "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)"
    ))) |> 
  mutate(research_stage = fct_recode(research_stage,
    "Project genesis" = "Project genesis/ first thoughts/ idea creation",
    "Reality check" = "Reality check (e.g., literature search, consultation with colleagues)",
    "Preparations" = "Preparations (IRB permit, preregistration, experiment preparations)",
    "Data collection" = "Data collection",
    "Data analysis" = "Data analysis",
    "Report writing" = "Report writing",
    "Waiting for journal" = "Waiting for journal's response and revisions",
    "Reviews and revisions" = "Revisions",
    "Post-project stage" = "Post-project stage (the project has received a decision (accepted or rejected). At this point, it is either concluded or being revised and prepared for submission to another venue)")
  )
```

## Filtering bad responses

```{r}

data_test = data |> 
  filter(position != "Non-academic researcher") |> 
  mutate(across(interest:anger, as.numeric)) |> 
  rowwise() |> 
  mutate(
    n_non_na = sum(!is.na(c_across(interest:anger))),
    n_unique = n_distinct(c_across(interest:anger), na.rm = TRUE)
  ) |> 
  ungroup() |> 
  filter(
    n_non_na > 0,
    !(n_non_na > 1 & n_unique == 1)
  ) |> 
  select(-n_non_na, -n_unique)

```


## Demographic data

### Number of participants

```{r}
n = data |> 
  summarise(n = n())
```

### Gender

```{r}
gender = data |> 
  group_by(gender) |> 
  summarise(n = n())
```

### Position

```{r}
position = data |> 
  group_by(position) |> 
  summarise(n = n())
```

### Discipline

```{r}
discipline = data |> 
  group_by(area) |> 
  summarise(n = n())
```

### Country

```{r}

country = data |> 
  group_by(country) |> 
  summarise(n = n())
```

### Category of work

```{r}
category_of_work = data |> 
  group_by(category_of_work) |> 
  summarise(n = n())
```

## Research stage

```{r}
research_stage = data |> 
  filter(!is.na(research_stage)) |>
  group_by(research_stage) |> 
  summarise(n = n())
```

### Save each data as csv

```{r}
tables <- list(
  n = n,
  position = position,
  gender = gender,
  discipline = discipline,
  country = country,
  category_of_work = category_of_work,
  research_stage = research_stage
)
folder_path <- "tables/"

for (name in names(tables)) {
  file_name <- paste0(folder_path, name, ".csv")
  write.csv(tables[[name]], here::here(file_name), row.names = FALSE)
}
```

## General feelings

```{r}
general_feeling = data |> 
  group_by(general_feeling) |> 
  summarise(n = n())

general_feeling_distribution = data |> 
  ggplot(aes(x = general_feeling)) +
  geom_bar()

ggsave(
  here::here("plots/general_feeling_distribution.jpeg"),
  width = 8,
  height = 4,
  dpi = 300
)
```

## Stage-specific feelings

### Grouping research stages

```{r}
emotion_vars <- c(
  "interest", "amusement", "pride", "joy", "pleasure", "contentment",
  "love", "admiration", "relief", "compassion", "sadness", "guilt",
  "regret", "shame", "disappointment", "fear", "disgust", "contempt",
  "hate", "anger"
)

research_stage_grouped_mean <- data |> 
  filter(!is.na(research_stage)) |> 
  group_by(research_stage) |> 
  summarise(
    across(
      all_of(emotion_vars), 
      ~ round(mean(.x[.x != 0], na.rm = TRUE), 3)
    )
  )

# For every research stage, pick the highest and lowest

research_stage_long <- research_stage_grouped_mean |> 
  pivot_longer(cols = all_of(emotion_vars), names_to = "emotion", values_to = "mean_value")

highest_stage_feeling <- research_stage_long |> 
  group_by(research_stage) |> 
  slice_max(order_by = mean_value, n = 1, with_ties = FALSE)

lowest_stage_feeling <- research_stage_long |> 
  group_by(research_stage) |> 
  slice_min(order_by = mean_value, n = 1, with_ties = FALSE)

highest_lowest_feeling = highest_stage_feeling |> 
  left_join(lowest_stage_feeling, by = "research_stage", suffix = c("_highest", "_lowest")) |> 
  select(research_stage, emotion_highest, mean_value_highest, emotion_lowest, mean_value_lowest)

# Highest and lowest two emotions per stage
# NOT DONE

highest_stage_feeling <- research_stage_long |> 
  group_by(research_stage) |> 
  slice_max(order_by = mean_value, n = 2, with_ties = FALSE)

lowest_stage_feeling <- research_stage_long |> 
  group_by(research_stage) |> 
  slice_min(order_by = mean_value, n = 2, with_ties = FALSE)

highest_lowest_feeling = highest_stage_feeling |> 
  left_join(lowest_stage_feeling, by = "research_stage", suffix = c("_highest", "_lowest")) |> 
  select(research_stage, emotion_highest, mean_value_highest, emotion_lowest, mean_value_lowest)
```

### Dominant emotion for each stage

```{r}
dominant_emotion = research_stage_long |> 
  group_by(research_stage) |> 
  slice_max(order_by = mean_value, n = 1, with_ties = FALSE) |> 
  select(research_stage, emotion, mean_value)
```

# 3 highest intensity emotions for each stage

```{r}
three_highest_feelings = research_stage_long |> 
  group_by(research_stage) |> 
  slice_max(order_by = mean_value, n = 3, with_ties = FALSE)
```

### Most intense emotion for each person

```{r}
# FIX THIS
person_most_intense_feeling <- data %>% 
  rowwise() %>% 
  mutate(
    emotion_values = list(c_across(all_of(emotion_vars))),
    max_value = max(unlist(emotion_values), na.rm = TRUE),
    most_intense_feeling = paste0(
      emotion_vars[which(unlist(emotion_values) == max_value)],
      collapse = ", "
    )
  ) %>%
  select(anonym_id, research_stage, most_intense_feeling, max_value) %>%
  ungroup()
```


### Emotional change through the project

```{r}
research_stage_long = research_stage_long |> 
  mutate(emotion = factor(emotion, levels = emotion_vars))

ggplot(research_stage_long, aes(x = research_stage, y = mean_value, color = emotion, group = emotion)) +
  geom_line() +
  geom_point() +
  coord_cartesian(ylim = c(0, 7)) +
  facet_wrap( ~ emotion, ncol = 5) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.text.x = element_blank()
  )

ggsave(
  here::here("plots/emotion_line_plot.jpeg"),
  width = 8,
  height = 6,
  dpi = 300
)
```

## Positive vs negative emotions

### Group positive and negative emotions

```{r}
positive_emotions = c(
  "interest", "amusement", "pride", "joy", "pleasure", "contentment",
  "love", "admiration", "relief", "compassion"
)

negative_emotions = c(
  "sadness", "guilt", "regret", "shame", "disappointment", "fear",
  "disgust", "contempt", "hate", "anger"
)


dichotomous_emotion_data <- data |>
  filter(!is.na(research_stage)) |>
  rowwise() |>
  mutate(
    positive_emotions_mean = mean(c_across(all_of(positive_emotions))[c_across(all_of(positive_emotions)) != 0], na.rm = TRUE),
    negative_emotions_mean = mean(c_across(all_of(negative_emotions))[c_across(all_of(negative_emotions)) != 0], na.rm = TRUE)
  ) |>
  ungroup() |>
  group_by(research_stage) |>
  summarise(
    positive_emotions = mean(positive_emotions_mean, na.rm = TRUE),
    negative_emotions = mean(negative_emotions_mean, na.rm = TRUE)
  )


# highest positive and highest negative

positive_emotions_data = data |> 
  select(research_stage, all_of(positive_emotions)) |>
  filter(!is.na(research_stage))

negative_emotions_data = data |>
  select(research_stage, all_of(negative_emotions)) |>
  filter(!is.na(research_stage))
```

### Heatmap of emotion intensities

```{r}
heatmap_data <- research_stage_grouped_mean |>
  pivot_longer(
    cols = -research_stage,
    names_to = "emotion",
    values_to = "mean_intensity"
  ) |>
  mutate(emotion = factor(emotion, levels = rev(emotion_vars))) |> 
  mutate(valence = ifelse(emotion %in% positive_emotions, "positive", "negative"))

ggplot(heatmap_data, aes(x = factor(research_stage), y = emotion, fill = mean_intensity)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "plasma", na.value = "grey90") +
  labs(
    fill = "Mean Intensity (excl. 0)",
    title = "Mean Emotion Intensity by Research Stage"
  ) +
  geom_segment(aes(x = 0.5, xend = 9.5, y = 10.5), color = "green") +
  annotate("text", x = 10, y = 10.5, label = "Valence\ndivide") +
  coord_cartesian(clip = "off") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(20, 25, 10, 10),
    legend.position = "bottom"
  )

ggsave(
  here::here("plots/heatmap_plot.jpeg"),
  width = 8,
  height = 6,
  dpi = 300
)
```

### faceted bar chart for each stage for positive and negative emotions

```{r}
positive_emotions_mean <- positive_emotions_data |>
  filter(!is.na(research_stage)) |>
  rowwise() |>
  mutate(positive_mean = mean(c_across(all_of(positive_emotions))[c_across(all_of(positive_emotions)) != 0], na.rm = TRUE)) |>
  ungroup() |>
  group_by(research_stage) |>
  summarise(positive_mean = round(mean(positive_mean, na.rm = TRUE), 3))


negative_emotions_mean <- negative_emotions_data |>
  filter(!is.na(research_stage)) |>
  rowwise() |>
  mutate(negative_mean = mean(c_across(all_of(negative_emotions))[c_across(all_of(negative_emotions)) != 0], na.rm = TRUE)) |>
  ungroup() |>
  group_by(research_stage) |>
  summarise(negative_mean = round(mean(negative_mean, na.rm = TRUE), 3))

combined_valence_emotions_mean = positive_emotions_mean |> 
  left_join(negative_emotions_mean, by = "research_stage")

valence_long_mean <- combined_valence_emotions_mean |>
  pivot_longer(cols = c(positive_mean, negative_mean),
               names_to = "valence",
               values_to = "mean_intensity") |>
  mutate(valence = ifelse(valence == "positive_mean", "positive", "negative"))

ggplot(valence_long_mean, aes(x = valence, y = mean_intensity, fill = valence)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("positive" = "#d73027", "negative" = "#4575b4")) +
  facet_wrap(~ research_stage, ncol = 3) +
  labs(y = "Mean Emotion Intensity", x = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_blank())

ggsave(
  here::here("plots/faceted_bar_chart_valence.jpeg"),
  width = 8,
  height = 6,
  dpi = 300
)
```

### Heatmap for positive and negative emotions

```{r}
ggplot() +
  # Negative emotions in blue
  geom_tile(
    data = filter(heatmap_data, valence == "negative"),
    aes(x = factor(research_stage), y = emotion, fill = mean_intensity),
    color = "white"
  ) +
  scale_fill_gradient(
    low = "#e0ecf4", high = "#0571b0",  # light blue to dark blue
    name = "Negative\nMean Intensity"
  ) +
    ggnewscale::new_scale_fill() +
# Positive emotions in red
  geom_tile(
    data = filter(heatmap_data, valence == "positive"),
    aes(x = factor(research_stage), y = emotion, fill = mean_intensity),
    color = "white"
  ) +
  scale_fill_gradient(
    low = "#ffe5e5", high = "#d73027",  # light red to dark red
    name = "Positive\nMean Intensity"
  ) +
  labs(title = "Mean Emotion Intensity by Research Stage") +
  coord_cartesian(clip = "off") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    legend.position = "bottom",
    plot.margin = margin(20, 25, 10, 10)
  )

ggsave(
  here::here("plots/heatmap_plot_valence.jpeg"),
  width = 8,
  height = 6,
  dpi = 300
)
```

### Emotional change of positive and negative emotions

```{r}
dichotomous_emotion_data_long <- dichotomous_emotion_data |>
  pivot_longer(
    cols = c(positive_emotions, negative_emotions),
    names_to = "emotion",
    values_to = "mean_intensity"
  ) |> 
  mutate(emotion = ifelse(emotion == "positive_emotions", "positive", "negative"))

ggplot(dichotomous_emotion_data_long, aes(x = factor(research_stage), y = mean_intensity, color = emotion, group = emotion)) +
  geom_point() +
  geom_line() +
  scale_color_manual(values = c("positive" = "#d73027", "negative" = "#4575b4")) +
  labs(title = "Change of emotions over the course of a project", y = "Intensity of emotions", x = "") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

ggsave(
  here::here("plots/emotion_change_plot.jpeg"),
  width = 8,
  height = 6,
  dpi = 300
)
```

### Radar chart

```{r}
radar_data <- data |> 
  summarize(across(emotion_vars, ~ round(mean(.x, na.rm = TRUE), 1))) |> 
  rownames_to_column(var = "label") |> 
  pivot_longer(-label, names_to = "emotion", values_to = "score")


plot_data <- radar_data |> 
  select(-label) |> 
   mutate(emotion = factor(emotion, levels = emotion_vars))


ggplot(plot_data, aes(x = emotion, y = score, fill = score)) +
  geom_hline(yintercept = seq(1, 7, by = 1), color = "grey", size = 0.5) +
  geom_bar(stat = "identity") +
  scale_fill_gradientn(
    name = "Intensity of emotion",
    colours = c("#6C5B7B", "#C06C84", "#F67280", "#F8B195"),
    guide = guide_colorbar(
    barwidth = 15,
    barheight = 1.5,
    title.position = "top",
    title.hjust = 0.5
    )
  ) +
  coord_polar(start = 0, clip = "off") +
  scale_y_continuous(
    limits = c(-1, 7),
    expand = c(0, 0),
    breaks = c(0, 1, 2, 7)
  ) +
   annotate(
    x = 0.5, 
    y = 1, 
    label = "1", 
    geom = "text", 
    color = "gray12", 
    family = "serif",
    size = 4
  ) +
  annotate(
    x = 0.5, 
    y = 4, 
    label = "4", 
    geom = "text", 
    color = "gray12", 
    family = "serif",
    size = 4
  ) +
  annotate(
    x = 0.5, 
    y = 7, 
    label = "7", 
    geom = "text", 
    color = "gray12", 
    family = "serif",
    size = 4
  ) +
  theme_minimal(base_family = "serif") +
  labs(title = "Emotion wheel of researchers", y = "", x = "") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    plot.title = element_text(
      size = 16,
      family = "serif"
    ),
    legend.title = element_text(
      size = 12,
      family = "serif"
    ),
    panel.grid = element_blank(),
    axis.text.x = element_text(
      size = 12,
      family = "serif",
      margin = margin(t = 30)
  ),
  plot.margin = margin(20, 20, 20, 20),
    legend.position = "bottom"
  ) 


ggsave(
  here::here("plots/radar_chart_ggplot.jpeg"),
  width = 8,
  height = 8,
  dpi = 300
)
```

## Save data

```{r}
write.csv(research_stage_grouped_mean, here::here("data/research_stage_grouped_mean.csv"), row.names = FALSE)
write.csv(dichotomous_emotion_data, here::here("data/dichotomous_emotion_data.csv"), row.names = FALSE)
write.csv(general_feeling, here::here("data/general_feeling.csv"), row.names = FALSE)
write.csv(highest_lowest_feeling, here::here("data/highest_stage_feeling.csv"), row.names = FALSE)
write.csv(three_highest_feelings, here::here("data/lowest_stage_feeling.csv"), row.names = FALSE)
write.csv(dominant_emotion, here::here("data/highest_lowest_feeling.csv"), row.names = FALSE)
```
